---
title: "emoLearn_F24_AMI_analysis"
author: "Runan Wang"
date: "2026-02-18"
output: html_document
---

```{r setup, include=FALSE}
library(afex)
library(emmeans)
library(knitr)
library(tidyverse)
library(compute.es)
library(car)
library(ggplot2)
library(multcomp)
library(pastecs)
library(WRS2)
library(Hmisc)
library(tidyverse)
library(SuppDists)
library(ggpubr)
library(readxl)
library(ez)
library(lme4)
library(dplyr)
library(corrplot)
library(psych)
library(ggpubr) # for Q plot (normality check)
library(openxlsx)
library(colorspace)
library(ggrepel)
library(directlabels)
library(ggplot2)
library(reshape2)
library(plyr)
library(scales)
library(wesanderson)
library(brms)
library(stringr)
library(performance)
library(see)
library(tidyr)
library(lubridate)
library(tibble)
library(bayesplot)
library(janitor)
library(Rmisc)
library(RColorBrewer)
library(sjPlot)
`select` <- dplyr::select
`recode` <- dplyr::recode
`summarise` <- dplyr::summarise
`describe` <- psych::describe
knitr::opts_chunk$set(echo = TRUE)
```
# Load in function
## Collapsed function
```{r}
library(dplyr)
library(tibble)

collapse_text_by_label <- function(label_api_text, sentiment, intensity) {
  r <- rle(label_api_text)
  block_id <- rep(seq_along(r$lengths), r$lengths)

  tibble(
    label_api_text = label_api_text,
    sentiment = sentiment,
    intensity = intensity,
    block_id = block_id
  ) %>%
    group_by(block_id) %>%
    summarise(
      collapsed_text_type = first(label_api_text),
      length = dplyr::n(),
      score_sum = sum(sentiment * intensity),
      score_avg = mean(sentiment * intensity),
      score_peak = max(abs(sentiment * intensity)),
      score_start = first(sentiment * intensity),
      score_end = last(sentiment * intensity),
      .groups = "drop"
    ) %>%
    mutate(
      block_sentiment = case_when(
        score_sum > 0 ~ "POSITIVE",
        score_sum < 0 ~ "NEGATIVE",
        TRUE ~ "NEUTRAL"
      )
    )

}

```

# Load in data
```{r cars}
# AMI data
df_ami_senti_tmp <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/sentiment_analysis/AM/premedEMA_AMI_F24_sentiment.csv")
df_ami_senti <- df_ami_senti_tmp %>% filter(text != "")
#1.0, positive
#-1.0, negative
#0.0, neutral
#0.5, mixed
unique(df_ami_senti$valence)
```

```{r pressure, echo=FALSE}
# senti data
df_senti_full <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/emaData_F24_phrase_sentiment_v5.csv")

df_senti_full <- df_senti_full %>% mutate(api_val = ifelse(api_val == -0.5, 0.5, api_val))
unique(df_senti_full$api_val)

df_senti_full <- df_senti_full %>% mutate(label_api_text = case_when(label_api == -1 ~ "Expression",
                                                           label_api == 0 ~ "Neither",
                                                           label_api == 1 ~ "Regulation"))
```

## PE
```{r}
df_PE <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/survey_data_f24/premedEMA_f2024_predictors_df.csv")
colnames(df_PE)[1] = "ID"
# drop the wrong grade
df_PE <- df_PE %>% filter(shown_wrong !="1")
```
```{r}
df_PE <- df_PE %>% mutate(PE_1_val = case_when(PE_1 < 0 ~ "negative",
                                               PE_1 > 0 ~ "positive",
                                               PE_1 == 0 ~ "zero"), 
                          PE_1_mag = abs(PE_1),
                          PE_2_val = case_when(PE_2 < 0 ~ "negative",
                                               PE_2 > 0 ~ "positive",
                                               PE_2 == 0 ~ "zero"),
                          PE_2_mag = abs(PE_2),
                          EVPE_val = case_when(EVPE < 0 ~ "negative",
                                               EVPE > 0 ~ "positive",
                                               EVPE == 0 ~ "zero"),
                          EVPE_mag = abs(EVPE)
                    )
```

```{r}
df_collapsed_senti_score <- df_senti_full %>%
  dplyr::group_by(ID, exam_num, ResponseNumber) %>%
  group_modify(~ collapse_text_by_label(
    label_api_text = .x$label_api,
    sentiment = .x$api_val,
    intensity = .x$api_intensity)) %>%
  ungroup()

df_collapsed_senti_score <- df_collapsed_senti_score %>% relocate(exam_num, .after = ID) %>% arrange(ID, exam_num, ResponseNumber)

df_pre_post_collapsed <- df_collapsed_senti_score %>% dplyr::group_by(ID, exam_num, ResponseNumber) %>%
  dplyr::mutate(prev_senti = lag(score_avg),
         post_senti = lead(score_avg),
         prev_peak = lag(score_peak),
         post_peak = lead(score_peak),
         prev_end = lag(score_end),
         post_end = lead(score_end),
         prev_type = lag(collapsed_text_type),
         post_type = lead(collapsed_text_type),
         prev_block_id = lag(block_id),
         post_block_id = lead(collapsed_text_type),
         pre_post_avg = post_senti-prev_senti,
         pre_post_peak = post_peak-prev_peak,
         pre_post_end = post_end-prev_end
      ) %>%
  ungroup()


write.csv(df_pre_post_collapsed, "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/scripts/pre_post_collapsed_senti_v5.csv", row.names = FALSE) 

df_pre_post_collapsed_reg <- df_pre_post_collapsed %>% filter(collapsed_text_type == "Regulation")
```

```{r}
df_pre_post_collapsed_reg_exam <- df_pre_post_collapsed_reg %>% dplyr::group_by(ID, exam_num) %>% summarise(
  pre_post_avg = mean(pre_post_avg, na.rm = TRUE),
  pre_post_peak = max(pre_post_peak, na.rm = TRUE),
  pre_post_end = last(pre_post_end, na.rm = TRUE))

```

```{r}
df_collapsed_senti_score <- df_collapsed_senti_score %>% dplyr::group_by(ID, exam_num) %>% dplyr::mutate(
  exam_avg = mean(score_avg),
  exam_peak = max(score_peak),
  exam_end = last(score_end)
) %>% ungroup()
```

```{r}
df_collapsed_senti_score_exam <- df_collapsed_senti_score %>% select(ID, exam_num, exam_avg, exam_peak, exam_end) %>% unique()
# merge w/ AMI data
df_senti_ami_exam_tmp <- inner_join(df_ami_senti,df_collapsed_senti_score_exam, by = c("ID", "exam_num"))
df_senti_ami_exam <- df_senti_ami_exam_tmp %>% dplyr::rename(ami_val = valence, ami_int = intensity, ami_senti = score)
```

```{r}
df_pre_post_ami_reg_exam <- inner_join(df_senti_ami_exam, df_pre_post_collapsed_reg_exam, by = c("ID", "exam_num"))
df_pre_post_ami_reg_exam_PE <- inner_join(df_pre_post_ami_reg_exam, df_PE, by = c("ID","exam_num"))
```

```{r}
m1_ami_senti_exam_avg <- lmer(ami_senti ~ exam_avg + (1|ID) + (1|exam_num), data = df_senti_ami_exam)
summary(m1_ami_senti_exam_avg)
```
```{r}
pp_check(m1_ami_senti_exam_avg)
```
```{r}
ggplot(df_senti_ami_exam, aes(x = exam_avg, y = ami_senti)) +geom_point()+ 
      geom_smooth(method=lm, colour="black", size = 1.25, se=TRUE )
```


```{r}
hist(df_senti_ami_exam$ami_senti)

```

```{r}
m1_ami_senti_exam_peak <- lmer(ami_senti ~ exam_peak + (1|ID) + (1|exam_num), data = df_senti_ami_exam)
summary(m1_ami_senti_exam_peak)
```
```{r}
pp_check(m1_ami_senti_exam_peak)
```


```{r}
m1_ami_senti_exam_end <- lmer(ami_senti ~ exam_end + (1|ID) + (1|exam_num), data = df_senti_ami_exam)
summary(m1_ami_senti_exam_end)
```
```{r}
pp_check(m1_ami_senti_exam_end)
```
```{r}
mix <- mixture(gaussian(), gaussian())
fit_ami_senti_exam_end_mix <- brm(ami_senti ~ exam_end + (1|ID),
               data = df_senti_ami_exam,
               family = mix)
summary(fit_ami_senti_exam_end_mix)
pp_check(fit_ami_senti_exam_end_mix)
```
```{r}
summary(fit_mix)
post <- posterior_samples(fit_mix)

# Plot mixture components using theta1 / theta2 as weights
ggplot(post, aes(x = Intercept_mu1, y = Intercept_mu2)) +
  geom_point(alpha = 0.1) +
  labs(title = "Posterior samples of component means")
```
```{r}
mcmc_areas(post, regex_pars = "mu[12]_exam_end")
```
```{r}
pp_check(fit_mix)
```



```{r}
plot(fit_mix, type = "acf")
```

```{r}
mix <- mixture(gaussian(), gaussian())
fit_ami_senti_exam_avg_mix <- brm(ami_senti ~ exam_avg + (1|ID) +(1|exam_num),
               data = df_senti_ami_exam,
               family = mix)
summary(fit_ami_senti_exam_avg_mix)
pp_check(fit_ami_senti_exam_avg_mix)
```
```{r}
plot(fit_ami_senti_exam_avg_mix, type = "acf"
     )
```
# Prior: senti vs. exam_avg
```{r}
# prior setup
mix_fam <- mixture(gaussian, gaussian)
# check the parameter names to set priors
get_prior(
  ami_senti ~ exam_avg + (1|ID) + (1|exam_num),
  family = mix_fam,
  data   = df_senti_ami_exam
)

pri_mix <- c(
  # Means of the two components (on the standardized y scale)
  prior(normal(-0.7, 0.3), class = "Intercept", dpar = "mu1"),
  prior(normal( 0.35, 0.3), class = "Intercept", dpar = "mu2"),
  prior(normal(0, 0.4),     class = "b",        dpar = "mu1"),
  prior(normal(0, 0.4),     class = "b",        dpar = "mu2"),

  # Residual SDs for each component
  prior(student_t(3, 0, 0.5), class = "sigma1"),
  prior(student_t(3, 0, 0.5), class = "sigma2"),

  # Mixture weight prior (Dirichlet over two comps; Beta(2,2) symmetric)
  prior(dirichlet(2, 2), class = "theta")
)

fit_ami_senti_exam_avg_mix <- brm(ami_senti ~ exam_avg + (1|ID) +(1|exam_num),
               data = df_senti_ami_exam,
               family = mix_fam,
              prior   = pri_mix,
  chains  = 4, iter = 2000, warmup = 1000, seed = 123,
  control = list(adapt_delta = 0.99, max_treedepth = 15)
)
summary(fit_ami_senti_exam_avg_mix)
pp_check(fit_ami_senti_exam_avg_mix)
```
```{r}
pp_check(fit_ami_senti_exam_avg_mix)
```

```{r}
plot(fit_ami_senti_exam_avg_mix, type = "acf"
     )
```




```{r}
df_senti_ami_exam_PE <- inner_join(df_senti_ami_exam,df_PE, by = c("ID","exam_num"))
```
### ami_senti vs. PE_1
```{r}
m2_ami_senti_PE1 <- lmer(ami_senti ~ PE_1 + 1+ (1|ID) + (1|exam_num), data = df_senti_ami_exam_PE)
summary(m2_ami_senti_PE1)
```
```{r}
pp_check(m2_ami_senti_PE1)
```
```{r}
m2_ami_senti_PE2 <- lmer(ami_senti ~ PE_2 + 1+ (1|ID) + (1|exam_num), data = df_senti_ami_exam_PE)
summary(m2_ami_senti_PE2)
```

```{r}
m2_ami_senti_EVPE <- lmer(ami_senti ~ EVPE + 1+ (1|ID) + (1|exam_num), data = df_senti_ami_exam_PE)
summary(m2_ami_senti_EVPE)
```
### ami_senti vs. PE_1_val
```{r}
m2_ami_senti_PE1_val <- lmer(ami_senti ~ PE_1_val + 1+ (1|ID) + (1|exam_num), data = df_senti_ami_exam_PE)
summary(m2_ami_senti_PE1_val)
```

```{r}
pp_check(m2_ami_senti_PE1_val)
```


# AMI_senti vs. pre_post_reg
```{r}
m1_ami_senti_pre_post_reg <- lmer(ami_senti ~ pre_post_avg + 1+ (1|ID) + (1|exam_num), data = df_pre_post_ami_reg_exam_PE)
summary(m1_ami_senti_pre_post_reg)
```
```{r}
pp_check(m1_ami_senti_pre_post_reg)
```
```{r}
m1_ami_senti_pre_post_reg_exam <- lmer(ami_senti ~ exam_avg + pre_post_avg + exam_avg*pre_post_avg + (1|ID) + (1|exam_num), data = df_pre_post_ami_reg_exam_PE)
summary(m1_ami_senti_pre_post_reg_exam)
```
```{r}
pp_check(m1_ami_senti_pre_post_reg_exam)
```
## brms mix_gaussian()
```{r}
brm_ami_senti_pre_post_exam_avg_mix <- brm(ami_senti ~ exam_avg + pre_post_avg + (1|ID) +(1|exam_num),
               data = df_pre_post_ami_reg_exam_PE,
               family = mix_fam,
  chains  = 4, iter = 2000, warmup = 1000, seed = 123,
  init = 0)

summary(brm_ami_senti_pre_post_exam_avg_mix)
pp_check(brm_ami_senti_pre_post_exam_avg_mix)
```

```{r}
plot(brm_ami_senti_pre_post_exam_avg_mix, type = "acf")
```
```{r}
pri_mix <- c(
  # Means of the two components (on the standardized y scale)
  prior(normal(-0.7, 15), class = "Intercept", dpar = "mu1"),
  prior(normal( 0.2, 7), class = "Intercept", dpar = "mu2"),
  prior(normal(0, 0.4),     class = "b",        dpar = "mu1"),
  prior(normal(0, 0.4),     class = "b",        dpar = "mu2"),

  # Residual SDs for each component
  prior(student_t(3, 0, 0.5), class = "sigma1"),
  prior(student_t(3, 0, 0.5), class = "sigma2"),

  # Mixture weight prior (Dirichlet over two comps; Beta(2,2) symmetric)
  prior(dirichlet(0.75, 1.5), class = "theta")
)

prior_model <- brm(
  formula = ami_senti ~ exam_avg + pre_post_avg + (1|ID) +(1|exam_num),
  data = df_pre_post_ami_reg_exam_PE,
  prior = pri_mix,
  sample_prior = "only",
  family = mix_fam
)
pp_check(prior_model)
```

```{r}
pp_check(prior_model)
```

# word_count vs. PE

```{r}
df_pre_post_ami_exam <- inner_join(df_senti_ami_exam, df_pre_post_collapsed, by = c("ID", "exam_num"))
df_pre_post_ami_exam_PE <- inner_join(df_pre_post_ami_exam, df_PE, by = c("ID","exam_num"))
```

```{r}
for (i in (1:nrow(df_pre_post_ami_exam_PE))){
  phrase = df_pre_post_ami_exam_PE$text[i]
  df_pre_post_ami_exam_PE$word_count[i] <- str_count(phrase,'[\\w\']+')
}
```

```{r}
m1_mem_length_PE_1 <- lmer(word_count ~ PE_1+(1|ID)+(1|exam_num), data = df_pre_post_ami_exam_PE)
summary(m1_mem_length_PE_1)
pp_check(m1_mem_length_PE_1)
```
```{r}
m1_mem_length_PE_1_exam_avg <- lmer(word_count ~ PE_1+exam_avg+(1|ID)+(1|exam_num), data = df_pre_post_ami_exam_PE)
summary(m1_mem_length_PE_1_exam_avg)
pp_check(m1_mem_length_PE_1_exam_avg)
```

```{r}
m1_mem_length_PE_1_exam_avg_int <- lmer(word_count ~ PE_1+exam_avg+PE_1*exam_avg+(1|ID)+(1|exam_num), data = df_pre_post_ami_exam_PE)
summary(m1_mem_length_PE_1_exam_avg_int)
pp_check(m1_mem_length_PE_1_exam_avg_int)
```
```{r}
plot_model(m1_mem_length_PE_1_exam_avg_int, type = "int", terms = c(exam_avg, PE_1), ci.lvl = 0.95)
```
```{r}
m1_mem_length_PE_2_exam_avg_int <- lmer(word_count ~ PE_2+exam_avg+PE_2*exam_avg+(1|ID)+(1|exam_num), data = df_pre_post_ami_exam_PE)
summary(m1_mem_length_PE_2_exam_avg_int)
pp_check(m1_mem_length_PE_2_exam_avg_int)
```
```{r}
plot_model(m1_mem_length_PE_2_exam_avg_int, type = "int", terms = c(exam_avg, PE_2), ci.lvl = 0.95)
```

```{r}
m1_mem_length_EVPE_exam_avg_int <- lmer(word_count ~ EVPE+exam_avg+EVPE*exam_avg+(1|ID)+(1|exam_num), data = df_pre_post_ami_exam_PE)
summary(m1_mem_length_EVPE_exam_avg_int)
pp_check(m1_mem_length_EVPE_exam_avg_int)
```

```{r}
plot_model(m1_mem_length_EVPE_exam_avg_int, type = "int", terms = c(exam_avg, EVPE), ci.lvl = 0.95)
```

```{r}
exam_avg_PE_1 <- lmer(ami_senti ~ exam_avg +(1|ID), data = df_pre_post_ami_exam_PE)
summary(exam_avg_PE_1)
pp_check(exam_avg_PE_1)
```
```{r}
plot_model(exam_avg_PE_1)
```

```{r}
m1_ami_sent_PE_1 <- lmer(ami_senti ~ PE_1+(1|ID)+(1|exam_num), data = df_pre_post_ami_exam_PE)
summary(m1_ami_sent_PE_1)
pp_check(m1_ami_sent_PE_1)
```
# word_count vs. ami_senti
```{r}
m1_ami_senti_word_count <- lmer(word_count ~ ami_senti + (1|ID) + (1|exam_num), data = df_pre_post_ami_exam_PE )

summary(m1_ami_senti_word_count)

pp_check(m1_ami_senti_word_count)
```

# ami_senti vs. reg_prop
```{r}
df_no_na <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/processed/premedEMA_API_F24_conf_processed.csv")

df_no_na <- df_no_na %>% mutate(label_api_text = case_when(label_api == -1 ~ "Expression",
                                                           label_api == 0 ~ "Neither",
                                                           label_api == 1 ~ "Regulation"))
df_select <- df_no_na %>% select(ID, exam_num, ResponseNumber, exam_resp, text_phrase, label_api_text, label_api, word_count)
df_by_sub_exam <- df_select %>% dplyr::count(ID, exam_num, label_api_text) %>% pivot_wider(names_from = label_api_text, values_from = n, values_fill = 0)

df_by_sub_exam <- df_by_sub_exam %>% dplyr::group_by(ID, exam_num) %>% mutate(total = Expression + Neither + Regulation,
                                  exp_ratio = Expression/total,
                                  nei_ratio = Neither/total,
                                  reg_ratio = Regulation/total
                                              )

# The total word count of each label, per exam
df_by_sub_exam_word_count <- df_select %>% group_by(ID, exam_num, label_api_text) %>% summarise(sum_word_count = sum(word_count), .groups = "drop")

# The wide format
df_by_sub_exam_word_count_wide <- df_by_sub_exam_word_count %>% group_by(ID, exam_num) %>% pivot_wider(names_from = label_api_text, values_from = sum_word_count)

df_by_sub_exam_word_count_wide <- df_by_sub_exam_word_count_wide %>% dplyr::mutate(across(where(is.numeric), ~replace(.,is.na(.), 0)))

df_by_sub_exam_word_count_wide <- df_by_sub_exam_word_count_wide %>% dplyr::group_by(ID, exam_num) %>%
  dplyr::mutate(exam_total_word = sum(Expression + Regulation + Neither),
         exp_word_ratio = Expression/exam_total_word,
         reg_word_ratio = Regulation/exam_total_word,
         nei_word_ratio = Neither/exam_total_word)
```

```{r}
df_ami_pre_post_ratio_PE_tmp <- inner_join(df_pre_post_ami_exam_PE, df_by_sub_exam, by = c("ID", "exam_num"))
df_ami_senti_ratio_PE <- inner_join(df_senti_ami_exam_PE, df_by_sub_exam, by = c("ID", "exam_num"))

df_ami_senti_word_PE_tmp <- inner_join(df_senti_ami_exam_PE, df_by_sub_exam_word_count_wide, by = c("ID", "exam_num"))

# remove text = NaN
df_ami_senti_word_PE <- df_ami_senti_word_PE_tmp %>% filter(df_ami_senti_word_PE_tmp$text != "")
```

```{r}
ggplot(data = df_ami_ratio_PE, aes(x = reg_ratio, y = ami_senti)) + geom_point()
```

```{r}
ggplot(data = df_ami_ratio_PE, aes(x = PE_1, y = ami_senti)) + geom_point()
```
```{r}
ggplot(data = df_ami_senti_ratio_PE, aes(x = PE_2, y = ami_senti)) + geom_point()
```

```{r}
ggplot(data = df_ami_senti_ratio_PE, aes(x = EVPE, y = ami_senti)) + geom_point()
```
```{r}
m1_ami_senti_reg_ratio <- lmer(ami_senti ~ reg_ratio + (1|ID) + (1|exam_num), data = df_ami_senti_ratio_PE)
summary(m1_ami_senti_reg_ratio)

pp_check(m1_ami_senti_reg_ratio)
```

```{r}
m1_ami_senti_reg_ratio_PE_1 <- lmer(ami_senti ~ reg_ratio + PE_1 + reg_ratio*PE_1 + (1|ID) + (1|exam_num), data = df_ami_ratio_PE)
summary(m1_ami_senti_reg_ratio_PE_1)

pp_check(m1_ami_senti_reg_ratio_PE_1)
```

```{r}
hist(df_ami_senti_ratio_PE$ami_senti)
```
# Ami_senti_group
## Data preprop
```{r}
df_ami_senti_ratio_PE
df_ami_senti_ratio_PE <- df_ami_senti_ratio_PE %>% mutate(ami_senti_group = cut(ami_senti, breaks = c(-1,-0.25,0.5,1.0), labels = c("neg","neu","pos")))

ggplot(df_ami_senti_ratio_PE, aes(x = ami_senti_group)) +
    geom_bar() +
    labs(title = "Frequency Plot of ami_senti group",
         x = "Ami_senti group",
         y = "Frequency")


```

### brm: multi_ordinal
```{r}
ordered_factor <- c("neg", "neu","pos")

df_ami_senti_ratio_PE$ami_senti_group <- ordered(df_ami_senti_ratio_PE$ami_senti_group, levels = c("neg","neu","pos"))
```

```{r}
m1_ordinal_ami_senti_PE_1 <- brm(ami_senti_group ~ PE_1 + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_ratio_PE)

summary(m1_ordinal_ami_senti_PE_1)
pp_check(m1_ordinal_ami_senti_PE_1)
```
```{r}
plot(conditional_effects(m1_ordinal_ami_senti_PE_1))
```

```{r}
m1_ordinal_ami_senti_PE_2 <- brm(ami_senti_group ~ PE_2 + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_ratio_PE)

summary(m1_ordinal_ami_senti_PE_2)
pp_check(m1_ordinal_ami_senti_PE_2)
```

```{r}
plot(conditional_effects(m1_ordinal_ami_senti_PE_2))
```


```{r}
m1_ordinal_ami_senti_EVPE <- brm(ami_senti_group ~ EVPE + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_ratio_PE)

summary(m1_ordinal_ami_senti_EVPE)
pp_check(m1_ordinal_ami_senti_EVPE)
```
```{r}
plot(conditional_effects(m1_ordinal_ami_senti_EVPE))
```
####Plotting
```{r}
# Generate conditional effects for each model
eff_EVPE <- conditional_effects(m1_ordinal_ami_senti_EVPE, effects = "EVPE")$EVPE %>%
  as_tibble() %>% mutate(Predictor = "EVPE")

eff_PE1 <- conditional_effects(m1_ordinal_ami_senti_PE_1, effects = "PE_1")$PE_1 %>%
  as_tibble() %>% mutate(Predictor = "PE_1")

eff_PE2 <- conditional_effects(m1_ordinal_ami_senti_PE_2, effects = "PE_2")$PE_2 %>%
  as_tibble() %>% mutate(Predictor = "PE_2")

# Combine all into one dataframe
eff_all <- bind_rows(eff_EVPE, eff_PE1, eff_PE2)
```
```{r}
PE1_AMI_senti <- ggplot(eff_PE1, aes(x = effect1__, y = estimate__)) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.15, color = NA) +
  labs(
    title = "PE1 effect on autobiographical memory sentiment",
    x = "Prediction error 1",
    y = "Predicted ordered logit (AMI sentiment)",
    color = "Predictor", fill = "Predictor"
  ) +
  theme_classic(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "top"
  )
PE1_AMI_senti
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/PE1_AMI_senti.png",plot = PE1_AMI_senti, width = 6, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/PE1_AMI_senti.pdf",plot = PE1_AMI_senti, width = 6, heigh = 4, dpi = 300)
```
```{r}
PE2_AMI_senti <- ggplot(eff_PE2, aes(x = effect1__, y = estimate__)) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.15, color = NA) +
  labs(
    title = "PE2 effect on autobiographical memory sentiment",
    x = "Prediction error 2",
    y = "Predicted ordered logit (AMI sentiment)",
    color = "Predictor", fill = "Predictor"
  ) +
  theme_classic(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "top"
  )
PE2_AMI_senti
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/PE2_AMI_senti.png",plot = PE2_AMI_senti, width = 6, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/PE2_AMI_senti.pdf",plot = PE2_AMI_senti, width = 6, heigh = 4, dpi = 300)
```
```{r}
EVPE_AMI_senti <- ggplot(eff_EVPE, aes(x = effect1__, y = estimate__)) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.15, color = NA) +
  labs(
    title = "EVPE effect on autobiographical memory sentiment",
    x = "EVPE",
    y = "Predicted ordered logit (AMI sentiment)",
    color = "Predictor", fill = "Predictor"
  ) +
  theme_classic(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "top"
  )
EVPE_AMI_senti
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/EVPE_AMI_senti.png",plot = EVPE_AMI_senti, width = 6, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/EVPE_AMI_senti.pdf",plot = EVPE_AMI_senti, width = 6, heigh = 4, dpi = 300)
```
```{r}
three_PEs_AMI_senti <- ggplot(eff_all, aes(x = effect1__, y = estimate__, color = Predictor, fill = Predictor)) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.15, color = NA) +
  labs(
    title = "PE predictors' effect on autobiographical memory sentiment",
    x = "Prediction Error (PE value)",
    y = "Predicted ordered logit (AMI sentiment)",
    color = "Predictor", fill = "Predictor"
  ) +
  theme_classic(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
three_PEs_AMI_senti
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/three_PEs_AMI_senti.png",plot = three_PEs_AMI_senti, width = 6, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/three_PEs_AMI_senti.pdf",plot = three_PEs_AMI_senti, width = 6, heigh = 4, dpi = 300)
```

### ami_senti vs. reg_prop
```{r}
m2_ordinal_ami_senti_reg <- brm(ami_senti_group ~ reg_ratio + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_ratio_PE)

summary(m2_ordinal_ami_senti_reg)
pp_check(m2_ordinal_ami_senti_reg)
```
```{r}
m2_ordinal_ami_senti_reg_EVPE <- brm(ami_senti_group ~ reg_ratio + EVPE + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_ratio_PE)

summary(m2_ordinal_ami_senti_reg_EVPE)
pp_check(m2_ordinal_ami_senti_reg_EVPE)
```

```{r}
m2_ordinal_ami_senti_reg_EVPE_val_int <- brm(ami_senti_group ~ EVPE_val*reg_ratio + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_ratio_PE)

summary(m2_ordinal_ami_senti_reg_EVPE_val_int)
pp_check(m2_ordinal_ami_senti_reg_EVPE_val_int)
```

```{r}
m3_ordinal_ami_senti_reg_EVPE_val_add <- brm(ami_senti_group ~ EVPE_val+reg_ratio + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_ratio_PE)

summary(m3_ordinal_ami_senti_reg_EVPE_val_add)
pp_check(m3_ordinal_ami_senti_reg_EVPE_val_add)
```
### final: ami_senti vs. reg_prop*PE
```{r}
m2_ordinal_ami_senti_reg_EVPE_val_int <- brm(ami_senti_group ~ EVPE_val*reg_ratio + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_ratio_PE)

summary(m2_ordinal_ami_senti_reg_EVPE_val_int)
pp_check(m2_ordinal_ami_senti_reg_EVPE_val_int)
```
```{r}
ami_senti_reg_EVPE_val_int_plotting <- conditional_effects(m2_ordinal_ami_senti_reg_EVPE_val_int)

ami_senti_reg_EVPE_val_int_plot_list <- plot(ami_senti_reg_EVPE_val_int_plotting, plot = FALSE)
ami_senti_reg_EVPE_val_int_plot_main <- ami_senti_reg_EVPE_val_int_plot_list[[3]]

```
### Model comparison
```{r}
molde0_senti_reg_word_ratio_EVPE_val <-  add_criterion(m2_ordinal_ami_senti_reg_word_ratio, "loo")
model1_senti_reg_word_ratio_EVPE_val_add <- add_criterion(m3_ordinal_ami_senti_reg_EVPE_val_add, "loo")
model2_senti_reg_word_ratio_EVPE_val_int <- add_criterion(m2_ordinal_ami_senti_reg_EVPE_val_int, "loo")

model_comparison_senti_reg_EVPE_val <- loo_compare(molde0_senti_reg_word_ratio_EVPE_val,model1_senti_reg_word_ratio_EVPE_val_add,model2_senti_reg_word_ratio_EVPE_val_int, criterion = "loo")
print(model_comparison_senti_reg_EVPE_val , simplify = FALSE)
```
#### Final
```{r}
ami_senti_reg_EVPE_val_int_plot_main_fn <- ami_senti_reg_EVPE_val_int_plot_main +
  labs(
    title = "ER and Autobiographical Memory by PE Valence",
    x = "The ratio of regulation-related language",
    y = "Autobiographic memory sentiment",
    color = "PE valence",
    fill = "PE valence") +
  theme_classic() +
  theme(
    plot.caption = element_text(
      size = 10,
      hjust = 0
    ), plot.title = element_text(size = 19),
    axis.title = element_text(size = 17),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 14),    # Legend Title
    legend.text = element_text(size = 12))
ami_senti_reg_EVPE_val_int_plot_main_fn
ggsave(file = "/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/final plots/interaction_EVPE_val_reg_ratio_AMI_senti.png",plot =ami_senti_reg_EVPE_val_int_plot_main_fn, width = 10, heigh = 7, dpi = 300)

ggsave(file = "/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/final plots/interaction_EVPE_val_reg_ratio_AMI_senti.pdf",plot = ami_senti_reg_EVPE_val_int_plot_main_fn, width = 10, heigh = 7, dpi = 300)

ggsave(file = "/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/final plots/interaction_EVPE_val_reg_ratio_AMI_senti.eps",plot = ami_senti_reg_EVPE_val_int_plot_main_fn, width = 10, heigh = 7, dpi = 300)
```

```{r}
m2_ordinal_ami_senti_reg_EVPE_int <- brm(ami_senti_group ~ EVPE + reg_ratio + EVPE*reg_ratio + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_ratio_PE)

summary(m2_ordinal_ami_senti_reg_EVPE_int)
pp_check(m2_ordinal_ami_senti_reg_EVPE)
```
```{r}
plot(conditional_effects(m2_ordinal_ami_senti_reg_EVPE_int))
```
```{r}
marginal_effects(m2_ordinal_ami_senti_reg_EVPE)
```

### model comparison
```{r}
loo_reg <- loo(m2_ordinal_ami_senti_reg)
loo_EVPE <- loo(m2_ordinal_ami_senti_reg_EVPE)
loo_reg_EVPE_int <- loo(m2_ordinal_ami_senti_reg_EVPE_int)
```
```{r}
loo_reg
loo_EVPE
loo_reg_EVPE_int
```


```{r}
loo_compare(loo_reg, loo_EVPE, loo_reg_EVPE_int)
```

```{r}
m2_ordinal_ami_senti_reg_PE_2 <- brm(ami_senti_group ~ PE_2 + reg_ratio + PE_2*reg_ratio + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_ratio_PE)

summary(m2_ordinal_ami_senti_reg_PE_2)
pp_check(m2_ordinal_ami_senti_reg_PE_2)
```
```{r}
plot(conditional_effects(m2_ordinal_ami_senti_reg_PE_2))
```

```{r}
m2_ordinal_ami_senti_reg_PE_1 <- brm(ami_senti_group ~ PE_1 + reg_ratio + PE_1*reg_ratio + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_ratio_PE)

summary(m2_ordinal_ami_senti_reg_PE_1)
pp_check(m2_ordinal_ami_senti_reg_PE_1)
```
```{r}
plot(conditional_effects(m2_ordinal_ami_senti_reg_PE_1))
```


### ami_senti vs reg_prop*PE*ema_senti
```{r}
m2_ordinal_ami_senti_reg_EVPE_avg <- brm(ami_senti_group ~ EVPE + reg_ratio + exam_avg + EVPE*reg_ratio*exam_avg + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_ratio_PE)

summary(m2_ordinal_ami_senti_reg_EVPE_avg)
pp_check(m2_ordinal_ami_senti_reg_EVPE_avg)
```
```{r}
plot(conditional_effects(m2_ordinal_ami_senti_reg_EVPE_avg))
```

### ami_senti vs. reg_prop*ema_senti
```{r}
m3_ordinal_ami_senti_reg_avg <- brm(ami_senti_group ~ reg_ratio * exam_avg + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_ratio_PE)

summary(m3_ordinal_ami_senti_reg_avg)
pp_check(m3_ordinal_ami_senti_reg_avg)
```
```{r}
plot(conditional_effects(m3_ordinal_ami_senti_reg_avg))
```
###ami_senti vs. pre_post_reg
```{r}
df_pre_post_ami_reg_exam_PE <- df_pre_post_ami_reg_exam_PE %>% mutate(ami_senti_group = cut(ami_senti, breaks = c(-1,-0.25,0.5,1.0), labels = c("neg","neu","pos")))
df_pre_post_ami_reg_exam_PE$ami_senti_group <- ordered(df_pre_post_ami_reg_exam_PE$ami_senti_group, levels = c("neg","neu","pos"))


df_pre_post_ami_reg_exam_PE <- df_pre_post_ami_reg_exam_PE %>% mutate(pre_post_val = case_when(pre_post_avg > 0 ~ "up",
                                                                        pre_post_avg == 0 ~ "no_change",
                                                                        pre_post_avg < 0 ~ "down"))


df_pre_post_ami_reg_exam_PE$pre_post_val <- ordered(df_pre_post_ami_reg_exam_PE$pre_post_val, levels = c("down", "no_change","up"))
```

```{r}
m3_ordinal_ami_senti_pre_post_reg <- brm(ami_senti_group ~ pre_post_avg * exam_avg + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_pre_post_ami_reg_exam_PE)

summary(m3_ordinal_ami_senti_pre_post_reg)
pp_check(m3_ordinal_ami_senti_pre_post_reg)
```
```{r}
plot(conditional_effects(m3_ordinal_ami_senti_pre_post_reg))
```
```{r}
df_ami_ratio_PE <- df_ami_ratio_PE %>% mutate(pre_post_val = case_when(pre_post_avg > 0 ~ "up",
                                                                        pre_post_avg == 0 ~ "no_change",
                                                                        pre_post_avg < 0 ~ "down"))


df_ami_ratio_PE$pre_post_val <- ordered(df_ami_ratio_PE$pre_post_val, levels = c("down", "no_change","up"))

```
```{r}
m3_ordinal_ami_senti_pre_post_reg_val <- brm(ami_senti_group ~ pre_post_val * score_avg + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_ratio_PE)

summary(m3_ordinal_ami_senti_pre_post_reg_val)
pp_check(m3_ordinal_ami_senti_pre_post_reg_val)
```
```{r}
plot(conditional_effects(m3_ordinal_ami_senti_pre_post_reg_val))
```

### ami_senti vs. reg_occur*PE
```{r}
# if regulation occurr
df_ami_senti_ratio_PE <- df_ami_senti_ratio_PE %>% mutate(reg_check = ifelse(Regulation >0, 1, 0))
df_ami_senti_ratio_PE$reg_check <- as.factor(df_ami_senti_ratio_PE$reg_check)
df_ami_senti_ratio_PE$reg_check <- ordered(df_ami_senti_ratio_PE$reg_check, levels = c(0,1))
```
```{r}
m4_ordinal_ami_senti_reg_occur_PE_1 <- brm(ami_senti_group ~ reg_check * PE_1 + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_ratio_PE)
summary(m4_ordinal_ami_senti_reg_occur_PE_1)
pp_check(m4_ordinal_ami_senti_reg_occur_PE_1)
```
```{r}
plot(conditional_effects(m4_ordinal_ami_senti_reg_occur_PE_1))
```

```{r}
m4_ordinal_ami_senti_reg_occur_PE_2 <- brm(ami_senti_group ~ reg_check * PE_2 + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_ratio_PE)
summary(m4_ordinal_ami_senti_reg_occur_PE_2)
pp_check(m4_ordinal_ami_senti_reg_occur_PE_2)
```

```{r}
plot(conditional_effects(m4_ordinal_ami_senti_reg_occur_PE_2))
```

```{r}
m4_ordinal_ami_senti_reg_occur_EVPE <- brm(ami_senti_group ~ reg_check * EVPE + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_ratio_PE)
summary(m4_ordinal_ami_senti_reg_occur_EVPE)
pp_check(m4_ordinal_ami_senti_reg_occur_EVPE)
```
```{r}
plot(conditional_effects(m4_ordinal_ami_senti_reg_occur_EVPE))
```

### ami_senti vs. reg_word_count*PE +total_word
```{r}
m1_ordinal_ami_senti_reg_word_EVPE <- brm(ami_senti_group ~ Regulation * EVPE + exam_total_word + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE)
summary(m1_ordinal_ami_senti_reg_word_EVPE)
pp_check(m1_ordinal_ami_senti_reg_word_EVPE)
```
```{r}
plot(conditional_effects(m1_ordinal_ami_senti_reg_word_EVPE))
```
```{r}
m1_ordinal_ami_senti_reg_word_EVPE_val <- brm(ami_senti_group ~ Regulation * EVPE_val + exam_total_word + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE)
summary(m1_ordinal_ami_senti_reg_word_EVPE_val)
pp_check(m1_ordinal_ami_senti_reg_word_EVPE_val)
```
```{r}
plot(conditional_effects(m1_ordinal_ami_senti_reg_word_EVPE_val))
```

```{r}
m1_ordinal_ami_senti_reg_word_PE_1 <- brm(ami_senti_group ~ Regulation * PE_1 + exam_total_word + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE)
summary(m1_ordinal_ami_senti_reg_word_PE_1)
pp_check(m1_ordinal_ami_senti_reg_word_PE_1)
```
```{r}
plot(conditional_effects(m1_ordinal_ami_senti_reg_word_PE_1))
```

```{r}
m1_ordinal_ami_senti_reg_word_PE_2 <- brm(ami_senti_group ~ Regulation * PE_2 + exam_total_word + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE)
summary(m1_ordinal_ami_senti_reg_word_PE_2)
pp_check(m1_ordinal_ami_senti_reg_word_PE_2)
```
```{r}
plot(conditional_effects(m1_ordinal_ami_senti_reg_word_PE_2))
```
###ami_senti vs. reg_word_ratio*PE
```{r}
df_ami_senti_word_PE <- df_ami_senti_word_PE %>% mutate(ami_senti_group = cut(ami_senti, breaks = c(-1,-0.25,0.5,1.0), labels = c("neg","neu","pos")))

ordered_factor <- c("neg", "neu","pos")

df_ami_senti_word_PE$ami_senti_group <- ordered(df_ami_senti_word_PE$ami_senti_group, levels = c("neg","neu","pos"))
```

```{r}
m2_ordinal_ami_senti_reg_word_ratio_EVPE <- brm(ami_senti_group ~ reg_word_ratio * EVPE + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE)
summary(m2_ordinal_ami_senti_reg_word_ratio_EVPE)
pp_check(m2_ordinal_ami_senti_reg_word_ratio_EVPE)
```
```{r}
plot(conditional_effects(m2_ordinal_ami_senti_reg_word_ratio_EVPE))
```

```{r}
m2_ordinal_ami_senti_reg_word_ratio_EVPE_val <- brm(ami_senti_group ~ reg_word_ratio * EVPE_val + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE)
summary(m2_ordinal_ami_senti_reg_word_ratio_EVPE_val)
pp_check(m2_ordinal_ami_senti_reg_word_ratio_EVPE_val)
```
```{r}
plot(conditional_effects(m2_ordinal_ami_senti_reg_word_ratio_EVPE_val))
```
####Plotting
```{r}
ami_senti_EVPE_val_int_plotting <- conditional_effects(m2_ordinal_ami_senti_reg_word_ratio_EVPE_val)

ami_senti_EVPE_val_int_plot_list <- plot(ami_senti_EVPE_val_int_plotting, plot = FALSE)
ami_senti_EVPE_val_int_plot_main <- ami_senti_EVPE_val_int_plot_list[[3]]
```

#### Model_comparison

```{r}
m2_ordinal_ami_senti_reg_word_ratio <- brm(ami_senti_group ~ reg_word_ratio + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE)
summary(m2_ordinal_ami_senti_reg_word_ratio)
pp_check(m2_ordinal_ami_senti_reg_word_ratio)
```
```{r}
m2_ordinal_ami_senti_reg_word_ratio_EVPE_add <- brm(ami_senti_group ~ reg_word_ratio + EVPE_val + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE)
summary(m2_ordinal_ami_senti_reg_word_ratio_EVPE_add)
pp_check(m2_ordinal_ami_senti_reg_word_ratio_EVPE_add)
```

```{r}
molde0_senti_reg_word_ratio_EVPE <-  add_criterion(m2_ordinal_ami_senti_reg_word_ratio, "loo")
model1_senti_reg_word_ratio_EVPE_add <- add_criterion(m2_ordinal_ami_senti_reg_word_ratio_EVPE_add, "loo")
model2_senti_reg_word_ratio_EVPE_int <- add_criterion(m2_ordinal_ami_senti_reg_word_ratio_EVPE_val, "loo")

model_comparison_senti_reg_EVPE <- loo_compare(molde0_senti_reg_word_ratio_EVPE,model1_senti_reg_word_ratio_EVPE_add,model2_senti_reg_word_ratio_EVPE_int, criterion = "loo")
print(model_comparison_senti_reg_EVPE , simplify = FALSE)
```

```{r}
ami_senti_EVPE_val_int_plot_main_fn <- ami_senti_EVPE_val_int_plot_main +
  labs(title = "Interaction effect of EVPE valence and regulation ratio on autobiographical memory sentiment",
    x = "The ratio of regulation-related language",
    y = "Autobiographic memory sentiment",
    color = "EVPE valence",
    fill = "EVPE valence",
    caption = strwrap("This plot shows the interaction effect of EVPE valence and the regulation-lated word ratio on later autobiographical memory sentiment category. For participants who received a higher-than-average grade, higher proportion of regulation in their EMA audio recording is associated with higher probablity to have a more negative AMI memory sentiment, while for participants who received a lower-than-average grade, higher regulation ratio is associated with slightly higher memory sentiment.", width = 130) %>%paste(collapse = "\n"
  )) +
  theme_classic() +
  theme(
    plot.caption = element_text(
      size = 10,
      hjust = 0
    )
  )
ami_senti_EVPE_val_int_plot_main_fn
#ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/interaction_EVPE_val_reg_ratio_AMI_senti.png",plot = ami_senti_EVPE_val_int_plot_main_fn, width = 10, heigh = 7, dpi = 300)

#ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/interaction_EVPE_val_reg_ratio_AMI_senti.pdf",plot = ami_senti_EVPE_val_int_plot_main_fn, width = 10, heigh = 7, dpi = 300)
```
### ami_senti vs. EVPE*reg*GAD

```{r}
df_ami_senti_word_PE_mood <- inner_join(df_ami_senti_word_PE, df_qual, by ="ID")
```

```{r}
m2_ordinal_ami_senti_reg_word_ratio_EVPE_val_gad <- brm(ami_senti_group ~ reg_word_ratio * EVPE_val * GAD_score + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE_mood)
summary(m2_ordinal_ami_senti_reg_word_ratio_EVPE_val_gad)
pp_check(m2_ordinal_ami_senti_reg_word_ratio_EVPE_val_gad)
```

#### Final model: ami_senti ~ reg_word_ratio*EVPE_val*GAD
```{r}
rdm_ordinal_ami_senti_reg_word_ratio <- brm(ami_senti_group ~ reg_word_ratio * EVPE_val + (1 + reg_word_ratio * EVPE_val|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE)
summary(rdm_ordinal_ami_senti_reg_word_ratio)
pp_check(rdm_ordinal_ami_senti_reg_word_ratio)
```



```{r}
m2_ordinal_ami_senti_reg_word_ratio_PE_1 <- brm(ami_senti_group ~ reg_word_ratio * PE_1 + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE)
summary(m2_ordinal_ami_senti_reg_word_ratio_PE_1)
pp_check(m2_ordinal_ami_senti_reg_word_ratio_PE_1)
```
```{r}
plot(conditional_effects(m2_ordinal_ami_senti_reg_word_ratio_PE_1))
```

```{r}
m2_ordinal_ami_senti_reg_word_ratio_PE_2 <- brm(ami_senti_group ~ reg_word_ratio * PE_2 + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE)
summary(m2_ordinal_ami_senti_reg_word_ratio_PE_2)
pp_check(m2_ordinal_ami_senti_reg_word_ratio_PE_2)
```
```{r}
plot(conditional_effects(m2_ordinal_ami_senti_reg_word_ratio_PE_2))
```

```{r}
m1_exam_word_exam_avg <- lmer(exam_total_word ~ exam_avg  + (1|ID) + (1|exam_num),data = df_ami_senti_word_PE)
summary(m1_exam_word_exam_avg)
```
```{r}
pp_check(m1_exam_word_exam_avg)
```

```{r}
m1_reg_word_ratio_exam_avg <- lmer(reg_word_ratio ~ exam_avg + (1|ID) + (1|exam_num),data = df_ami_senti_word_PE)
summary(m1_reg_word_ratio_exam_avg)
pp_check(m1_reg_word_ratio_exam_avg)
```
```{r}
m1_reg_word_exam_avg_only <- lmer(Regulation ~ exam_avg  + (1|ID) + (1|exam_num),data = df_ami_senti_word_PE)
summary(m1_reg_word_exam_avg_only)
pp_check(m1_reg_word_exam_avg_only)
```

```{r}
m1_reg_word_exam_avg <- lmer(Regulation ~ exam_avg + exam_total_word + (1|ID) + (1|exam_num),data = df_ami_senti_word_PE)
summary(m1_reg_word_exam_avg)
pp_check(m1_reg_word_exam_avg)
```


##ami_senti vs regulation and exam_avg

```{r}
m1_ordinal_ami_senti_reg_word <- brm(ami_senti_group ~ Regulation + exam_total_word + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE)
summary(m1_ordinal_ami_senti_reg_word)
pp_check(m1_ordinal_ami_senti_reg_word)
```
```{r}
plot_model(m1_ordinal_ami_senti_reg_word)
```

```{r}
m1_ordinal_ami_senti_reg_word_ratio <- brm(ami_senti_group ~ reg_word_ratio + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE)
summary(m1_ordinal_ami_senti_reg_word_ratio)
pp_check(m1_ordinal_ami_senti_reg_word_ratio)
```
```{r}
plot_model(m1_ordinal_ami_senti_reg_word_ratio)
```

# Individual difference
```{r}
df_qual <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/survey_data_f24/processed/premedEMA_exit_mood_final.csv")
df_neu <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/survey_data_f24/negative_emotionality_scores.csv")
```

```{r}
# model name: m2_ordinal_ami_senti_reg_word_ratio_EVPE_val
```

```{r}
df_ami_senti_word_PE_qual <- inner_join(df_ami_senti_word_PE, df_qual, by = "ID")
df_ami_senti_word_PE_neu <- inner_join(df_ami_senti_word_PE, df_neu, by = "ID")
```
## reg_word_ratio ~ GAD
```{r}
m1_reg_word_ratio_gad <- lmer(reg_word_ratio ~ GAD_score*exam_avg+ + (1|ID) + (1|exam_num),  data = df_ami_senti_word_PE_qual)

summary(m1_reg_word_ratio_gad)
pp_check(m1_reg_word_ratio_gad)
```
```{r}
hist(df_ami_senti_word_PE_qual$GAD_score)
```
```{r}
gad_evpe <- lmer(GAD_score ~ EVPE_val*EVPE_mag+ (1|ID) + (1|exam_num),  data = df_ami_senti_word_PE_qual)

summary(gad_evpe)
```

```{r}
m1_reg_word_ratio_gad_EVPE_val <- lmer(reg_word_ratio ~ GAD_score*EVPE_val + 1 + (1|ID) + (1|exam_num),  data = df_ami_senti_word_PE_qual)

summary(m1_reg_word_ratio_gad_EVPE_val)
pp_check(m1_reg_word_ratio_gad_EVPE_val)
```
```{r}
m1_reg_word_ratio_gad_EVPE_val_mag <- lmer(reg_word_ratio ~ GAD_score*EVPE_val*EVPE_mag + (1|ID) + (1|exam_num),  data = df_ami_senti_word_PE_qual)

summary(m1_reg_word_ratio_gad_EVPE_val_mag)
pp_check(m1_reg_word_ratio_gad_EVPE_val_mag)
```

```{r}
m1_reg_word_ratio_gad_EVPE_mag <- lmer(reg_word_ratio ~ GAD_score*EVPE_mag + (1|ID) + (1|exam_num),  data = df_ami_senti_word_PE_qual)

summary(m1_reg_word_ratio_gad_EVPE_mag)
pp_check(m1_reg_word_ratio_gad_EVPE_mag)
```
## reg_word_ratio ~ PE*GAD
```{r}
test_EVPE <- lmer(reg_word_ratio ~ GAD_score*EVPE + (1|ID) + (1|exam_num),  data = df_ami_senti_word_PE_qual)

summary(test_EVPE)
pp_check(test_EVPE)
```
```{r}
test_PE_2 <- lmer(reg_word_ratio ~ GAD_score*PE_2 + (1|ID) + (1|exam_num),  data = df_ami_senti_word_PE_qual)

summary(test_PE_2)
pp_check(test_PE_2)
```
```{r}
test_PE_1 <- lmer(reg_word_ratio ~ GAD_score*PE_1 + (1|ID) + (1|exam_num),  data = df_ami_senti_word_PE_qual)

summary(test_PE_1)
pp_check(test_PE_1)
```

### PE shift vs. GAD
```{r}
df_ami_senti_word_PE_qual_no_na <- df_ami_senti_word_PE_qual %>% filter(!is.na(PE_1)&!is.na(PE_2)) %>% mutate(PE_shift = PE_2-PE_1)
```


```{r}
m3_PE_shift_gad <- lmer(PE_shift ~ EVPE*GAD_score + (1|exam_num) +(1|ID), data =df_ami_senti_word_PE_qual_no_na)
summary(m3_PE_shift_gad)
```
```{r}
plot(x = df_ami_senti_word_PE_qual_no_na$GAD_score, y = df_ami_senti_word_PE_qual_no_na$PE_shift)
```

```{r}
m3_PE_shift_SIAS <- lmer(PE_shift ~ SIAS_score + Prediction_1_confidence + (1|exam_num) +(1|ID), data =df_ami_senti_word_PE_qual_no_na)
summary(m3_PE_shift_SIAS)
```

```{r}
test_phq <- lmer(reg_word_ratio ~ PHQ_score*EVPE + (1|ID) + (1|exam_num),  data = df_ami_senti_word_PE_qual)

summary(test_phq)
pp_check(test_phq)
```


```{r}
m3_ordinal_ami_senti_reg_word_ratio <- brm(reg_word_ratio ~ GAD_score*EVPE + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE)
```


```{r}
neu_ami_reg_ratio_EVPE_val_dotplot <- ggplot(df_ami_senti_word_PE_neu, aes(x = negative_emotionality.x, y = reg_word_ratio, color = ami_senti_group)) +
  geom_point(size = 2, alpha = 0.7) +
  facet_wrap(~ EVPE_val) + 
  labs(
    x = "Neuroticism (individual difference)",
    y = "Ragulation word ratio",
    title = "Relationship between Neuroticism and model interaction effect"
  ) +
  theme_classic()

neu_ami_reg_ratio_EVPE_val_dotplot
```

```{r}
gad_ami_reg_ratio_EVPE_val_dotplot <- ggplot(df_ami_senti_word_PE_qual, aes(x = GAD_score, y = reg_word_ratio, color = ami_senti_group)) +
  geom_point(size = 2, alpha = 0.7) +
  facet_wrap(~ EVPE_val) + 
  labs(
    x = "GAD (individual difference)",
    y = "Regulation word ratio",
    title = "Relationship between GAD and model interaction effect"
  ) +
  theme_classic()

gad_ami_reg_ratio_EVPE_val_dotplot
```
```{r}
rdm_ordinal_ami_senti_reg_word_ratio <- brm(ami_senti_group ~ reg_word_ratio * EVPE_val + (1 + reg_word_ratio * EVPE_val|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE)
summary(rdm_ordinal_ami_senti_reg_word_ratio)
pp_check(rdm_ordinal_ami_senti_reg_word_ratio)
```

```{r}
rdm_ordinal_ami_senti_reg_word_ratio <- brm(ami_senti_group ~ reg_word_ratio + (1 + reg_word_ratio * EVPE_val|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE)
summary(rdm_ordinal_ami_senti_reg_word_ratio)
pp_check(rdm_ordinal_ami_senti_reg_word_ratio)
```
```{r}
loo(rdm_ordinal_ami_senti_reg_word_ratio,m2_ordinal_ami_senti_reg_word_ratio_EVPE_val)
```

```{r}
ranef_df <- ranef(rdm_ordinal_ami_senti_reg_word_ratio)$ID %>%
  as.data.frame() %>%
  tibble::rownames_to_column("ID")

interaction_effects <- ranef_df %>%
  select(ID, starts_with("Estimate.reg_word_ratio:EVPE_val"))
```

```{r}
interaction_effects$ID <- as.integer(interaction_effects$ID)
df_plot_neu <- df_neu %>%
  left_join(interaction_effects, by = "ID") %>%
  dplyr::rename(estimate = `Estimate.reg_word_ratio:EVPE_valpositive`)
```
## Neuro vs mem_senti
```{r}
cor_test <- cor.test(df_plot_neu$estimate, df_plot_neu$negative_emotionality)
cor_test

r_value  <- cor_test$estimate
p_value  <- cor_test$p.value
r2_value <- r_value^2

```

```{r}
library(ggplot2)

neu_ami_reg_ratio_EVPE_val_plot <- ggplot(df_plot_neu, aes(x = negative_emotionality, y = estimate)) +
  geom_point(size = 2, alpha = 0.7) +
  geom_smooth(method = "lm", se = TRUE, color = "purple") +
  annotate(
    "text",
    x = Inf, y = Inf,
    label = paste0(
      "r = ", round(r_value, 2),
      ", R² = ", round(r2_value, 2),
      ", p = ", signif(p_value, 2)
    ),
    hjust = 1.1, vjust = 1.5, size = 4
  ) +
  labs(
    x = "Neuroticism (individual difference)",
    y = "Interaction Effect (reg_word_ratio × EVPE_val)",
    title = "Relationship between Neuroticism and model interaction effect"
  ) +
  theme_classic()
  
neu_ami_reg_ratio_EVPE_val_plot
```


```{r}
df_plot_mood <- df_qual %>%
  left_join(interaction_effects, by = "ID") %>%
  dplyr::rename(estimate = `Estimate.reg_word_ratio:EVPE_valpositive`)
```

## GAD vs. mem_senti
```{r}
cor_test_gad <- cor.test(df_plot_mood$estimate, df_plot_mood$GAD_score)
cor_test_gad

r_value  <- cor_test_gad$estimate
p_value  <- cor_test_gad$p.value
r2_value <- r_value^2

```
```{r}
library(ggplot2)

gad_ami_reg_ratio_EVPE_val_plot <- ggplot(df_plot_mood, aes(x = GAD_score, y = estimate)) +
  geom_point(size = 2, alpha = 0.6, color = "skyblue2") +
  geom_smooth(method = "lm", se = TRUE, color = "skyblue4") +
  annotate(
    "text",
    x = Inf, y = Inf,
    label = paste0(
      "r = ", round(r_value, 2),
      ", R² = ", round(r2_value, 2),
      ", p = ", signif(p_value, 2)
    ),
    hjust = 1.1, vjust = 1.5, size = 4
  ) + 
  labs(
    x = "GAD score",
    y = "Estimate of the interaction Effect \n(regulation ratio × EVPE valence)",
    title = "Relationship between GAD and the interaction effect"
  ) +
  theme_classic()
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/GAD_EVPE_val_reg_ratio_int_AMI_senti.png",plot = gad_ami_reg_ratio_EVPE_val_plot, width = 6, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/GAD_EVPE_val_reg_ratio_int_AMI_sent.pdf",plot = gad_ami_reg_ratio_EVPE_val_plot, width = 6, heigh = 4, dpi = 300)
gad_ami_reg_ratio_EVPE_val_plot
```

## wrap_facet GAD
```{r}
hist(df_plot_mood$GAD_score)
summary(df_plot_mood$GAD_score)
sd_gad <- sd(df_plot_mood$GAD_score)
mean_gad <- mean(df_plot_mood$GAD_score)

library(dplyr)
# m2_ordinal_ami_senti_reg_EVPE_int <- brm(ami_senti_group ~ EVPE + reg_ratio + EVPE*reg_ratio + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_ratio_PE)

## with each exam GAD
# df_plot_mood <- df_plot_mood %>%
#   mutate(
#     GAD_level = ifelse(
#       GAD_score <= median(GAD_score, na.rm = TRUE),
#       "Low GAD",
#       "High GAD"
#     ),
#     GAD_level = factor(GAD_level, levels = c("Low GAD", "High GAD"))
#   )
```


```{r}
low_cut  <- quantile(df_plot_mood$GAD_score, 0.30, na.rm = TRUE)
high_cut <- quantile(df_plot_mood$GAD_score, 0.70, na.rm = TRUE)

df_plot_mood <- df_plot_mood %>%
  mutate(
    GAD_level = case_when(
      GAD_score <= low_cut  ~ "Low GAD",
      GAD_score >= high_cut ~ "High GAD",
      TRUE                  ~ NA_character_
    ),
    GAD_level = factor(GAD_level,
                       levels = c("Low GAD", "High GAD"))
  )
df_ami_senti_reg_PE_mood <- inner_join(df_ami_senti_ratio_PE, df_plot_mood, by = "ID")
```

```{r}
# separate into two group
high_gad_ami_senti_reg_PE <- df_ami_senti_reg_PE_mood %>% filter(GAD_level == "High GAD")
low_gad_ami_senti_reg_PE <- df_ami_senti_reg_PE_mood %>% filter(GAD_level == "Low GAD")
```
```{r}
# High GAD: memory_senti ~ EVPE_val + reg_ratio + EVPE*reg_ratio
m7_ordinal_ami_senti_reg_EVPE_val_high_gad <- brm(ami_senti_group ~ EVPE_val + reg_ratio + EVPE_val*reg_ratio + (1|ID) + (1|exam_num), family = cumulative("logit"), data = high_gad_ami_senti_reg_PE)
summary(m7_ordinal_ami_senti_reg_EVPE_val_high_gad)
```
```{r}
# High GAD: memory_senti ~ EVPE_val + reg_ratio + EVPE*reg_ratio
m7_ordinal_ami_senti_reg_EVPE_high_gad <- brm(ami_senti_group ~ EVPE + reg_ratio + EVPE*reg_ratio + (1|ID) + (1|exam_num), family = cumulative("logit"), data = high_gad_ami_senti_reg_PE)
summary(m7_ordinal_ami_senti_reg_EVPE_high_gad)
```
```{r}
# Low GAD: memory_senti ~ EVPE + reg_ratio + EVPE*reg_ratio
m7_ordinal_ami_senti_reg_EVPE_val_low_gad <- brm(ami_senti_group ~ EVPE_val + reg_ratio + EVPE_val*reg_ratio + (1|ID) + (1|exam_num), family = cumulative("logit"), data = low_gad_ami_senti_reg_PE)
summary(m7_ordinal_ami_senti_reg_EVPE_val_low_gad)
```
```{r}
# Low GAD: memory_senti ~ EVPE + reg_ratio + EVPE*reg_ratio
m7_ordinal_ami_senti_reg_EVPE_low_gad <- brm(ami_senti_group ~ EVPE + reg_ratio + EVPE*reg_ratio + (1|ID) + (1|exam_num), family = cumulative("logit"), data = low_gad_ami_senti_reg_PE)
summary(m7_ordinal_ami_senti_reg_EVPE_low_gad)
```
```{r}
high_gad_ami_senti_EVPE_int_plotting <- conditional_effects(m7_ordinal_ami_senti_reg_EVPE_high_gad, effects = "reg_ratio:EVPE",
  int_conditions = list(
    EVPE = c(10, 0, -10)
  ),
  categorical = FALSE
)
high_gad_ami_senti_EVPE_int_plot <- high_gad_ami_senti_EVPE_int_plotting[["reg_ratio:EVPE"]]
# high_gad_ami_senti_EVPE_int_plot_list <- plot(high_gad_ami_senti_EVPE_int_plotting, plot = FALSE)
# high_had_ami_senti_EVPE_int_plot_main <- high_gad_ami_senti_EVPE_int_plot_list[[3]]
# high_had_ami_senti_EVPE_int_plot_main
```
```{r}
library(ggplot2)
library(dplyr)

high_gad_ami_senti_EVPE_int_plot <- high_gad_ami_senti_EVPE_int_plot %>%
  mutate(
    EVPE = factor(
      EVPE,
      levels = c(10, -10)
    )
  )

high_gad_ami_senti_EVPE_int_plot_fn <- ggplot(
  high_gad_ami_senti_EVPE_int_plot,
  aes(
    x = reg_ratio,
    y = estimate__,
    color = EVPE,
    fill = EVPE,
    group = EVPE
  )
) +
  geom_ribbon(
    aes(ymin = lower__, ymax = upper__),
    alpha = 0.4,
    color = NA
  ) +
  geom_line(linewidth = 1.2) +
  # scale_color_manual(
  #   values = c(
  #     "10" = "#619CFF",
  #     "0" = "#00BA38",
  #     "-10" = "#F8766D"
  #   )
  # ) +
  # scale_fill_manual(
  #   values = c(
  #     "10" = "#619CFF",
  #     "0" = "#00BA38",
  #     "-10" = "#F8766D"
  #   )
  # ) +
  labs(
    x = "Regulation proportion",
    y = "Predicted memory valence category",
    color = "PE",
    fill = "PE",
    title = "High General Anxiety"
  ) +
  theme_classic(base_size = 12)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_reg_high_GAD_plot.pdf",plot = high_gad_ami_senti_EVPE_int_plot_fn, width = 5, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_reg_high_GAD_plot.eps",plot = high_gad_ami_senti_EVPE_int_plot_fn, width = 5, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_reg_high_GAD_plot.png",plot = high_gad_ami_senti_EVPE_int_plot_fn, width = 5, heigh = 4, dpi = 300)
high_gad_ami_senti_EVPE_int_plot_fn
```
```{r}
high_gad_ami_senti_EVPE_val_int_plotting <- conditional_effects(
  m7_ordinal_ami_senti_reg_EVPE_val_high_gad,
  effects = "reg_ratio:EVPE_val"
)

names(high_gad_ami_senti_EVPE_val_int_plotting)

high_gad_ami_senti_EVPE_val_int_plot <- high_gad_ami_senti_EVPE_val_int_plotting[["reg_ratio:EVPE_val"]]

high_gad_ami_senti_EVPE_val_int_plot_fn <- ggplot(
  high_gad_ami_senti_EVPE_val_int_plot,
  aes(
    x = reg_ratio,
    y = estimate__,
    color = factor(EVPE_val),
    fill = factor(EVPE_val)
  )
) +
  geom_ribbon(
    aes(
      ymin = lower__,
      ymax = upper__
    ),
    alpha = 0.4,
    color = NA
  ) +
  geom_line(linewidth = 0.8) +
  labs(
    x = "Regulation proportion",
    y = "Predicted AMI sentiment",
    color = "PE valence",
    fill = "PE valence",
    title = "High General Anxiety"
  ) +
  theme_classic(base_size = 12)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_val_reg_high_GAD_plot.pdf",plot = high_gad_ami_senti_EVPE_val_int_plot_fn, width = 5, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_val_reg_high_GAD_plot.eps",plot = high_gad_ami_senti_EVPE_val_int_plot_fn, width = 5, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_val_reg_high_GAD_plot.png",plot = high_gad_ami_senti_EVPE_val_int_plot_fn, width = 5, heigh = 4, dpi = 300)
high_gad_ami_senti_EVPE_val_int_plot_fn
```

```{r}
low_gad_ami_senti_EVPE_val_int_plotting <- conditional_effects(
  m7_ordinal_ami_senti_reg_EVPE_val_low_gad,
  effects = "reg_ratio:EVPE_val"
)

names(low_gad_ami_senti_EVPE_val_int_plotting)

low_gad_ami_senti_EVPE_val_int_plot <- low_gad_ami_senti_EVPE_val_int_plotting[["reg_ratio:EVPE_val"]]

low_gad_ami_senti_EVPE_val_int_plot_fn <- ggplot(
  low_gad_ami_senti_EVPE_val_int_plot,
  aes(
    x = reg_ratio,
    y = estimate__,
    color = factor(EVPE_val),
    fill = factor(EVPE_val)
  )
) +
  geom_ribbon(
    aes(
      ymin = lower__,
      ymax = upper__
    ),
    alpha = 0.4,
    color = NA
  ) +
  geom_line(linewidth = 0.8) +
  labs(
    x = "Regulation proportion",
    y = "Predicted AMI sentiment",
    color = "PE valence",
    fill = "PE valence",
    title = "Low General Anxiety"
  ) +
  theme_classic(base_size = 12)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_val_reg_low_GAD_plot.pdf",plot = low_gad_ami_senti_EVPE_val_int_plot_fn, width = 5, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_val_reg_low_GAD_plot.eps",plot = low_gad_ami_senti_EVPE_val_int_plot_fn, width = 5, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_val_reg_low_GAD_plot.png",plot = low_gad_ami_senti_EVPE_val_int_plot_fn, width = 5, heigh = 4, dpi = 300)

low_gad_ami_senti_EVPE_val_int_plot_fn
```


```{r}
low_gad_ami_senti_EVPE_int_plotting <- conditional_effects(m7_ordinal_ami_senti_reg_EVPE_low_gad, effects = "reg_ratio:EVPE",
  int_conditions = list(
    EVPE = c(10, -10)
  ),
  categorical = FALSE
)
low_gad_ami_senti_EVPE_int_plot <- low_gad_ami_senti_EVPE_int_plotting[["reg_ratio:EVPE"]]
```
```{r}
library(ggplot2)
library(dplyr)

low_gad_ami_senti_EVPE_int_plot <- low_gad_ami_senti_EVPE_int_plot %>%
  mutate(
    EVPE = factor(
      EVPE,
      levels = c(10, -10)
    )
  )

low_gad_ami_senti_EVPE_int_plot_fn <- ggplot(
  low_gad_ami_senti_EVPE_int_plot,
  aes(
    x = reg_ratio,
    y = estimate__,
    color = EVPE,
    fill = EVPE,
    group = EVPE
  )
) +
  geom_ribbon(
    aes(ymin = lower__, ymax = upper__),
    alpha = 0.4,
    color = NA
  ) +
  geom_line(linewidth = 1.2) +
 
  labs(
    x = "Regulation proportion",
    y = "Predicted memory valence category",
    color = "PE",
    fill = "PE",
    title = "Low General Anxiety"
  ) +
  theme_classic(base_size = 12)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_reg_low_GAD_plot.pdf",plot = low_gad_ami_senti_EVPE_int_plot_fn, width = 5, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_reg_low_GAD_plot.eps",plot = low_gad_ami_senti_EVPE_int_plot_fn, width = 5, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_reg_low_GAD_plot.png",plot = low_gad_ami_senti_EVPE_int_plot_fn, width = 5, heigh = 4, dpi = 300)
low_gad_ami_senti_EVPE_int_plot_fn
```

```{r}
# trait GAD
library(patchwork)

gad_ami_senti_EVPE_int_side_plot <- 
  low_gad_ami_senti_EVPE_int_plot_fn +
  high_gad_ami_senti_EVPE_int_plot_fn +
  plot_layout(guides = "collect") &
  theme(legend.position = "right")

gad_ami_senti_EVPE_int_side_plot
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_reg_GAD_side_plot.pdf", gad_ami_senti_EVPE_int_side_plot, width = 10, height = 4, dpi = 300, device = cairo_pdf)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_reg_GAD_side_plot.eps", gad_ami_senti_EVPE_int_side_plot, width = 10, height = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_reg_GAD_side_plot.png", gad_ami_senti_EVPE_int_side_plot, width = 10, height = 4, dpi=600)
```
```{r}
# trait GAD vs. PE_val
library(patchwork)

gad_ami_senti_EVPE_val_int_side_plot <- 
  low_gad_ami_senti_EVPE_val_int_plot_fn +
  high_gad_ami_senti_EVPE_val_int_plot_fn +
  plot_layout(guides = "collect") &
  theme(legend.position = "right")

gad_ami_senti_EVPE_val_int_side_plot
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_val_reg_GAD_side_plot.pdf", gad_ami_senti_EVPE_val_int_side_plot, width = 10, height = 4, dpi = 300, device = cairo_pdf)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_val_reg_GAD_side_plot.eps", gad_ami_senti_EVPE_val_int_side_plot, width = 10, height = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_val_reg_GAD_side_plot.png", gad_ami_senti_EVPE_val_int_side_plot, width = 10, height = 4, dpi=600)
```


```{r}
high_ce <- conditional_effects(
  m7_ordinal_ami_senti_reg_EVPE_high_gad,
  effects = "EVPE_val:reg_ratio",
  categorical = FALSE
)

plot_highgad_df <- high_ce[["EVPE_val:reg_ratio"]]
```
```{r}
ggplot(
  plot_highgad_df,
  aes(
    x = reg_ratio,
    y = estimate__,
    color = EVPE_val,
    fill = EVPE_val,
    group = EVPE_val
  )
) +
  geom_ribbon(
    aes(ymin = lower__, ymax = upper__),
    alpha = 0.15,
    color = NA
  ) +
  geom_line(linewidth = 1.2) +
  labs(
    x = "Regulation ratio",
    y = "Predicted AMI sentiment",
    color = "EVPE valence",
    fill = "EVPE valence"
  ) +
  theme_classic(base_size = 14)
```
```{r}
low_ce <- conditional_effects(
  m7_ordinal_ami_senti_reg_EVPE_low_gad,
  effects = "EVPE_val:reg_ratio",
  categorical = FALSE
)

plot_lowgad_df <- low_ce[["EVPE_val:reg_ratio"]]
```

```{r}
ggplot(
  plot_lowgad_df,
  aes(
    x = reg_ratio,
    y = estimate__,
    color = EVPE_val,
    fill = EVPE_val,
    group = EVPE_val
  )
) +
  geom_ribbon(
    aes(ymin = lower__, ymax = upper__),
    alpha = 0.15,
    color = NA
  ) +
  geom_line(linewidth = 1.2) +
  labs(
    x = "Regulation ratio",
    y = "Predicted AMI sentiment",
    color = "EVPE valence",
    fill = "EVPE valence"
  ) +
  theme_classic(base_size = 14)
```
```{r}
cond <- data.frame(
  reg_ratio = quantile(
    low_gad_ami_senti_reg_PE$reg_ratio,
    probs = c(.25, .75),
    na.rm = TRUE
  )
)

cond$reg_level <- c("Low regulation", "High regulation")

ce <- conditional_effects(
  m7_ordinal_ami_senti_reg_EVPE_low_gad,
  effects = "EVPE_val",
  conditions = cond,
  categorical = TRUE
)

plot_df <- ce[[1]]
head(plot_df)
```
```{r}
ggplot(
  plot_df,
  aes(
    x = EVPE_val,
    y = estimate__,
    color = cats__
  )
) +
  geom_point(size = 3, position = position_dodge(width = .3)) +
  geom_errorbar(
    aes(ymin = lower__, ymax = upper__),
    width = .1,
    position = position_dodge(width = .3)
  ) +
  facet_wrap(~ cond__) +
  labs(
    x = "EVPE valence",
    y = "Predicted probability",
    color = "AMI sentiment"
  ) +
  theme_classic()
```

```{r}
low_gad_ami_senti_EVPE_val_int_plotting <- conditional_effects(m7_ordinal_ami_senti_reg_EVPE_low_gad)

low_gad_ami_senti_EVPE_val_int_plot_list <- plot(low_gad_ami_senti_EVPE_val_int_plotting, plot = FALSE)
low_had_ami_senti_EVPE_val_int_plot_main <- low_gad_ami_senti_EVPE_val_int_plot_list[[3]]
low_had_ami_senti_EVPE_val_int_plot_main
```
```{r}
m5_ordinal_ami_senti_reg_EVPE_GAD_int <- brm(ami_senti_group ~ EVPE*reg_ratio*GAD_score + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_reg_PE_mood)
```
```{r}
summary(m5_ordinal_ami_senti_reg_EVPE_GAD_int)
```

# Threeway int: mem_senti ~ EVPE + reg+GAD
## dense GAD
```{r}
df_ami_senti_word_PE_mood
```

```{r}
m_ordinal_ami_senti_reg_word_EVPE_exam_GAD_int <- brm(ami_senti_group ~ EVPE*reg_word_ratio*GAD + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_word_PE_mood)
summary(m_ordinal_ami_senti_reg_word_EVPE_exam_GAD_int)
```
```{r}
summary(m_ordinal_ami_senti_reg_word_EVPE_exam_GAD_int)
```

```{r}
m6_ordinal_ami_senti_reg_EVPE_exam_GAD_int <- brm(ami_senti_group ~ EVPE*reg_ratio*GAD + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_reg_PE_mood)
```
```{r}
summary(m6_ordinal_ami_senti_reg_EVPE_exam_GAD_int)
```

```{r}
low_GAD  <- mean(df_ami_senti_reg_PE_mood$GAD, na.rm = TRUE) - sd(df_ami_senti_reg_PE_mood$GAD, na.rm = TRUE)
high_GAD <- mean(df_ami_senti_reg_PE_mood$GAD, na.rm = TRUE) + sd(df_ami_senti_reg_PE_mood$GAD, na.rm = TRUE)

ce_3way <- conditional_effects(
  m6_ordinal_ami_senti_reg_EVPE_exam_GAD_int,
  effects = "reg_ratio:EVPE",
  conditions = data.frame(
    GAD = c(low_GAD, high_GAD)
  ),
  int_conditions = list(
    EVPE = c(10, -10)
  )
)

```
```{r}
plot_list <- plot(ce_3way, plot = FALSE)
plot_list[[1]]
```
```{r}
plot_df <- ce_3way[[1]]
plot_df$EVPE <- round(plot_df$EVPE, 2)
plot_df$GAD_level <- factor(
  plot_df$cond__,
  levels = c(1, 2),
  labels = c(
    paste0("Low General Anxiety (", round(low_GAD, 1), ")"),
    paste0("High General Anxiety (", round(high_GAD, 1), ")")
  )
)
plot_df$EVPE <- factor(
  plot_df$EVPE,
  levels = c(10, -10)
)
```
### threeway int plotting
```{r}
ami_mem_senti_PE_reg_GAD_level_plot <- ggplot(plot_df,
       aes(x = reg_ratio,
           y = estimate__,
           color = factor(EVPE))) +
  geom_line(linewidth = 0.8) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__,
                  fill = factor(EVPE)),
                alpha = 0.4,
  color = NA,
  linewidth = 0) +
#   scale_color_manual(
#   values = c(
#     "10" = "#619CFF",
#     "0" = "#00BA38",
#     "-10" = "#F8766D"
#   )
# ) +
#   scale_color_manual(
#   values = c(
#     "10" = "#49beaa",
#     "0" = "#f3a712",
#     "-10" = "#db2b39"
#   )
# ) +
  # scale_fill_manual(
  #   values = c(
  #     "10" = "#619CFF",
  #     "0" = "#00BA38",
  #     "-10" = "#F8766D"
  #   )
  # ) +
  # scale_fill_manual(
  # values = c(
  #   "10" = "#49beaa",
  #   "0" = "#f3a712",
  #   "-10" = "#db2b39"
  # )
  # ) +
  ylab("Predicted memory valence category") +
  xlab("Regulation proportion") + 
  labs(color = "PE", fill = "PE") +
  facet_wrap(~ GAD_level) +
  theme_classic() +
  theme(
    text = element_text(family = "sans",size = 14),
    strip.text = element_text(size = 14),
    strip.background = element_blank())
ami_mem_senti_PE_reg_GAD_level_plot
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_reg_GAD_level_plot.pdf",plot = ami_mem_senti_PE_reg_GAD_level_plot, width = 8, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_reg_GAD_level_plot.eps",plot = ami_mem_senti_PE_reg_GAD_level_plot, width = 8, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_reg_GAD_level_plot.png",plot = ami_mem_senti_PE_reg_GAD_level_plot, width = 8, heigh = 4, dpi = 300)
```

```{r}
m6_ordinal_ami_senti_reg_EVPE_val_exam_GAD_int <- brm(ami_senti_group ~ EVPE_val*reg_ratio*GAD + (1|ID) + (1|exam_num), family = cumulative("logit"), data = df_ami_senti_reg_PE_mood)
```
```{r}
summary(m6_ordinal_ami_senti_reg_EVPE_val_exam_GAD_int)
```
```{r}
low_GAD  <- mean(df_ami_senti_reg_PE_mood$GAD, na.rm = TRUE) - sd(df_ami_senti_reg_PE_mood$GAD, na.rm = TRUE)
high_GAD <- mean(df_ami_senti_reg_PE_mood$GAD, na.rm = TRUE) + sd(df_ami_senti_reg_PE_mood$GAD, na.rm = TRUE)

ce_PE_val_3way <- conditional_effects(
  m6_ordinal_ami_senti_reg_EVPE_val_exam_GAD_int,
  effects = "reg_ratio:EVPE_val",
  conditions = data.frame(
    GAD = c(low_GAD, high_GAD)
  ),
  int_conditions = list(
    EVPE_val = c("negative", "positive")
  ),
  categorical = FALSE
)

```
```{r}
ce_PE_val_3way_list <- plot(ce_PE_val_3way, plot = FALSE)
ce_PE_val_3way_list[[1]]
```
```{r}
ce_PE_val_3way_df <-ce_PE_val_3way[["reg_ratio:EVPE_val"]]
ce_PE_val_3way_df$GAD_level <- factor(
  ce_PE_val_3way_df$cond__,
  levels = c(1, 2),
  labels = c(
    paste0("Low General Anxiety (", round(low_GAD, 1), ")"),
    paste0("High General Anxiety (", round(high_GAD, 1), ")")
  )
)


```
### threeway int plotting
```{r}
ami_mem_senti_PE_val_reg_GAD_level_plot <- ggplot(ce_PE_val_3way_df ,
       aes(x = reg_ratio,
           y = estimate__,
           color = EVPE_val,
           fill = EVPE_val,
           group_EVPE_val)) +
  geom_line(linewidth = 0.8) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__,
                  fill = EVPE_val),
                alpha = 0.4,
  color = NA,
  linewidth = 0) +
  ylab("Predicted memory valence category") +
  xlab("Regulation proportion") + 
  labs(color = "PE", fill = "PE") +
  facet_wrap(~ GAD_level) +
  theme_classic() +
  theme(
    text = element_text(family = "sans",size = 14),
    strip.text = element_text(size = 14),
    strip.background = element_blank())
ami_mem_senti_PE_val_reg_GAD_level_plot
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_val_reg_GAD_level_plot.pdf",plot = ami_mem_senti_PE_val_reg_GAD_level_plot, width = 8, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_val_reg_GAD_level_plot.eps",plot = ami_mem_senti_PE_val_reg_GAD_level_plot, width = 8, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/ami_mem_senti_PE_val_reg_GAD_level_plot.png",plot = ami_mem_senti_PE_val_reg_GAD_level_plot, width = 8, heigh = 4, dpi = 300)
```
## PHQ vs. ami_senti
```{r}
cor_test_phq <- cor.test(df_plot_mood$estimate, df_plot_mood$PHQ_score)
cor_test_phq

r_value  <- cor_test_phq$estimate
p_value  <- cor_test_phq$p.value
r2_value <- r_value^2

PHQ_ami_reg_ratio_EVPE_val_plot <- ggplot(df_plot_mood, aes(x = PHQ_score, y = estimate)) +
  geom_point(size = 2, alpha = 0.6, color = "skyblue2") +
  geom_smooth(method = "lm", se = TRUE, color = "skyblue4") +
  annotate(
    "text",
    x = Inf, y = Inf,
    label = paste0(
      "r = ", round(r_value, 2),
      ", R² = ", round(r2_value, 2),
      ", p = ", signif(p_value, 2)
    ),
    hjust = 1.1, vjust = 1.5, size = 4
  ) + 
  labs(
    x = "PHQ score",
    y = "Estimate of the interaction Effect \n(regulation ratio × EVPE valence)",
    title = "Relationship between PHQ and the interaction effect"
  ) +
  theme_classic()
#ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/PHQ_EVPE_val_reg_ratio_int_AMI_senti.png",plot = PHQ_ami_reg_ratio_EVPE_val_plot, width = 6, heigh = 4, dpi = 300)
#ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/PHQ_EVPE_val_reg_ratio_int_AMI_sent.pdf",plot = PHQ_ami_reg_ratio_EVPE_val_plot, width = 6, heigh = 4, dpi = 300)
PHQ_ami_reg_ratio_EVPE_val_plot
```

## SIAS vs. ami_senti
```{r}
cor_test_sias <- cor.test(df_plot_mood$estimate, df_plot_mood$SIAS_score)
cor_test_sias

r_value  <- cor_test_sias$estimate
p_value  <- cor_test_sias$p.value
r2_value <- r_value^2

SIAS_ami_reg_ratio_EVPE_val_plot <- ggplot(df_plot_mood, aes(x = SIAS_score, y = estimate)) +
  geom_point(size = 2, alpha = 0.7) +
  geom_smooth(method = "lm", se = TRUE, color = "purple") +
  annotate(
    "text",
    x = Inf, y = Inf,
    label = paste0(
      "r = ", round(r_value, 2),
      ", R² = ", round(r2_value, 2),
      ", p = ", signif(p_value, 2)
    ),
    hjust = 1.1, vjust = 1.5, size = 4
  ) + 
  labs(
    x = "SIAS score (individual difference)",
    y = "Interaction Effect (reg_word_ratio × EVPE_val)",
    title = "Relationship between SIAS and model interaction effect"
  ) +
  theme_classic()
  
SIAS_ami_reg_ratio_EVPE_val_plot
```
## OCIR vs. ami_senti
```{r}
cor_test_ocir <- cor.test(df_plot_mood$estimate, df_plot_mood$OCIR_score)
cor_test_ocir

r_value  <- cor_test_ocir$estimate
p_value  <- cor_test_ocir$p.value
r2_value <- r_value^2

OCIR_ami_reg_ratio_EVPE_val_plot <- ggplot(df_plot_mood, aes(x = OCIR_score, y = estimate)) +
  geom_point(size = 2, alpha = 0.7) +
  geom_smooth(method = "lm", se = TRUE, color = "purple") +
  annotate(
    "text",
    x = Inf, y = Inf,
    label = paste0(
      "r = ", round(r_value, 2),
      ", R² = ", round(r2_value, 2),
      ", p = ", signif(p_value, 2)
    ),
    hjust = 1.1, vjust = 1.5, size = 4
  ) + 
  labs(
    x = "OCIR score (individual difference)",
    y = "Interaction Effect (reg_word_ratio × EVPE_val)",
    title = "Relationship between OCIR and model interaction effect"
  ) +
  theme_classic()
  
OCIR_ami_reg_ratio_EVPE_val_plot
```

```{r}
cor.test(df_plot_mood$GAD_score, df_plot_mood$OCIR_score)

```

## ERQ vs. ami_senti
```{r}
cor_test_erq <- cor.test(df_plot_mood$estimate, df_plot_mood$ERQ_score)
cor_test_erq

r_value  <- cor_test_erq$estimate
p_value  <- cor_test_erq$p.value
r2_value <- r_value^2

ERQ_ami_reg_ratio_EVPE_val_plot <- ggplot(df_plot_mood, aes(x = ERQ_score, y = estimate)) +
  geom_point(size = 2, alpha = 0.7) +
  geom_smooth(method = "lm", se = TRUE, color = "purple") +
  annotate(
    "text",
    x = Inf, y = Inf,
    label = paste0(
      "r = ", round(r_value, 2),
      ", R² = ", round(r2_value, 2),
      ", p = ", signif(p_value, 2)
    ),
    hjust = 1.1, vjust = 1.5, size = 4
  ) + 
  labs(
    x = "ERQ score (individual difference)",
    y = "Interaction Effect (reg_word_ratio × EVPE_val)",
    title = "Relationship between ERQ and model interaction effect"
  ) +
  theme_classic()
  
ERQ_ami_reg_ratio_EVPE_val_plot
```
```{r}
cor_test_erq_rep <- cor.test(df_plot_mood$estimate, df_plot_mood$ERQ_rep)
cor_test_erq_rep

r_value  <- cor_test_erq_rep$estimate
p_value  <- cor_test_erq_rep$p.value
r2_value <- r_value^2

ERQ_rep_ami_reg_ratio_EVPE_val_plot <- ggplot(df_plot_mood, aes(x = ERQ_rep, y = estimate)) +
  geom_point(size = 2, alpha = 0.7) +
  geom_smooth(method = "lm", se = TRUE, color = "purple") +
  annotate(
    "text",
    x = Inf, y = Inf,
    label = paste0(
      "r = ", round(r_value, 2),
      ", R² = ", round(r2_value, 2),
      ", p = ", signif(p_value, 2)
    ),
    hjust = 1.1, vjust = 1.5, size = 4
  ) +
  labs(
    title = "Relationship between Trait reappraisal and model interaction effect",
    x = "ERQ Reappraisal score (individual difference)",
    y = "Interaction Effect (reg_word_ratio × EVPE_val)"
  ) +
  theme_classic()
  
ERQ_rep_ami_reg_ratio_EVPE_val_plot
```


###FAB analysis
```{r}
df_response_senti <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/emaData_F24_resp_sentiment_v5.csv")

df_exam_senti_intensity <- df_response_senti %>% dplyr::group_by(ID, exam_num) %>% dplyr::summarise(intensity_exam = mean(intensity_resp, na.rm = TRUE))
```

```{r}
df_senti_ami_exam_fab <- inner_join(df_senti_ami_exam, df_exam_senti_intensity, by = c("ID", "exam_num"))
```



# ordering PE and reg_ratio
```{r}
ordered_data_EVPE <- df_ami_ratio_PE[order(-df_ami_ratio_PE$EVPE, -df_ami_ratio_PE$reg_ratio),]
ordered_data_EVPE
```

```{r}
ordered_data_PE_1 <- df_ami_ratio_PE[order(-df_ami_ratio_PE$PE_1, -df_ami_ratio_PE$reg_ratio),]
ordered_data_PE_1
```

```{r}
ordered_data_PE_2 <- df_ami_ratio_PE[order(-df_ami_ratio_PE$PE_2, -df_ami_ratio_PE$reg_ratio),]
ordered_data_PE_2
```


