---
title: "emoLearn_F24_API_v4_analysis"
author: "Runan Wang"
date: "2026-02-17"
output: html_document
---

```{r setup, include=FALSE}
library(afex)
library(emmeans)
library(knitr)
library(tidyverse)
library(compute.es)
library(car)
library(ggplot2)
library(multcomp)
library(pastecs)
library(WRS2)
library(Hmisc)
library(tidyverse)
library(SuppDists)
library(ggpubr)
library(readxl)
library(ez)
library(lme4)
library(corrplot)
library(psych)
library(ggpubr) # for Q plot (normality check)
library(openxlsx)
library(colorspace)
library(ggrepel)
library(directlabels)
library(ggplot2)
library(reshape2)
library(plyr)
library(scales)
library(dplyr)
library(wesanderson)
library(brms)
library(stringr)
library(performance)
library(see)
library(tidyr)
library(lubridate)
library(tibble)
library(bayesplot)
library(sjPlot)
`mutate` <- dplyr::mutate
`select` <- dplyr::select
`recode` <- dplyr::recode
`summarise` <- dplyr::summarise
`describe` <- psych::describe
knitr::opts_chunk$set(echo = TRUE)
```

## Load in data
```{r cars}
df_output <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/scripts/NLP/emaData_F24_trainset_conf_labeled_full.csv")
#df_supp <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/scripts/NLP/emaData_F24_trainset_conf_labeled_supp.csv")

df <- df_output %>% filter(exam_num != "")
df <- df%>% arrange(ID, exam_num, ResponseNumber)

```


```{r}
library(dplyr)
library(tibble)

library(dplyr)
library(tibble)

collapse_text_by_label <- function(label_api_text, text_phrase) {
  r <- rle(label_api_text)
  block_id <- rep(seq_along(r$lengths), r$lengths)

  tibble(
    block_id = block_id,
    label_api_text = label_api_text,
    text_phrase = text_phrase
  ) %>%
    group_by(block_id) %>%
    summarise(
      collapsed_text_type = first(label_api_text),
      collapsed_text      = paste(text_phrase, collapse = " "),
      phrase_count        = n(),
      .groups = "drop"
    )
}


```
```{r}
df_collapsed_text <- df %>%
  group_by(ID, exam_num, ResponseNumber) %>%
  group_modify(~ collapse_text_by_label(
    label_api_text = .x$label_api,
    text_phrase    = .x$text_phrase
  )) %>%
  ungroup()
```


```{r}
write.csv(df_collapsed_text,"/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/ER/input/emaData_F24_conf_collapsed_ER_input.csv", row.names = FALSE)
```


## Precrocess data
```{r cars}
# remove na
df_no_na <- na.omit(df)

# add exam_resp number 
df_no_na <- df_no_na %>%group_by(ID, exam_num, ResponseNumber) %>% dplyr::mutate(dummy = 1) %>%  ungroup() %>% group_by(ID, exam_num, ResponseNumber) %>% dplyr::mutate(exam_resp = cur_group_id()) %>% group_by(ID) %>% dplyr::mutate(exam_resp = dense_rank(exam_resp)) %>% ungroup() %>%select(-dummy)

```

```{r}
# str_count(df_no_na$text_phrase[2], '[\\w\']+')
# '[\\w\']+' count apostrophe as one word
# Count word
# to count each phrases and add to the word_count row
for (i in (1:nrow(df_no_na))){
  phrase = df_no_na$text_phrase[i]
  df_no_na$word_count[i] <- str_count(phrase,'[\\w\']+')
}
```
# Save df_no_na
```{r}
write.csv(df_no_na, "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/processed/premedEMA_API_F24_conf_processed.csv", row.names = FALSE)
```
```{r}
df_no_na <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/processed/premedEMA_API_F24_conf_processed.csv")
```

```{r}
df_no_na <- df_no_na %>% mutate(label_api_text = case_when(label_api == -1 ~ "Expression",
                                                           label_api == 0 ~ "Neither",
                                                           label_api == 1 ~ "Regulation"))
```

```{r}
# check data
summary(df_no_na %>% filter(label_api_text == "Regulation"))
summary(df_no_na %>% filter(label_api_text == "Expression"))
summary(df_no_na %>% filter(label_api_text == "Neither"))
```
# Prelimnary Plots
## Fig1.Label frequency
```{r pressure, echo=FALSE}
Fig1_label_count_bar_plot <- df_no_na %>% ggplot(aes(x = label_api_text,
           fill = label_api_text)) +
  geom_bar(position=position_dodge(.5), size=0.55,  width=0.5, alpha = 0.8, colour="black") +
  geom_text(
    stat = "count",
    aes(label = ..count..),
    vjust = -0.3,  # moves the text above the bar
    size = 4
  ) +
  scale_fill_brewer(palette = "Set3")+
  labs(y = "Counts", x = "Labels") +
  scale_x_discrete(labels=c("Expression", "Neither", "Regulation")) +
  theme_classic() +
  theme(legend.position = "none")
  ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Fig1_bar_label_count.png",height=4, width=5, dpi=300)
  ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Fig1_bar_label_count.pdf",height=4, width=5, dpi=300)
```
```{r}
Fig1_label_count_bar_plot
```

## Select cols
```{r}
df_select <- df_no_na %>% select(ID, exam_num, ResponseNumber, exam_resp, text_phrase, label_api_text, label_api, word_count)
```
## Stacked bar plot by sub
```{r}
df_by_sub <- df_select %>% dplyr::count(ID, label_api_text) %>% pivot_wider(names_from = label_api_text, values_from = n, values_fill = 0)

df_by_sub <- df_by_sub %>% mutate(total = Expression + Neither + Regulation,
                                  exp_ratio = Expression/total,
                                  nei_ratio = Neither/total,
                                  reg_ratio = Regulation/total
                                              )
ordered_ids <- df_by_sub %>%
  arrange(desc(reg_ratio)) %>%
  pull(ID)

df_by_sub_long <- df_by_sub %>%
  select(ID, Expression, exp_ratio, Neither, nei_ratio, Regulation, reg_ratio ) %>%
  pivot_longer(cols = c(exp_ratio, nei_ratio, reg_ratio),
               names_to = "label", values_to = "count") %>%
  group_by(ID) %>%
  ungroup() %>%
  mutate(ID = factor(ID, levels = ordered_ids))
```

## Fig2. stacked bar, by sub
```{r}
dev.new(width=20, height=5)
stacked_sub_bar_plot <- ggplot(df_by_sub_long, aes(x = ID, y = count, fill = label)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black", width = 0.8, size = .1, linewidth = 0.1) +
  scale_fill_brewer(palette = "Set3", name = "", labels = c("Expression", "Neither", "Regulation")) +
  labs(
    #title = "The stacked bar plot by subjects",
    x = "Subject ID",
    y = "Percentage",
    fill = "Label"
  ) +
  #scale_fill_discrete(name = "Classification", labels = c("Expression", "Neither", "Regulation")) +
  scale_y_continuous(labels = scales::percent_format()) +
  theme_classic(base_size = 20) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
          legend.position = "bottom",
  legend.direction = "horizontal")
 ggsave("/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/Fig1_stacked_bar_by_sub.pdf", width = 30, height = 8, dpi=300, device=cairo_pdf)
  ggsave("/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/Fig1_stacked_bar_by_sub.png", width = 30, height = 8, dpi=300)
    ggsave("/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/Fig1_stacked_bar_by_sub.eps", width = 30, height = 8, dpi=300)

stacked_sub_bar_plot
```
## by response
```{r}
df_by_resp <- df_select %>% dplyr::count(ResponseNumber, label_api_text) %>% pivot_wider(names_from = label_api_text, values_from = n, values_fill = 0)

df_by_resp <- df_by_resp %>% mutate(total = Expression + Neither + Regulation,
                                  exp_ratio = Expression/total,
                                  nei_ratio = Neither/total,
                                  reg_ratio = Regulation/total
                                              )

df_by_resp_long <- df_by_resp %>%
  select(ResponseNumber, Expression, exp_ratio, Neither, nei_ratio, Regulation, reg_ratio) %>%
  pivot_longer(cols = c(exp_ratio, nei_ratio, reg_ratio),
               names_to = "label", values_to = "count") %>%
  dplyr::group_by(ResponseNumber) %>%
  ungroup()
```

```{r}
count(df_no_na$ResponseNumber)
```

## Fig3. stacked bar plot by response
```{r}
dev.new(width=4, height=3)
stacked_bar_plot_by_resp <- ggplot(df_by_resp_long, aes(x = ResponseNumber, y = count, fill = label)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black", width = 0.8, size = .1) +
  scale_fill_brewer(palette = "Set3") +
  labs(
    title = "The stacked bar plot by response number",
    x = "Response Number",
    y = "Percentage",
    fill = "Label"
  ) +
  scale_y_continuous(labels = scales::percent_format()) +
  theme_classic()
 ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Fig3_stacked_bar_by_respNo.pdf", width = 4, height = 3, dpi=300, device=cairo_pdf)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Fig3_stacked_bar_by_respNo.png", width = 4, height = 3, dpi=300)

stacked_bar_plot_by_resp
```
## By response, word_count
```{r}
df_by_resp_word_count <- df_select %>% dplyr::group_by(ResponseNumber, label_api_text) %>% summarise(avg_word_count = mean(word_count, na.rm = TRUE), .groups = "drop") %>% ungroup()
```

```{r}
dev.new(width=4, height=3)
avg_word_count_by_resp <- ggplot(df_by_resp_word_count, aes(x = ResponseNumber, y = avg_word_count, fill = label_api_text)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black", width = 0.8, size = .1) +
  scale_fill_brewer(palette = "Set3") +
  labs(
    title = "The stacked bar plot by response number",
    x = "Response Number",
    y = "Average word count",
    fill = "Label"
  ) +
  theme_classic()
# ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v4_fullset/Fig3_stacked_bar_by_respNo.pdf", width = 4, height = 3, dpi=300, device=cairo_pdf)
# ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v4_fullset/Fig3_stacked_bar_by_respNo.png", width = 4, height = 3, dpi=300)

avg_word_count_by_resp
```

```{r}
# Each subject, each exam, each response, ratio of each label
df_by_sub_by_resp <- df_select %>% dplyr::count(ID, exam_num, ResponseNumber, label_api_text) %>% pivot_wider(names_from = label_api_text, values_from = n, values_fill = 0)

df_by_sub_by_resp <- df_by_sub_by_resp %>% mutate(total = Expression + Neither + Regulation,
                                  exp_ratio = Expression/total,
                                  nei_ratio = Neither/total,
                                  reg_ratio = Regulation/total
                                              )

df_by_sub_by_resp_long <- df_by_sub_by_resp %>%
  select(ID, exam_num, ResponseNumber, Expression, exp_ratio, Neither, nei_ratio, Regulation, reg_ratio ) %>%
  pivot_longer(cols = c(exp_ratio, nei_ratio, reg_ratio),
               names_to = "label", values_to = "count") %>%
  dplyr::group_by(ID, exam_num, ResponseNumber) %>%
  ungroup()
```

```{r}
# Adjust the level of factors
df_by_sub_by_resp_long$label <- factor(
  df_by_sub_by_resp_long$label,
  levels = c("exp_ratio", "nei_ratio", "reg_ratio"),
  labels = c("Expression", "Neither", "Regulation")
)
# 
# # Count number of responses per exam
# exam_counts <- df_long_by_sub_by_resp %>%
#   distinct(ID, exam_num, ResponseNumber) %>%
#   dplyr::count(ID, exam_num, name = "n_responses")
# 
# df_plot <- df_long_by_sub_by_resp %>%
#   left_join(exam_counts, by = c("ID", "exam_num")) %>%
#   mutate(label = factor(label, levels = c("exp_ratio", "nei_ratio", "reg_ratio"),
#                         labels = c("Expression", "Neither", "Regulation")))

```

```{r}
for (i in unique(df_by_sub_by_resp_long$ID)){
  iSub <- df_by_sub_by_resp_long %>% filter(ID == i)
  fname=sprintf('/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/subjects_bar_plots/sub%s_bar_plot_by_exam_by_resp.pdf', i )
  ggplot(iSub, aes(x = factor(ResponseNumber), y = count, fill = label)) +
    geom_bar(stat = "identity", position = "fill", color = "black") +
    facet_wrap(~ exam_num, scales = "free_x") +
    scale_y_continuous(labels = scales::percent_format()) +
    scale_fill_brewer(palette = "Set3") +
    labs(
      x = "Response Number",
      y = "Proportion",
      fill = "Label",
      title = sprintf("Sub_%s_Label Proportions per Response (by Exam)", i)
    ) +
    theme_classic(base_size = 14) +
    theme(
      strip.background = element_blank(),
      strip.text = element_text(face = "bold", size = 12),
      axis.text.x = element_text(angle = 0, hjust = 0.5),
      plot.title=element_text(size = 14, hjust=0.5, vjust=0.7)
    )
  ggsave(fname,height=5, width=6, dpi=300)
}
```
## Fig4. By_exam_resp
```{r}
df_by_exam_resp <- df_select %>% dplyr::count(ID, exam_num, ResponseNumber,exam_resp, label_api_text) %>% pivot_wider(names_from = label_api_text, values_from = n, values_fill = 0)

df_by_exam_resp <- df_by_exam_resp %>% mutate(total = Expression + Neither + Regulation,
                                  exp_ratio = Expression/total,
                                  nei_ratio = Neither/total,
                                  reg_ratio = Regulation/total
                                              )

df_by_exam_resp_long <- df_by_exam_resp %>%
  select(ID, exam_num, ResponseNumber, exam_resp, Expression, exp_ratio, Neither, nei_ratio, Regulation, reg_ratio ) %>%
  pivot_longer(cols = c(exp_ratio, nei_ratio, reg_ratio),
               names_to = "label", values_to = "count") %>%
  dplyr::group_by(ID, exam_num, ResponseNumber, exam_resp) %>%
  ungroup()
```
# Fig5. exam_num vs. label ratio
```{r}
exam_label_ratio_change_plot <- ggplot(df_by_exam_resp_long, aes(x = exam_num, y = count, color = label)) +
  stat_summary(
    fun = mean, geom = "line", size = 1.2,
    aes(group = label)
  ) +
  stat_summary(
    fun = mean, geom = "point", size = 3,
    aes(shape = label)
  ) +
  scale_color_brewer(palette = "Set3") +
  geom_line(aes(group = ID), alpha = 0.1) +
  coord_cartesian(ylim=c(-0.1, 1.1)) + 
  labs(
    title = "Change in Label Proportion Across Responses",
    x = "Exam Order",
    y = "Mean Proportion",
    color = "Label",
    shape = "Label"
  ) +
  scale_y_continuous(labels = scales::percent_format()) +
  theme_classic(base_size = 14)
  ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Fig4_ratio_across_exam.png",height=4, width=5, dpi=300)
    ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Fig4_ratio_across_exam.pdf",height=4, width=5, dpi=300)
    
exam_label_ratio_change_plot
```
# Fig6. exam_resp vs. reg_ratio
```{r}
df_by_exam_resp_reg <- df_by_exam_resp_long %>% filter (label == "reg_ratio")
reg_ratio_across_all_resp_plot <- ggplot(df_by_exam_resp_reg, aes(x = exam_resp, y = count)) +
  stat_summary(
    fun = mean, geom = "line", size = 1.2,
    aes(group = label)
  ) +
  stat_summary(
    fun = mean, geom = "point", size = 3,
    aes(shape = label)
  ) +
  scale_color_brewer(palette = "Set3") +
  geom_line(aes(group = ID), alpha = 0.1) +
  coord_cartesian(ylim=c(-0.1, 1.1)) + 
  labs(
    title = "Change in Label Proportion Across Responses",
    x = "Exam Response Order (exam_resp)",
    y = "Mean Proportion",
    color = "Label",
    shape = "Label"
  ) +
  scale_y_continuous(labels = scales::percent_format()) +
  theme_classic(base_size = 14)

reg_ratio_across_all_resp_plot
```

# Fig. Individual plot
```{r}
iSub_exam_resp_reg <- df_by_exam_resp_long %>% filter (ID == "10004" & label == "reg_ratio")
ggplot(iSub_exam_resp_reg, aes(x = factor(exam_resp), y = count)) +
  geom_line(aes(group = interaction(ID, label)), alpha = 0.5) +# subject lines
  # stat_summary(fun = mean, geom = "line", size = 1.2) +  # mean line
  stat_summary(fun = mean, geom = "point", size = 3) +
  scale_color_brewer(palette = "Set3") +
  scale_y_continuous(labels = scales::percent_format()) +
  coord_cartesian(ylim=c(-0.1, 1.1)) + 
  labs(
    title = "Proportion Change of Regulation Across Responses ",
    x = "Exam Response Order (exam_resp)",
    y = "Proportion"
  ) +
  theme_classic()+
  theme(plot.title=element_text(size = 14))

  ggsave('/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v4_fullset/subjects_reg_dot_plots/reg/sub_dot_plot_by_exam_resp.pdf',height=4, width=6, dpi=300)
```

```{r}
# iSub_exam_resp_reg <- df_by_exam_resp_long %>% filter (ID == "10004" & label == "reg_ratio")
# ggplot(iSub_exam_resp_reg, aes(x = factor(ResponseNumber), y = count)) +
#   geom_line(aes(group = interaction(ID, label)), alpha = 0.5) +# subject lines
#   # stat_summary(fun = mean, geom = "line", size = 1.2) +  # mean line
#   stat_summary(fun = mean, geom = "point", size = 3) +
#   scale_color_brewer(palette = "Set3") +
#   facet_wrap(~ exam_num, scales = "free_x") +
#   scale_y_continuous(labels = scales::percent_format()) +
#   coord_cartesian(ylim=c(-0.1, 1.1)) + 
#   labs(
#     title = "Proportion Change of Regulation Across Responses ",
#     x = "Exam Response Order (exam_resp)",
#     y = "Proportion"
#   ) +
#   theme_classic(base_size = 14)
# 
#   # ggsave(fname,height=5, width=6, dpi=300)
```
## regulation_ratio
```{r}
df_by_exam_resp_long_reg <- df_by_exam_resp_long %>% filter(label == "reg_ratio")
for (i in unique(df_by_exam_resp_long_reg $ID)){
  iSub_reg <- df_by_exam_resp_long_reg  %>% filter(ID == i)
  fname=sprintf('/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/subjects_reg_dot_plots/reg/sub%s_dot_plot_by_exam_resp.pdf', i )
  ggplot(iSub_reg, aes(x = factor(exam_resp), y = count)) +
  geom_line(aes(group = interaction(ID, label)), alpha = 0.5) +# subject lines
  # stat_summary(fun = mean, geom = "line", size = 1.2) +  # mean line
  stat_summary(fun = mean, geom = "point", size = 3) +
  scale_color_brewer(palette = "Set3") +
  scale_y_continuous(labels = scales::percent_format()) +
  coord_cartesian(ylim=c(-0.1, 1.1)) + 
  labs(
    title = "Proportion Change of Regulation Across Responses ",
    x = "Exam Response Order (exam_resp)",
    y = "Proportion"
  ) +  theme_classic()+
  theme(plot.title=element_text(size = 14))

  ggsave(fname,height=4, width=6, dpi=300)
}
```

```{r}
ggplot(df_by_exam, aes(x = ID, y = reg_ratio)) +
  geom_point() +  # this adds the points
  geom_smooth(method = "loess", se = FALSE) +  # this adds the loess line
  labs(x = "slphrs", y = "anx") +
  ggtitle("Anxiety scores of students by sleep durations with a loess line")  # you can use these to change the titles of your axes
```
## label_count vs. PE, exam and response
### data prep
#### df_by_sub_by_resp
Within each exam, for each response, what the reg_ratio for each PE_1_bin
```{r}
# Load in prediction file
df_PE <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/survey_data_f24/premedEMA_f2024_predictors_df.csv")
colnames(df_PE)[1] = "ID"
# drop the wrong grade
df_PE_correct <- df_PE %>% filter(shown_wrong !="1")

df_PE <- df_PE_correct %>% mutate(PE_1_val = case_when(PE_1 < 0 ~ "negative",
                                               PE_1 > 0 ~ "positive",
                                               PE_1 == 0 ~ "zero"), 
                          PE_1_mag = abs(PE_1),
                          PE_2_val = case_when(PE_2 < 0 ~ "negative",
                                               PE_2 > 0 ~ "positive",
                                               PE_2 == 0 ~ "zero"),
                          PE_2_mag = abs(PE_2),
                          EVPE_val = case_when(EVPE < 0 ~ "negative",
                                               EVPE > 0 ~ "positive",
                                               EVPE == 0 ~ "zero"),
                          EVPE_mag = abs(EVPE)
                    )

```
```{r}
# The word count is for each phrase
df_select_tmp <- df_no_na %>% select(c(ID, exam_num, ResponseNumber, label_api, label_api_text, word_count))
# Sum up the word_count for each response and each category
df_select_tmp <- df_select_tmp %>% dplyr::group_by(ID, exam_num, ResponseNumber, label_api_text) %>% summarise(word_count_sum = sum(word_count)) %>% ungroup()
df_select_tmp_wide <- df_select_tmp %>% pivot_wider(names_from = label_api_text, values_from = word_count_sum)

df_select_tmp_wide[, c("Expression", "Neither", "Regulation")] <- replace(df_select_tmp_wide[, c("Expression", "Neither", "Regulation")], is.na(df_select_tmp_wide[, c("Expression", "Neither", "Regulation")]), 0)

# Calculate ratio of word
df_by_sub_by_resp_tmp <- df_select_tmp_wide %>% mutate(total = Expression + Neither + Regulation,
                                  exp_ratio = Expression/total,
                                  nei_ratio = Neither/total,
                                  reg_ratio = Regulation/total
                                              )
df_PE$exam_num <- as.integer(df_PE$exam_num)
df_by_sub_by_resp_PE <- inner_join(df_by_sub_by_resp_tmp, df_PE, by = c("ID", "exam_num"))

```

```{r}
# df_by_sub_by_resp_PE1 <- df_by_sub_by_resp_PE %>% filter(!is.na(PE_1))
# df_by_sub_by_resp_PE1 <- df_by_sub_by_resp_PE1 %>% mutate(
#     PE_1_bin = cut(PE_1, breaks = 10, include.lowest = TRUE, ordered_result = TRUE),
#     PE_1_abs_bin = cut(PE_1_mag, breaks = 10, include.lowest = TRUE, ordered_result = TRUE)# use factor integer code # use factor integer code
#   )
# reg_ratio_PE_1_plot <- ggplot(df_by_sub_by_resp_PE1, aes(x = exam_num, y = reg_ratio, fill = PE_1_bin)) +
# geom_bar(stat = "identity", position = "dodge") +
# labs(
#   title = paste0("Proportion of Regulation by PE Bin, Exam", sep=""),,
#   x = "Exam Number",
#   y = "Proportion of Regulation",
#   fill = "PE Bin"
# ) +
# theme_minimal() +
# theme(axis.text.x = element_text(angle = 45, hjust = 1))
# 
# reg_ratio_PE_1_plot
```

#### df_sub_by_exam
```{r}
df_select_exam_tmp <- df_no_na %>% select(c(ID, exam_num, ResponseNumber, label_api, label_api_text, word_count))

df_select_exam_tmp <- df_select_exam_tmp %>% group_by(ID, exam_num, label_api_text) %>% summarise(word_count_sum = sum(word_count)) %>% ungroup()

df_select_exam_tmp_wide <- df_select_exam_tmp %>% pivot_wider(names_from = label_api_text, values_from = word_count_sum)

df_select_exam_tmp_wide[, c("Expression", "Neither", "Regulation")] <- replace(df_select_exam_tmp_wide[, c("Expression", "Neither", "Regulation")], is.na(df_select_exam_tmp_wide[, c("Expression", "Neither", "Regulation")]), 0)

# Calculate ratio of word
df_by_sub_by_exam_tmp <- df_select_exam_tmp_wide %>% mutate(total = Expression + Neither + Regulation,
                                  exp_ratio = Expression/total,
                                  nei_ratio = Neither/total,
                                  reg_ratio = Regulation/total
                                              )
df_PE$exam_num <- as.integer(df_PE$exam_num)
df_by_sub_by_exam_PE <- inner_join(df_by_sub_by_exam_tmp, df_PE, by = c("ID", "exam_num")) 
```
```{r}
df_by_sub_by_exam_PE1 <- df_by_sub_by_exam_PE %>% filter(!is.na(PE_1))
df_by_sub_by_exam_PE1 <- df_by_sub_by_exam_PE1 %>% mutate(
    PE_1_bin = cut(PE_1, breaks = 10, include.lowest = TRUE, ordered_result = TRUE),
    PE_1_abs_bin = cut(PE_1_mag, breaks = 10, include.lowest = TRUE, ordered_result = TRUE)# use factor integer code
  )
```
##### Fig. PE_1 vs. reg_ratio
```{r}
reg_ratio_PE_1_plot <- ggplot(df_by_sub_by_exam_PE1, aes(x = exam_num, y = reg_ratio, fill = PE_1_bin)) +
geom_bar(stat = "identity", position = "dodge") +
labs(
  title = paste0("Proportion of Regulation by PE1 Bin, Exam", sep=""),,
  x = "Exam Number",
  y = "Proportion of Regulation",
  fill = "PE1 Bin"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/v5/Figure/PE_reg/per_exam/PE1_reg_ratio_exam.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/v5/Figure/PE_reg/per_exam/PE1_reg_ratio_exam.pdf",height=4, width=6, dpi=300)

reg_ratio_PE_1_plot

reg_ratio_PE_1_abs_plot <- ggplot(df_by_sub_by_exam_PE1, aes(x = exam_num, y = reg_ratio, fill = PE_1_abs_bin)) +
geom_bar(stat = "identity", position = "dodge") +
labs(
  title = paste0("Proportion of Regulation by abs PE1 Bin, Exam", sep=""),,
  x = "Exam Number",
  y = "Proportion of Regulation",
  fill = "abs PE1 Bin"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/v5/Figure/abs_PE_reg/per_exam/abs_PE1_reg_ratio_exam.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/v5/Figure/abs_PE_reg/per_exam/abs_PE1_reg_ratio_exam.pdf",height=4, width=6, dpi=300)

reg_ratio_PE_1_abs_plot
```
##### Fig. PE_1 vs. exp_ratio
```{r}
exp_ratio_PE_1_plot <- ggplot(df_by_sub_by_exam_PE1, aes(x = exam_num, y = exp_ratio, fill = PE_1_bin)) +
geom_bar(stat = "identity", position = "dodge") +
labs(
  title = paste0("Proportion of Expression by PE1 Bin, Exam", sep=""),,
  x = "Exam Number",
  y = "Proportion of Expression",
  fill = "PE1 Bin"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/v5/Figure/PE_reg/per_exam/PE1_exp_ratio_exam.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/v5/Figure/PE_reg/per_exam/PE1_exp_ratio_exam.pdf",height=4, width=6, dpi=300)

exp_ratio_PE_1_plot

exp_ratio_PE_1_abs_plot <- ggplot(df_by_sub_by_exam_PE1, aes(x = exam_num, y = exp_ratio, fill = PE_1_abs_bin)) +
geom_bar(stat = "identity", position = "dodge") +
labs(
  title = paste0("Proportion of Expression by abs PE1 Bin, Exam", sep=""),,
  x = "Exam Number",
  y = "Proportion of Expression",
  fill = "abs PE1 Bin"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/v5/Figure/abs_PE_reg/per_exam/abs_PE1_exp_ratio_exam.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/v5/Figure/abs_PE_reg/per_exam/abs_PE1_exp_ratio_exam.pdf",height=4, width=6, dpi=300)

exp_ratio_PE_1_abs_plot
```

##### Fig. PE_2 vs. reg_ratio
```{r}
df_by_sub_by_exam_PE2 <- df_by_sub_by_exam_PE %>% filter(!is.na(PE_2))
df_by_sub_by_exam_PE2 <- df_by_sub_by_exam_PE2 %>% mutate(
    PE_2_bin = cut(PE_2, breaks = 10, include.lowest = TRUE, ordered_result = TRUE),
    PE_2_abs_bin = cut(PE_2_mag, breaks = 10, include.lowest = TRUE, ordered_result = TRUE)# use factor integer code
  )
```

```{r}
reg_ratio_PE_2_plot <- ggplot(df_by_sub_by_exam_PE2, aes(x = exam_num, y = reg_ratio, fill = PE_2_bin)) +
geom_bar(stat = "identity", position = "dodge") +
labs(
  title = paste0("Proportion of Regulation by PE2 Bin, Exam", sep=""),,
  x = "Exam Number",
  y = "Proportion of Regulation",
  fill = "PE2 Bin"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/v5/PE_reg/per_exam/PE2_reg_ratio_exam.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/v5/PE_reg/per_exam/PE2_reg_ratio_exam.pdf",height=4, width=6, dpi=300)

reg_ratio_PE_2_plot

reg_ratio_PE_2_abs_plot <- ggplot(df_by_sub_by_exam_PE2, aes(x = exam_num, y = reg_ratio, fill = PE_2_abs_bin)) +
geom_bar(stat = "identity", position = "dodge") +
labs(
  title = paste0("Proportion of Regulation by abs PE2 Bin, Exam", sep=""),,
  x = "Exam Number",
  y = "Proportion of Regulation",
  fill = "abs PE2 Bin"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/v5/abs_PE_reg/per_exam/abs_PE2_reg_ratio_exam.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/v5/abs_PE_reg/per_exam/abs_PE2_reg_ratio_exam.pdf",height=4, width=6, dpi=300)

reg_ratio_PE_2_abs_plot

```
##### Fig. EVPE vs. reg_ratio
```{r}
df_by_sub_by_exam_EVPE <- df_by_sub_by_exam_PE %>% filter(!is.na(EVPE))
df_by_sub_by_exam_EVPE <- df_by_sub_by_exam_EVPE %>% mutate(
    EVPE_bin = cut(EVPE, breaks = 10, include.lowest = TRUE, ordered_result = TRUE),
    EVPE_abs_bin = cut(EVPE_mag, breaks = 10, include.lowest = TRUE, ordered_result = TRUE)# use factor integer code
  )
```
```{r}
reg_ratio_EVPE_plot <- ggplot(df_by_sub_by_exam_EVPE, aes(x = exam_num, y = reg_ratio, fill = EVPE_bin)) +
geom_bar(stat = "identity", position = "dodge") +
labs(
  title = paste0("Proportion of Regulation by EVPE Bin, Exam", sep=""),,
  x = "Exam Number",
  y = "Proportion of Regulation",
  fill = "EVPE Bin"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/v5/PE_reg/per_exam/EVPE_reg_ratio_exam.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/v5/PE_reg/per_exam/EVPE_reg_ratio_exam.pdf",height=4, width=6, dpi=300)

reg_ratio_EVPE_plot

reg_ratio_EVPE_abs_plot <- ggplot(df_by_sub_by_exam_EVPE, aes(x = exam_num, y = reg_ratio, fill = EVPE_abs_bin)) +
geom_bar(stat = "identity", position = "dodge") +
labs(
  title = paste0("Proportion of Regulation by abs EVPE Bin, Exam", sep=""),,
  x = "Exam Number",
  y = "Proportion of Regulation",
  fill = "abs EVPE Bin"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/v5/abs_PE_reg/per_exam/abs_EVPE_reg_ratio_exam.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/v5/abs_PE_reg/per_exam/abs_EVPE_reg_ratio_exam.pdf",height=4, width=6, dpi=300)

reg_ratio_EVPE_abs_plot
```

```{r}
# select temporal information from df_no_na
df_select_time <- df_no_na %>% select(ID, exam_num, ResponseNumber, grade_reveal_time, RecordedDate, time_since_grade_reveal_mins, text_phrase, label_api_text, label_api, word_count)
```
```{r}
#transfer time into numeric format
df_select_time <- df_select_time %>% mutate(reveal_time_posix = mdy_hm(grade_reveal_time),
                                            record_time_posix = mdy_hm(RecordedDate))
#class(df_select_time$record_time_posix)
```
```{r}
df_by_resp_time <- df_select_time %>% dplyr::group_by (ID, exam_num, ResponseNumber, record_time_posix, time_since_grade_reveal_mins) %>% summarise (exp_count = sum(label_api_text == "Expression"),
    reg_count = sum(label_api_text == "Regulation"),
    nei_count = sum(label_api_text == "Neither"),
    exp_word_count = sum(word_count[label_api_text == "Expression"]),
    # Sum word_count ONLY for phrases with 'regulation' label
    reg_word_count = sum(word_count[label_api_text == "Regulation"]),
    # Sum word_count ONLY for phrases with 'neither' label
    nei_word_count = sum(word_count[label_api_text == "Neither"]),
    total_phrases = n(), 
    .groups = 'drop' # This tells dplyr to remove the grouping structure after summarise
  ) %>%
  dplyr::mutate(
    # Calculate ratios
    exp_ratio = exp_count / total_phrases,
    reg_ratio = reg_count / total_phrases,
    nei_ratio = nei_count / total_phrases
  ) %>%
  # Arrange by ID and time for time series modeling
  arrange(ID, time_since_grade_reveal_mins)

# df_by_resp_time$ID <- as.integer(df_by_resp_time$ID)
# df_by_resp_time_tmp <- df_by_resp_time %>%
#  rowid_to_column("original_row_index")
df_by_resp_time_PE <- inner_join(df_by_resp_time, df_PE, by=c("ID", "exam_num"))
```

```{r}
df_by_sub_resp_PE <- df_by_resp_time_PE[order(df_by_resp_time_PE$ID, df_by_resp_time_PE$exam_num, df_by_resp_time_PE$ResponseNumber, df_by_resp_time_PE$record_time_posix),]

df_by_sub_resp_PE_1_clean <- df_by_sub_resp_PE %>% filter(!is.na(PE_1))

#PE_1_is binned into 10 bins
df_by_sub_resp_PE_1 <- df_by_sub_resp_PE_1_clean %>% mutate(
    PE_1_bin = cut(PE_1, breaks = 10, include.lowest = TRUE, ordered_result = TRUE),
    PE_1_bin_label = as.character(PE_1_bin),
    PE_1_bin_id = paste0("bin_", as.integer(PE_1_bin))  # use factor integer code
  )

print(head(df_by_sub_resp_PE_1))
```

# Response-level ratio
```{r}
df_by_sub_resp_PE_1_plot <- df_by_sub_resp_PE_1 %>% group_by(exam_num, ResponseNumber, PE_1_binned) %>% summarise(sum_reg_count = sum(reg_count), sum_exp_count = sum(exp_count),
sum_nei_count = sum(nei_count), sum_reg_word = sum(reg_word_count), sum_exp_word = sum(exp_word_count), sum_nei_word = sum(nei_word_count), sum_abs_PE_1 = sum(PE_1_abs), .groups = 'drop')

df_by_sub_resp_abs_PE_1_plot <- df_by_sub_resp_PE_1 %>% group_by(exam_num, ResponseNumber, PE_1_abs_binned) %>% summarise(sum_reg_count = sum(reg_count), sum_exp_count = sum(exp_count),
sum_nei_count = sum(nei_count), sum_reg_word = sum(reg_word_count), sum_exp_word = sum(exp_word_count), sum_nei_word = sum(nei_word_count), sum_abs_PE_1 = sum(PE_1_abs), .groups = 'drop')
```

```{r}
df_abs_normalized <- df_by_sub_resp_abs_PE_plot %>%
  mutate(
    total_phrase_count = sum_reg_count + sum_exp_count + sum_nei_count,
    reg_prop = sum_reg_count / total_phrase_count,
    exp_prop = sum_exp_count / total_phrase_count
  )
```

```{r}
df_normalized <- df_by_sub_resp_PE_plot %>%
  mutate(
    total_phrase_count = sum_reg_count + sum_exp_count + sum_nei_count,
    reg_prop = sum_reg_count / total_phrase_count,
    exp_prop = sum_exp_count / total_phrase_count
  )
```

```{r}
bin_summary_table <- df_by_sub_resp_PE_clean %>%
  group_by(PE_1_binned) %>%
  summarise(
    Min_PE_in_Bin = min(PE_1, na.rm = TRUE), # na.rm=TRUE to handle potential NAs
    Max_PE_in_Bin = max(PE_1, na.rm = TRUE),
    Count_in_Bin = n(),
    .groups = 'drop'
  ) %>%
  # Optionally, arrange by bin order to make it neat
  arrange(PE_1_binned)

bin_summary_table
```
```{r}
#add the bin range to PE_df
df_num_normalized <- inner_join(df_normalized, bin_summary_table, by = "PE_1_binned")
```

```{r}
bin_abs_summary_table <- df_by_sub_resp_PE_clean %>%
  group_by(PE_1_abs_binned) %>%
  summarise(
    Min_PE_abs_in_Bin = min(PE_1_abs, na.rm = TRUE), # na.rm=TRUE to handle potential NAs
    Max_PE_abs_in_Bin = max(PE_1_abs, na.rm = TRUE),
    Count_in_Bin = n(),
    .groups = 'drop'
  ) %>%
  # Optionally, arrange by bin order to make it neat
  arrange(PE_1_abs_binned)

bin_abs_summary_table
```
```{r}
df_abs_num_normalized <- inner_join(df_abs_normalized, bin_abs_summary_table, by = "PE_1_abs_binned")
```


### reg_ratio vs.abs_PE
```{r}
for (i in 1:4){
  df_abs_normalized$PE_1_abs_binned_label <- as.character(df_abs_normalized$PE_1_abs_binned)
  df_normalized_exam_current <- df_abs_normalized %>% filter(exam_num == i)
  plotname_png <- paste0("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/v5/Figure/abs_PE_reg/abs_PE_reg_ratio_exam",i,".png",sep = "")
  plotname_pdf <- paste0("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/v5/Figure/abs_PE_reg/abs_PE_reg_ratio_exam",i,".pdf",sep = "")
  ggplot(df_normalized_abs_exam_current, aes(x = ResponseNumber, y = reg_prop, fill = PE_1_abs_binned_label)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ exam_num) +
  labs(
    title = paste0("Proportion of Regulation by abs(PE Bin, Exam)",i, sep=""),,
    x = "Response Number",
    y = "Proportion of Regulation",
    fill = "PE Bin (abs)"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # ggsave(plotname_png,height=4, width=5, dpi=300)
  # ggsave(plotname_pdf,height=4, width=5, dpi=300)
}
```
```{r}
df_normalized_abs_exam_current <- df_abs_num_normalized %>% filter(exam_num == i)
  plotname_png <- paste0("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/abs_PE_reg/abs_PE_reg_ratio_exam",i,".png",sep = "")
  plotname_pdf <- paste0("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/abs_PE_reg/abs_PE_reg_ratio_exam",i,".pdf",sep = "")
  ggplot(df_normalized_abs_exam_current, aes(x = ResponseNumber, y = reg_prop, fill = PE_1_abs_binned_num)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ exam_num) +
  labs(
    title = paste0("Proportion of Regulation by abs(PE Bin), Exam",i, sep=""),,
    x = "Response Number",
    y = "Proportion of Regulation",
    fill = "PE Bin (abs)"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### exp_ratio vs. abs_PE
```{r}
for (i in 1:4){
  df_normalized_abs_exam_current <- df_abs_normalized %>% filter(exam_num == i)
  plotname_png <- paste0("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/abs_PE_exp/abs_PE_exp_ratio_exam",i,".png",sep = "")
  plotname_pdf <- paste0("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/abs_PE_exp/abs_PE_exp_ratio_exam",i,".pdf",sep = "")
  ggplot(df_normalized_abs_exam_current, aes(x = ResponseNumber, y = exp_prop, fill = PE_1_abs_binned)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ exam_num) +
  labs(
    title = paste0("Proportion of Expression by abs(PE Bin), Exam",i, sep=""),,
    x = "Response Number",
    y = "Proportion of Expression",
    fill = "PE Bin (abs)"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  ggsave(plotname_png,height=4, width=5, dpi=300)
  ggsave(plotname_pdf,height=4, width=5, dpi=300)
}
```
### reg_ratio vs. PE
```{r}
for (i in 1:4){
  df_normalized_exam_current <- df_normalized %>% filter(exam_num == i)
  plotname_png <- paste0("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/PE_reg/PE_reg_ratio_exam",i,".png",sep = "")
  plotname_pdf <- paste0("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/PE_reg/PE_reg_ratio_exam",i,".pdf",sep = "")
  ggplot(df_normalized_exam_current, aes(x = ResponseNumber, y = reg_prop, fill = PE_1_binned)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ exam_num) +
  labs(
    title = paste0("Proportion of Regulation by PE Bin, Exam",i, sep=""),,
    x = "Response Number",
    y = "Proportion of Regulation",
    fill = "PE Bin"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  ggsave(plotname_png,height=4, width=5, dpi=300)
  ggsave(plotname_pdf,height=4, width=5, dpi=300)
}
```
### exp_ratio vs. PE
```{r}
for (i in 1:4){
  df_normalized_exam_current <- df_normalized %>% filter(exam_num == i)
  plotname_png <- paste0("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/PE_exp/PE_exp_ratio_exam",i,".png",sep = "")
  plotname_pdf <- paste0("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/PE_exp/PE_exp_ratio_exam",i,".pdf",sep = "")
  ggplot(df_normalized_exam_current, aes(x = ResponseNumber, y = exp_prop, fill = PE_1_binned)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ exam_num) +
  labs(
    title = paste0("Proportion of Expression by PE Bin, Exam",i, sep=""),,
    x = "Response Number",
    y = "Proportion of Expression",
    fill = "PE Bin"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  ggsave(plotname_png,height=4, width=5, dpi=300)
  ggsave(plotname_pdf,height=4, width=5, dpi=300)
}
```


### data prep
```{r}
df_by_exam_PE_plot <- df_by_sub_resp_PE %>% group_by(exam_num, bin_id) %>% summarise(sum_reg_count = sum(reg_count), sum_exp_count = sum(exp_count),
sum_nei_count = sum(nei_count), sum_reg_word = sum(reg_word_count), sum_exp_word = sum(exp_word_count), sum_nei_word = sum(nei_word_count), sum_abs_PE_1 = sum(PE_1_abs), .groups = 'drop')

df_by_exam_abs_PE_plot <- df_by_sub_resp_PE %>% group_by(exam_num,PE_1_abs_bin_id) %>% summarise(sum_reg_count = sum(reg_count), sum_exp_count = sum(exp_count),
sum_nei_count = sum(nei_count), sum_reg_word = sum(reg_word_count), sum_exp_word = sum(exp_word_count), sum_nei_word = sum(nei_word_count), sum_abs_PE_1 = sum(PE_1_abs), .groups = 'drop')
```

```{r}
df_abs_PE_exam_normalized <- df_by_exam_abs_PE_plot %>%
  mutate(
    total_phrase_count = sum_reg_count + sum_exp_count + sum_nei_count,
    reg_prop = sum_reg_count / total_phrase_count,
    exp_prop = sum_exp_count / total_phrase_count
  )
```

```{r}
df_PE_exam_normalized <- df_by_exam_PE_plot %>%
  mutate(
    total_phrase_count = sum_reg_count + sum_exp_count + sum_nei_count,
    reg_prop = sum_reg_count / total_phrase_count,
    exp_prop = sum_exp_count / total_phrase_count
  )
```

### reg_ratio vs. PE exam
```{r}
ggplot(df_abs_PE_exam_normalized, aes(x = exam_num, y = reg_prop, fill = PE_1_abs_bin_label)) +
geom_bar(stat = "identity", position = "dodge") +
scale_fill_viridis_d(option = "D") +
labs(
  title = paste0("Proportion of Regulation by abs(PE Bin), Exam", sep=""),
  x = "Exam Number",
  y = "Proportion of Regulation",
  fill = "PE Bin (abs)"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/abs_PE_reg/per_exam/abs_PE_reg_ratio_exam.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/abs_PE_reg/per_exam/abs_PE_reg_ratio_exam.pdf",height=4, width=6, dpi=300)
```
```{r}
ggplot(df_PE_exam_normalized, aes(x = exam_num, y = reg_prop, fill = PE_1_binned)) +
geom_bar(stat = "identity", position = "dodge") +
labs(
  title = paste0("Proportion of Regulation by PE Bin, Exam", sep=""),,
  x = "Exam Number",
  y = "Proportion of Regulation",
  fill = "PE Bin"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/PE_reg/per_exam/PE_reg_ratio_exam.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/PE_reg/per_exam/PE_reg_ratio_exam.pdf",height=4, width=6, dpi=300)
```

```{r}
ggplot(df_abs_PE_exam_normalized, aes(x = exam_num, y = exp_prop, fill = PE_1_abs_bin_label)) +
geom_bar(stat = "identity", position = "dodge") +
scale_fill_viridis_d(option = "D") +
labs(
  title = paste0("Proportion of Expression by abs(PE Bin), Exam", sep=""),,
  x = "Exam Number",
  y = "Proportion of Expression",
  fill = "PE Bin (abs)"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/abs_PE_exp/per_exam/abs_PE_exp_ratio_exam.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/abs_PE_exp/per_exam/abs_PE_exp_ratio_exam.pdf",height=4, width=6, dpi=300)
```

```{r}
ggplot(df_PE_exam_normalized, aes(x = exam_num, y = exp_prop, fill = PE_1_binned)) +
geom_bar(stat = "identity", position = "dodge") +
labs(
  title = paste0("Proportion of Expression by PE Bin, Exam", sep=""),,
  x = "Exam Number",
  y = "Proportion of Expression",
  fill = "PE Bin"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/PE_exp/per_exam/PE_exp_ratio_exam.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/PE_exp/per_exam/PE_exp_ratio_exam.pdf",height=4, width=6, dpi=300)
```

## 
```{r}
df_by_phrase_id <- df_no_na %>% dplyr::group_by(ID, exam_resp) %>% dplyr::mutate(phrase_id = as.integer(row_number())) %>% ungroup()
```

```{r}
library(dplyr)
library(tidyr)
df_by_phrase_id_exam1 <- df_by_phrase_id %>% filter(exam_num == 1, ResponseNumber == 2)
df_phrase_props_all <- df_by_phrase_id %>%
  dplyr::count(phrase_id, label_api_text) %>%
  complete(
    phrase_id,
    label_api_text = c("Expression", "Regulation", "Neither"),
    fill = list(n = 0)
  ) %>%
  group_by(phrase_id) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup()

df_phrase_props_15 <- df_phrase_props_all %>% filter(phrase_id <= 15)
```

```{r}
ggplot(df_phrase_props_15, aes(x = phrase_id, y = prop, group = label_api_text, color = label_api_text)) +
  geom_point(aes(size = n),alpha = 0.8) +
  geom_line() +
  labs(
    title = "Proportion of Labels by Phrase Index, all exams",
    x = "Phrase Index",
    y = "Proportion",
    color = "Label"
  ) +
  theme_minimal()
```
```{r}
df_per_subject <- df_by_phrase_id %>%
  dplyr::count(ID, phrase_id, label_api_text) %>%
  complete(ID, phrase_id, label_api_text = c("Expression", "Regulation", "Neither"), fill = list(n = 0)) %>%
  group_by(ID, phrase_id) %>%
  mutate(prop = n / sum(n)) %>%  # proportion within each phrase index for each subject
  ungroup()

df_summary <- df_per_subject %>%
  group_by(phrase_id, label_api_text) %>%
  summarise(
    mean_prop = mean(prop, na.rm = TRUE),
    var_prop = var(prop, na.rm = TRUE),   # <-- subject variance
    sd_prop = sd(prop, na.rm = TRUE),
    n = n(),
    se_prop = sd_prop / sqrt(n),
    .groups = "drop"
  )

df_summary <- df_summary %>%
  mutate(
    lower = mean_prop - se_prop,
    upper = mean_prop + se_prop
  )
```

```{r}
df_summary_15 <- df_summary %>% filter(phrase_id <= 15)

ggplot(df_summary_15, aes(x = phrase_id, y = mean_prop, color = label_api_text, fill = label_api_text)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, color = NA) +
  geom_line(size = 1) +
  labs(
    title = "Mean Proportion of Labels by Phrase Index (± SEM)",
    x = "Phrase Index",
    y = "Proportion",
    color = "Label",
    fill = "Label"
  ) +
  theme_minimal()

```

```{r}
ggplot(df_phrase_props_all, aes(x = phrase_id, y = prop, color = label_api_text)) +
  geom_point() +
  geom_line() +
  labs(
    title = "Proportion of Labels by Phrase Index, all exams",
    x = "Phrase Index",
    y = "Proportion",
    color = "Label"
  ) +
  theme_minimal()
```

```{r}
# df_subject_phrase_props <- df_by_phrase_id %>%
#   filter(exam_num == 1, ResponseNumber == 1) %>%
#   group_by(ID, phrase_id, label_api_text) %>%
#   summarise(n = n(), .groups = "drop") %>%
#   group_by(ID, phrase_id) %>%
#   mutate(prop = n / sum(n)) %>%
#   ungroup()

```
```{r}
# library(ggplot2)
# 
# ggplot(df_plot_indiv, aes(x = phrase_id, y = factor(ID), color = label_api_text)) +
#   geom_point(size = 2, alpha = 0.8) +
#   labs(
#     title = "Label Trajectory per Subject (Exam 1, Response 1)",
#     x = "Phrase Index",
#     y = "Subject ID",
#     color = "Label"
#   ) +
#   theme_minimal() +
#   theme(
#     axis.text.y = element_blank(),  # Hide long subject ID labels (optional)
#     axis.ticks.y = element_blank()
#   )
```
## Label transition: exp - reg
```{r}
exam_list <- c(1:4)
## reg and exp position relation
for (iExam in exam_list){
  df_by_phrase_id_posit <- df_by_phrase_id %>%
  filter(exam_num == iExam) %>%
  group_by(ID, ResponseNumber) %>%
  arrange(phrase_id) %>%
  mutate(
  prev_label = lag(label_api_text),
  follows_expression = label_api_text == "Regulation" & prev_label == "Expression"
  ) %>%
  summarise(prop_follow_expr = mean(follows_expression, na.rm = TRUE)) %>%
  ungroup() %>%
  filter(!is.na(prop_follow_expr))
  
  file_dir <- "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/label_transition/adjacent"
  if(!exists(file_dir)){
    dir.create(file_dir, recursive = TRUE)
  }
  filename_pdf <- paste0("/exp_reg_transition_exam", iExam,".pdf")
  filename_png <- paste0("/exp_reg_transition_exam", iExam,".png")
  plot_title <- paste0("Trend of Regulation Following Expression, Exam", iExam)
  ggplot(df_by_phrase_id_posit, aes(x = ResponseNumber, y = prop_follow_expr)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "loess", se = FALSE, color = "darkgreen") +
  labs(
    title = plot_title,
    x = "Responsse across all exams",
    y = "Proportion of Regulation Phrases that Follow Expression"
  ) +
  theme_minimal() 
  ggsave(paste0(file_dir,filename_pdf),height=4, width=6, dpi=300)
  ggsave(paste0(file_dir,filename_png),height=4, width=6, dpi=300)
}
```

```{r}
df_transitions <- df_by_phrase_id %>%
  filter(exam_num == 4) %>%
  group_by(ID, exam_resp) %>%
  arrange(phrase_id) %>%
  mutate(
    label_curr = label_api_text,
    label_prev = lag(label_api_text)
  ) %>%
  filter(!is.na(label_prev))  # remove first phrase of each response
```

```{r}
df_transition_counts <- df_transitions %>%
  dplyr::count(label_prev, label_curr, name = "n")

df_transition_props <- df_transition_counts %>%
  dplyr::group_by(label_prev) %>%
  dplyr::mutate(prop = n / sum(n)) %>%
  ungroup()
```
```{r}
library(ggplot2)

ggplot(df_transition_props, aes(x = label_prev, y = label_curr, fill = prop)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "white", high = "blue") +
  labs(
    title = "Transition Probabilities Between Labels",
    x = "Previous Phrase Label",
    y = "Current Phrase Label",
    fill = "Proportion"
  ) +
  theme_minimal()

```
```{r}
ggplot(df_transition_props, aes(x = label_prev, y = prop, fill = label_curr)) +
  geom_col(position = "dodge") +
  labs(
    title = "Label Transition Probabilities (Next Label by Previous Label), Exam 4",
    x = "Previous Label",
    y = "Proportion of Next Labels",
    fill = "Next Label"
  ) +
  theme_minimal()

```

### Exam: Non-repeat label transition
```{r}
for (iExam in exam_list){
  df_collapsed <- df_by_phrase_id %>%
    filter(exam_num == iExam) %>%
    arrange(ID, ResponseNumber, phrase_id) %>%
    group_by(ID, ResponseNumber) %>%
    summarise(
      label_seq = list(rle(label_api_text)$values),
      .groups = "drop"
    ) %>%
    mutate(
      from = map(label_seq, ~ head(.x, -1)),
      to = map(label_seq, ~ tail(.x, -1))
    ) %>%
    select(ID, ResponseNumber, from, to) %>%
    unnest(c(from, to))
  
  df_transition_counts <- df_collapsed %>%
    dplyr::count(from, to, name = "n")
  
  df_transition_props <- df_transition_counts %>%
    group_by(from) %>%
    mutate(prop = n / sum(n)) %>%
    ungroup()
  
  label_order <- c("Regulation", "Neither", "Expression")
  
  df_transition_props <- df_transition_props %>%
    mutate(
      from = factor(from, levels = label_order),
      to = factor(to, levels = label_order)
    )
  
  ggplot(df_transition_props, aes(x = from, y = to, fill = prop)) +
    geom_tile(color = "white") +
    scale_fill_gradient(low = "white", high = "skyblue4", limits = c(0,1)) +
    labs(
      title = paste0("Transition Probabilities (Collapsed Label Runs), Exam", iExam),
      x = "From Label",
      y = "To Label",
      fill = "Proportion"
    ) +
    theme_classic()
  file_dir <- "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/label_transition/collapsed"
  if(!dir.exists(file_dir)){
    dir.create(file_dir, recursive = TRUE)
  }
  filename_pdf <- paste0("/conf_label_transition_exam", iExam,".pdf")
  filename_png <- paste0("/conf_label_transition_exam", iExam,".png")
  ggsave(paste0(file_dir,filename_pdf),height=4, width=6, dpi=300)
  ggsave(paste0(file_dir,filename_png),height=4, width=6, dpi=300)
  
  label_order <- c("Regulation", "Neither", "Expression")

  df_transition_props <- df_transition_props %>%
    mutate(
      from = factor(from, levels = label_order),
      to = factor(to, levels = label_order),
      transition = paste(from, "→", to),
      prop_label = round(prop, 2)
    )
  write.csv(df_transition_props, paste0(file_dir, "/transition_props_exam", iExam, ".csv"), row.names = FALSE)

  ggplot(df_transition_props, aes(x = transition, y = prop, fill = from)) +
  geom_col( ) +
  geom_text(aes(label = prop_label), vjust = -0.3, size = 3.5) +
  labs(
    title = paste0("Transition Proportions Between Labels (Collapsed phrases), Exam",iExam),
    x = "transition",
    y = "Proportion",
    fill = "From Label"
  ) + 
  scale_y_continuous(limits = c(0, 1)) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  filename_pdf <- paste0("/bar_label_transition_exam", iExam,".pdf")
  filename_png <- paste0("/bar_label_transition_exam", iExam,".png")
ggsave(paste0(file_dir,filename_pdf),height=5, width=6, dpi=300)
ggsave(paste0(file_dir,filename_png),height=5, width=6, dpi=300)
}
```
```{r}
label_order <- c("Regulation", "Neither", "Expression")

df_transition_props <- df_transition_props %>%
  mutate(
    from = factor(from, levels = label_order),
    to = factor(to, levels = label_order),
    transition = paste(from, "→", to)
  )
```

### Response: Non-repeat label transition
```{r}
df_transitions_by_response <- df_by_phrase_id %>%
  arrange(ID, exam_num, ResponseNumber, phrase_id) %>%
  dplyr::group_by(ID, exam_num, ResponseNumber) %>%
  summarise(
    label_seq = list(rle(label_api_text)$values),
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    from = map(label_seq, ~ head(.x, -1)),
    to = map(label_seq, ~ tail(.x, -1))
  ) %>%
  select(exam_num, ResponseNumber, from, to) %>%
  unnest(c(from, to)) %>%
  dplyr::mutate(transition = paste(from, "→", to)) %>%
  dplyr::count(ResponseNumber, transition, name = "count")
  
  df_transitions_by_response <- df_transitions_by_response %>%
    dplyr::group_by(ResponseNumber) %>%
    dplyr::mutate(prop = count / sum(count)) %>%
    ungroup()
  
  # file_dir <- "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/label_transition/collapsed"
  # if(!dir.exists(file_dir)){
  #   dir.create(file_dir, recursive = TRUE)
  # }
  # filename_pdf <- paste0("/conf_label_transition_exam", iExam,".pdf")
  # filename_png <- paste0("/conf_label_transition_exam", iExam,".png")
  # ggsave(paste0(file_dir,filename_pdf),height=4, width=6, dpi=300)
  # ggsave(paste0(file_dir,filename_png),height=4, width=6, dpi=300)
  
  # label_order <- c("Regulation", "Neither", "Expression")

  ggplot(df_transitions_by_response, aes(x = ResponseNumber, y = prop, color = transition)) +
  geom_line(size = 1) +
  geom_point() +
  labs(
    title = "Label Transition Counts Across Responses",
    x = "Response Number",
    y = "Prop of Transitions",
    color = "Transition"
  ) + theme_minimal()
#   filename_pdf <- paste0("/bar_label_transition_exam", iExam,".pdf")
#   filename_png <- paste0("/bar_label_transition_exam", iExam,".png")
# ggsave(paste0(file_dir,filename_pdf),height=5, width=6, dpi=300)
# ggsave(paste0(file_dir,filename_png),height=5, width=6, dpi=300)
```

# Analysis


## Distribution
```{r}
hist(df_by_sub$Regulation, breaks = 30, main = "Distribution of Regulation Phrases", xlab = "Regulation count")
```
```{r}
mean_val <- mean(df_by_sub$Regulation)
var_val <- var(df_by_sub$Regulation)
mean_val
var_val
```
## lmer
###PE_1 vs. reg_ratio
```{r}
df_by_exam_select <- df_no_na %>% select (exam_num, ID, text, label_api_text, label_api, word_count)

df_by_exam <- df_by_exam_select %>% dplyr::count(ID, exam_num, label_api_text) %>% pivot_wider(names_from = label_api_text, values_from = n, values_fill = 0)

df_by_exam <- df_by_exam %>% mutate(total = Expression + Neither + Regulation,
                                  exp_ratio = Expression/total,
                                  nei_ratio = Neither/total,
                                  reg_ratio = Regulation/total
                                              )

df_by_exam_long <- df_by_exam %>%
  select(ID, exam_num, Expression, exp_ratio, Neither, nei_ratio, Regulation, reg_ratio ) %>%
  pivot_longer(cols = c(exp_ratio, nei_ratio, reg_ratio),
               names_to = "label", values_to = "count") %>%
  dplyr::group_by(ID, exam_num) %>%
  ungroup()
```

```{r}
# The total word count of each label, per exam
df_by_exam_word_count <- df_select %>% group_by(ID, exam_num, label_api_text) %>% summarise(sum_word_count = sum(word_count), .groups = "drop")

# The wide format
df_by_exam_word_count_wide <- df_by_exam_word_count %>% group_by(ID, exam_num) %>% pivot_wider(names_from = label_api_text, values_from = sum_word_count)

df_by_exam_word_count_wide <- df_by_exam_word_count_wide %>% mutate(across(where(is.numeric), ~replace(.,is.na(.), 0)))

df_by_exam_word_count_wide <- df_by_exam_word_count_wide %>% group_by(ID, exam_num) %>%
  mutate(exam_total_word = sum(Expression + Regulation + Neither),
         exp_word_ratio = Expression/exam_total_word,
         reg_word_ratio = Regulation/exam_total_word,
         nei_word_ratio = Neither/exam_total_word)
```
```{r}
df_by_exam_comp <- inner_join(df_by_exam, df_by_exam_word_count_wide, by = c("ID", "exam_num"))
```

```{r}
## Combine ema with PE
df_by_exam_pe <- inner_join(df_by_exam_comp, df_PE, by=c("ID", "exam_num"))
```
## Adding sentiment
```{r}
df_resp_senti <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/emaData_F24_sentiment_resp_sd_full.csv")

df_resp_senti <- df_resp_senti %>% dplyr::group_by(ID, exam_num) %>% dplyr::mutate(exam_senti = mean(sentiment))

df_exam_senti_select <- df_resp_senti %>% distinct(ID, exam_num, .keep_all = TRUE)

```
```{r}
df_by_exam_pe_senti <- inner_join(df_by_exam_pe, df_exam_senti_select, by=c("ID", "exam_num"))
```
### PE vs senti
```{r}
lmer_PE_1_exam_senti <- lmer(exam_senti ~ PE_1 + (1 | ID), data = df_by_exam_pe_senti)
summary(lmer_PE_1_exam_senti)
```
```{r}
lmer_PE_2_exam_senti <- lmer(exam_senti ~ PE_2 + (1 | ID), data = df_by_exam_pe_senti)
summary(lmer_PE_2_exam_senti)

```
```{r}
lmer_EVPE_exam_senti <- lmer(exam_senti ~ EVPE + (1 | ID), data = df_by_exam_pe_senti)
summary(lmer_EVPE_exam_senti)
```
```{r}
r_value  <- lmer_EVPE_exam_senti$estimate
p_value  <- lmer_EVPE_exam_senti$p.value
#r2_value <- r_value^2
```

### Plotting
```{r}
EVPE_exam_senti_plot <- ggplot(df_by_exam_pe_senti, aes(x=EVPE, y=exam_senti)) +
   geom_point(size = 2, alpha = 0.6, color = "skyblue2") +
  geom_smooth(method = "lm", se = TRUE, color = "skyblue4") +
  labs(
    x = "PE",
    y = "Exam sentiment"
  ) +
  theme(axis.text = element_text(size = 16),
        text = element_text(family = "sans",size = 14)) +
  theme_classic()
  ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Fig0_EVPE_exam_senti.png",EVPE_exam_senti_plot,height=5, width=4, dpi=300)
  ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Fig0_EVPE_exam_senti.pdf",EVPE_exam_senti_plot,height=5, width=4, dpi=300)
  ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Fig0_EVPE_exam_senti.eps",EVPE_exam_senti_plot,height=5, width=4, dpi=300)
  ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/Fig0_EVPE_exam_senti.png",EVPE_exam_senti_plot,height=4, width=6, dpi=300)
  ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/Fig0_EVPE_exam_senti.pdf",EVPE_exam_senti_plot,height=4, width=6, dpi=300)
  ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/Fig0_EVPE_exam_senti.eps",EVPE_exam_senti_plot,height=4, width=6, dpi=300)
EVPE_exam_senti_plot
```

```{r}
df_by_exam_pe_senti <- df_by_exam_pe_senti %>%
  mutate(
    PE_1_z = scale(PE_1)[,1],
    PE_2_z = scale(PE_2)[,1],
    EVPE_z = scale(EVPE)[,1]
  )
```

```{r}
lmer_PE_1_PE_2_EVPE_exam_senti <- lmer(exam_senti ~ PE_1_z + PE_2_z + EVPE_z + (1 | ID), data = df_by_exam_pe_senti)
summary(lmer_PE_1_PE_2_EVPE_exam_senti)
```
```{r}
fixef(lmer_PE_1_PE_2_EVPE_exam_senti)
```

```{r}
reg_senti_model <- lmer(reg_word_ratio ~ exam_senti + (1 | ID)+(1|exam_num), data = df_by_exam_pe_senti)

summary(reg_senti_model)
```
```{r}
PE_1_reg_model <- lmer(reg_word_ratio ~ PE_1 + (1 | ID), data = df_by_exam_pe_senti)

summary(PE_1_reg_model)
```
```{r}
pp_check(PE_1_reg_model)
```
```{r}
PE_1_reg_word <- lmer(reg_word_ratio ~ PE_1 + (1|exam_num) + (1 | ID), data = df_by_exam_pe_senti)

summary(PE_1_reg_word)
```
```{r}
PE_1_reg_word_senti <- lmer(reg_word_ratio ~ PE_1 + exam_senti+ (1 | ID) + (1|exam_num), data = df_by_exam_pe_senti)

summary(PE_1_reg_word_senti)
```
```{r}
PE_1_reg_word_senti_inx <- lmer(reg_word_ratio ~ PE_1 * exam_senti+ (1 | ID)+(1|exam_num), data = df_by_exam_pe_senti)

summary(PE_1_reg_word_senti_inx)
anova(PE_1_reg_word_senti_inx)
```

#### PE_1 reg model comparison
```{r}
anova(PE_1_reg_word,PE_1_reg_word_senti, PE_1_reg_word_senti_inx)
AIC(reg_senti_model,PE_1_reg_word,PE_1_reg_word_senti, PE_1_reg_word_senti_inx)
BIC(reg_senti_model,PE_1_reg_word,PE_1_reg_word_senti, PE_1_reg_word_senti_inx)
```
```{r}
nobs(reg_senti_model )
nobs(PE_1_reg_word)
nobs(PE_1_reg_word_senti)
nobs(PE_1_reg_word_senti_inx)
```

```{r}
library(tibble)
library(dplyr)

model_table <- tribble(
  ~Outcome, ~Model, ~AIC, ~BIC, ~logLik, ~Delta_AIC,
  "Expression proportion", "PE_1", -996.7, -969.60, 503.35, 128.3,
  "Expression proportion", "PE_1 + exam_senti", -1019.5, -986.96, 515.74, 105.5,
  "Expression proportion", "PE_1 * exam_senti", -1125.0, -1087.07, 569.51, 0.0,
  "Regulation proportion", "PE_1", -1112.2, -1085.2, 561.13, 140.0,
  "Regulation proportion", "PE_1 + exam_senti", -1130.2, -1097.6, 571.07, 122.0,
  "Regulation proportion", "PE_1 * exam_senti", -1252.2, -1214.2, 633.08, 0.0
) %>%
  group_by(Outcome) %>%
  mutate(
    Delta_AIC = AIC - min(AIC)
  ) %>%
  ungroup()
```
```{r}
library(gt)

gt_tbl <- model_table %>%
  gt(groupname_col = "Outcome") %>%
  tab_header(
    title = md("**Table II**"),
    subtitle = md("Model Comparison of Mixed-Effects Models for PE_1")
  ) %>%
  cols_label(
    Model = "Model predictors",
    AIC = "AIC",
    BIC = "BIC",
    logLik = "logLik",
    Delta_AIC = md("&Delta;AIC (model − final model)")
  ) %>%
  fmt_number(
    columns = c(AIC, BIC, logLik, Delta_AIC),
    decimals = 2
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      rows = Delta_AIC == 0
    )
  ) %>%
  tab_options(
    table.font.names = "Times New Roman"
  ) %>%
  tab_source_note(
    source_note = md("**Note.** Lower AIC/BIC values indicate better model fit. Bolded rows indicate the best-fitting model within each outcome.")
  )
```
```{r}
gt_tbl
```
```{r}
gtsave(gt_tbl, "PE_1_reg_model_comparison_table_new.pdf")
```

#### Cor_plot
```{r}
## correlation plot
rvalue=with(df_by_exam_pe, cor.test(PE_1, reg_ratio, use = "complete.obs"))
rhovalue=with(df_by_exam_pe, cor.test(PE_1, reg_ratio, use = "complete.obs", method="spearman",exact=FALSE ))

ggplot(df_by_exam_pe, aes(x=PE_1, y=reg_ratio)) +
  geom_point() +
  geom_smooth(method = "lm") +
  annotate("text", size= 4, x=Inf, y = Inf, label =paste("r = ", round(as.numeric(rvalue[4]), digits=2), " p = ", round(as.numeric(rvalue[3]), digits=2)," pRho = ", round(as.numeric(rhovalue[3]), digits=2), " n = ", round(as.numeric(rvalue[2])+2, digits=2)),colour = "black",vjust=1.15, hjust=1.1)+
  labs(
    title = "PE_1 vs. Regulation ratio",
    x = "Prediction error before taking exam",
    y = "Regulation ratio per exam"
  )
  theme_classic()
  ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Fig6_PE_reg_ratio.png",height=4, width=5, dpi=300)
  ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Fig6_PE_reg_ratio.pdf",height=4, width=5, dpi=300)
```
### PE_1_val vs. reg_ratio
```{r}
PE_1_val_reg_model <- lmer(reg_ratio ~ PE_1_val + (1 | ID), data = df_by_exam_pe)

summary(PE_1_val_reg_model)
```
```{r}
plot_model(PE_1_val_reg_model)
```

```{r}
pp_check(PE_1_val_reg_model)
```

```{r}
PE_1_mag_reg_model <- lmer(reg_ratio ~ PE_1_mag + (1 | ID), data = df_by_exam_pe)

summary(PE_1_mag_reg_model)
```
```{r}
PE_1_val_mag_reg_model <- lmer(reg_ratio ~ PE_1_mag + PE_1_val + PE_1_mag*PE_1_val +0+ (1 | ID), data = df_by_exam_pe)

summary(PE_1_val_mag_reg_model)
```
### PE_1 vs. exp_ratio
```{r}
PE_1_exp_model <- lmer(exp_ratio ~ PE_1 + (1 | ID), data = df_by_exam_pe)

summary(PE_1_exp_model)
```
```{r}
pp_check(PE_1_exp_model)
```

```{r}
PE_1_val_exp_model <- lmer(exp_ratio ~ PE_1_val + (1 | ID), data = df_by_exam_pe)

summary(PE_1_val_exp_model)
```

```{r}
PE_1_mag_exp_model <- lmer(exp_ratio ~ PE_1_mag + (1 | ID), data = df_by_exam_pe)

summary(PE_1_mag_exp_model)
```

```{r}
PE_1_val_mag_exp_model <- lmer(exp_ratio ~ PE_1_val + PE_1_mag + PE_1_val*PE_1_mag + 0+ (1 | ID), data = df_by_exam_pe)

summary(PE_1_val_mag_exp_model)
```
#### PE_1 vs. exp_word_ratio
```{r}
PE_1_exp_ratio <- lmer(exp_word_ratio ~ PE_1 + (1|ID) + (1|exam_num), data = df_by_exam_pe_senti)

summary(PE_1_exp_ratio)
```
```{r}
PE_1_exp_ratio_senti <- lmer(exp_word_ratio ~ PE_1 + exam_senti + (1|ID) + (1|exam_num), data = df_by_exam_pe_senti)

summary(PE_1_exp_ratio_senti)
```
```{r}
PE_1_exp_ratio_senti_inx <- lmer(exp_word_ratio ~ PE_1 * exam_senti + (1|ID) + (1|exam_num), data = df_by_exam_pe_senti)

summary(PE_1_exp_ratio_senti_inx)
```
#### PE_1 vs. exp model comparison
```{r}
anova(PE_1_exp_ratio,PE_1_exp_ratio_senti, PE_1_exp_ratio_senti_inx)
AIC(PE_1_exp_ratio,PE_1_exp_ratio_senti, PE_1_exp_ratio_senti_inx)
BIC(PE_1_exp_ratio,PE_1_exp_ratio_senti, PE_1_exp_ratio_senti_inx)
```

#### Cor_plot
```{r}
## correlation plot
rvalue=with(df_by_exam_pe, cor.test(PE_1, exp_ratio, use = "complete.obs"))
rhovalue=with(df_by_exam_pe, cor.test(PE_1, exp_ratio, use = "complete.obs", method="spearman",exact=FALSE ))
ggplot(df_by_exam_pe, aes(x=PE_1, y=exp_ratio)) +
  geom_point() +
  geom_smooth(method = "lm") +
  annotate("text", size= 4, x=Inf, y = Inf, label =paste("r = ", round(as.numeric(rvalue[4]), digits=2), " p = ", round(as.numeric(rvalue[3]), digits=2)," pRho = ", round(as.numeric(rhovalue[3]), digits=2), " n = ", round(as.numeric(rvalue[2])+2, digits=2)),colour = "black",vjust=1.15, hjust=1.1)+
  labs(
    title = "PE_1 vs. Expression ratio",
    x = "Prediction error before taking exam",
    y = "Expression ratio per exam"
  )
  theme_classic()
  ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Fig7_PE_exp_ratio.png",height=4, width=5, dpi=300)
  ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Fig7_PE_exp_ratio.pdf",height=4, width=5, dpi=300)
```

### PE2 vs. reg_ratio
```{r}
pe2_reg_model <- lmer(reg_word_ratio ~ PE_2 + (1 | ID) + (1|exam_num), data = df_by_exam_pe_senti)

summary(pe2_reg_model)
```
```{r}
pp_check(pe2_reg_model)
```

```{r}
pe2_reg_senti_model <- lmer(reg_word_ratio ~ PE_2 + exam_senti+ (1 | ID) + (1|exam_num), data = df_by_exam_pe_senti)

summary(pe2_reg_senti_model)
```
```{r}
pe2_reg_senti_model_inx <- lmer(reg_word_ratio ~ PE_2 * exam_senti+ (1 | ID) + (1|exam_num), data = df_by_exam_pe_senti)

summary(pe2_reg_senti_model_inx)
```
#### PE_2 vs reg model comparison
```{r}
anova(pe2_reg_model,pe2_reg_senti_model,pe2_reg_senti_model_inx)
AIC(pe2_reg_model,pe2_reg_senti_model,pe2_reg_senti_model_inx)
BIC(pe2_reg_model,pe2_reg_senti_model,pe2_reg_senti_model_inx)
```

```{r}
## correlation plot
rvalue=with(df_by_exam_pe, cor.test(PE_2, reg_ratio, use = "complete.obs"))
rhovalue=with(df_by_exam_pe, cor.test(PE_2, reg_ratio, use = "complete.obs", method="spearman",exact=FALSE ))
ggplot(df_by_exam_pe, aes(x=PE_2, y=reg_ratio)) +
  geom_point() +
  geom_smooth(method = "lm") +
  annotate("text", size= 4, x=Inf, y = Inf, label =paste("r = ", round(as.numeric(rvalue[4]), digits=2), " p = ", round(as.numeric(rvalue[3]), digits=2)," pRho = ", round(as.numeric(rhovalue[3]), digits=2), " n = ", round(as.numeric(rvalue[2])+2, digits=2)),colour = "black",vjust=1.15, hjust=1.1)+
  labs(
    title = "PE_2 vs. Regulation ratio",
    x = "Prediction error after taking exam",
    y = "Regulation ratio per exam"
  ) +
  theme_classic()
  ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Fig8_PE2_reg_ratio.png",height=4, width=5, dpi=300)
  ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Fig8_PE2_reg_ratio.pdf",height=4, width=5, dpi=300)
```
```{r}
pe2_val_reg_model <- lmer(reg_ratio ~ PE_2_val + (1 | ID), data = df_by_exam_pe)

summary(pe2_val_reg_model)
```
```{r}
pe2_mag_reg_model <- lmer(reg_ratio ~ PE_2_mag + (1 | ID), data = df_by_exam_pe)

summary(pe2_mag_reg_model)
```
```{r}
pe2_val_mag_reg_model <- lmer(reg_ratio ~ PE_2_val*PE_2_mag + (1|exam_num) + (1 | ID), data = df_by_exam_pe)

summary(pe2_val_mag_reg_model)
```
```{r}
pe2_val_mag_reg_model_total <- lmer(reg_ratio ~ PE_2_val*PE_2_mag + total+(1|exam_num) + (1|ID), data = df_by_exam_pe)

summary(pe2_val_mag_reg_model_total)
```
```{r}
plot_model(pe2_val_mag_reg_model_total, type = "int")
```

### PE2_1 vs. exp_ratio
```{r}
pe2_exp_model <- lmer(exp_ratio ~ PE_2 + (1 | ID), data = df_by_exam_pe)

summary(pe2_exp_model)
```
```{r}
pp_check(pe2_exp_model)
```

### PE_2 vs. exp_word_ratio
```{r}
PE2_exp_word_model <- lmer(exp_word_ratio ~ PE_2 + (1 | ID) + (1|exam_num), data = df_by_exam_pe_senti)

summary(PE2_exp_word_model)
```
```{r}
pp_check(PE2_exp_word_model)
```
```{r}
PE2_exp_word_senti_model <- lmer(exp_word_ratio ~ PE_2 + exam_senti + (1 | ID) + (1|exam_num), data = df_by_exam_pe_senti)

summary(PE2_exp_word_senti_model)
```
```{r}
PE2_exp_word_senti_model_inx <- lmer(exp_word_ratio ~ PE_2 * exam_senti + (1 | ID) + (1|exam_num), data = df_by_exam_pe_senti)

summary(PE2_exp_word_senti_model_inx)
```
#### PE_2 exp model comparison
```{r}
anova(PE2_exp_word_model,PE2_exp_word_senti_model,PE2_exp_word_senti_model_inx)
AIC(PE2_exp_word_model,PE2_exp_word_senti_model,PE2_exp_word_senti_model_inx)
BIC(PE2_exp_word_model,PE2_exp_word_senti_model,PE2_exp_word_senti_model_inx)
```
#### PE_2 table
```{r}
library(tibble)
library(dplyr)

pe2_model_table <- tribble(
  ~Outcome,            ~Model,                   ~AIC,     ~BIC,      ~logLik, ~Chisq,    ~Df, ~p,
  "Expression proportion",  "PE_2",                   -1015.8,  -988.06,   512.91,  NA,        NA,  NA,
  "Expression proportion",  "PE_2 + exam_senti",      -1018.8,  -985.44,   515.38,  4.9382,    1,   0.02627,
  "Expression proportion",  "PE_2 * exam_senti",      -1176.5,  -1137.63,  595.25,  159.7392,  1,   NA,

  "Regulation proportion",  "PE_2",                   -1266.1,  -1238.3,   638.03,  NA,        NA,  NA,
  "Regulation proportion",  "PE_2 + exam_senti",      -1265.6,  -1232.3,   638.82,  1.5709,    1,   0.2101,
  "Regulation proportion",  "PE_2 * exam_senti",      -1468.8,  -1429.9,   741.39,  205.1493,  1,   NA
) %>%
  group_by(Outcome) %>%
  mutate(Delta_AIC = AIC - min(AIC)) %>%
  ungroup() %>%
  mutate(
    p_label = case_when(
      is.na(p) & Model == "PE_2" ~ "—",
      Model == "PE_2 * exam_senti" ~ "< .001",
      TRUE ~ sprintf("%.3f", p)
    ),
    Chisq_label = ifelse(is.na(Chisq), "—", sprintf("%.2f", Chisq)),
    Df_label = ifelse(is.na(Df), "—", as.character(Df))
  )
```
```{r}
library(gt)

pe2_gt_tbl <- pe2_model_table %>%
  select(Outcome, Model, AIC, BIC, logLik, Delta_AIC, Chisq_label, Df_label, p_label) %>%
  gt(groupname_col = "Outcome") %>%
  tab_header(
    title = md("**Table III**"),
    subtitle = md("Model Comparison of Mixed-Effects Models for PE_2")
  ) %>%
  cols_label(
    Model = "Model predictors",
    AIC = "AIC",
    BIC = "BIC",
    logLik = "logLik",
    Delta_AIC = md("&Delta;AIC (model − final model)"),
    Chisq_label = md("&chi;<sup>2</sup>"),
    Df_label = "Df",
    p_label = md("*p*")
  ) %>%
  fmt_number(
    columns = c(AIC, BIC, logLik, Delta_AIC),
    decimals = 2
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(rows = Delta_AIC == 0)
  ) %>%
  tab_options(
    table.font.size = px(16),
    heading.title.font.size = px(22),
    heading.subtitle.font.size = px(18),
    row_group.font.weight = "bold",
    table.border.top.width = px(2),
    table.border.bottom.width = px(2),
    column_labels.border.bottom.width = px(1.5),
    data_row.padding = px(6),
    table.font.names = "Times New Roman"
  ) %>%
  tab_source_note(
    source_note = md("*Note.* Lower AIC and BIC values indicate better model fit. Bolded rows indicate the best-fitting model within each outcome.")
  )
```
```{r}
pe2_gt_tbl
gtsave(pe2_gt_tbl, "PE2_model_comparison_table_new.pdf")
```

```{r}
## correlation plot
rvalue=with(df_by_exam_pe, cor.test(PE_2, exp_ratio, use = "complete.obs"))
rhovalue=with(df_by_exam_pe, cor.test(PE_2, exp_ratio, use = "complete.obs", method="spearman",exact=FALSE ))
ggplot(df_by_exam_pe, aes(x=PE_2, y=exp_ratio)) +
  geom_point() +
  geom_smooth(method = "lm") +
  annotate("text", size= 4, x=Inf, y = Inf, label =paste("r = ", round(as.numeric(rvalue[4]), digits=2), " p = ", round(as.numeric(rvalue[3]), digits=2)," pRho = ", round(as.numeric(rhovalue[3]), digits=2), " n = ", round(as.numeric(rvalue[2])+2, digits=2)),colour = "black",vjust=1.15, hjust=1.1)+
  labs(
      title = "PE_2 vs. Expression ratio",
      x = "Prediction error after taking exam",
      y = "Expression ratio per exam"
    )+
    theme_classic()
    ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Fig9_PE2_exp_ratio.png",height=4, width=5, dpi=300)
    ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Fig9_PE2_exp_ratio.pdf",height=4, width=5, dpi=300)
```
```{r}
pe2_val_exp_model <- lmer(exp_ratio ~ PE_2_val + (1 | ID), data = df_by_exam_pe)

summary(pe2_val_exp_model)
```
```{r}
pp_check(pe2_val_exp_model)
```
```{r}
pe2_mag_exp_model <- lmer(exp_ratio ~ PE_2_mag + (1 | ID), data = df_by_exam_pe)

summary(pe2_mag_exp_model)
```
```{r}
pe2_val_mag_exp_model <- lmer(exp_ratio ~ PE_2_val * PE_2_mag + (1 | ID), data = df_by_exam_pe)

summary(pe2_val_mag_exp_model)
```

#### Final: EVPE vs. reg_ratio
```{r}
EVPE_reg_model <- lmer(reg_ratio ~ EVPE + (1 | ID), data = df_by_exam_pe)

summary(EVPE_reg_model)
```
```{r}
pp_check(EVPE_reg_model)
```
```{r}
EVPE_reg_word_model <- lmer(reg_word_ratio ~ EVPE + (1 | ID), data = df_by_exam_pe)

summary(EVPE_reg_word_model)
```

```{r}
library(ggeffects)
library(ggplot2)

EVPE_reg_plot <- ggpredict(
  EVPE_reg_model,
  terms = "EVPE"
)

EVPE_reg_plot_df <- as.data.frame(EVPE_reg_plot)
```
```{r}
ggplot() +
  # Original data
  geom_point(
    data = df_by_exam_pe,
    aes(x = EVPE, y = reg_ratio),
    alpha = 0.3,
    color = "lightskyblue1",
    size = 2
  ) +

  # 95% CI
  geom_ribbon(
    data = EVPE_reg_plot_df,
    aes(
      x = x,
      ymin = conf.low,
      ymax = conf.high
    ),
    fill = "skyblue3",
    alpha = 0.2
  ) +

  # Model-estimated line
  geom_line(
    data = EVPE_reg_plot_df,
    aes(x = x, y = predicted),
    color = "skyblue3",
    linewidth = 1.2
  ) +

  coord_cartesian(xlim = c(-40, 40)) +

  labs(
    x = "Prediction Error",
    y = "Regulation Proportion"
  ) +

  theme_classic()
ggsave("/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/reg_prop_EVPE.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/reg_prop_EVPE.pdf",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/reg_prop_EVPE.eps",height=4, width=6, dpi=300)
```



#### EVPE vs reg_word_ratio + exam_senti
```{r}
EVPE_reg_word_model <- lmer(reg_word_ratio ~ EVPE + (1 | ID)+(1|exam_num), data = df_by_exam_pe_senti)

summary(EVPE_reg_word_model)
```

```{r}
EVPE_reg_word_model_senti <- lmer(reg_word_ratio ~ EVPE +exam_senti+ (1 | ID)+(1|exam_num), data = df_by_exam_pe_senti)

summary(EVPE_reg_word_model_senti)
```
```{r}
EVPE_reg_word_model_senti_int <- lmer(reg_word_ratio ~ EVPE *exam_senti+ (1 | ID)+(1|exam_num), data = df_by_exam_pe_senti)

summary(EVPE_reg_word_model_senti_int)
```

##### Mediation model
```{r}
install.packages("mediation")
library(mediation)
```
```{r}
library(brms)
library(dplyr)

df_med <- df_by_exam_pe_senti %>%
  mutate(
    subject_id = factor(ID),
    exam_id = factor(exam_num)
  ) %>%
  select(
    subject_id,
    exam_id,
    EVPE,
    exam_senti,
    reg_ratio
  ) %>%
  filter(
    complete.cases(
      EVPE,
      exam_senti,
      reg_ratio,
      subject_id,
      exam_id
    )
  )

str(df_med)

sapply(df_med, class)
```
```{r}
table(df_by_exam_pe_senti$reg_ratio == 0)

table(df_by_exam_pe_senti$reg_ratio == 1)
```
```{r}

```


```{r}

library(brms)

bf_mediator <- bf(
  exam_senti ~ 1 + EVPE +
    (1 | gr(subject_id)) +
    (1 | gr(exam_id)),
  family = gaussian()
)

bf_outcome <- bf(
  reg_ratio ~ 1 + EVPE + exam_senti +
    (1 | gr(subject_id)) +
    (1 | gr(exam_id)),
  family = gaussian()
)

med_fit <- brm(
  bf_mediator +
    bf_outcome +
    set_rescor(FALSE),
  data = df_med,
  chains = 4,
  cores = 4,
  iter = 4000,
  warmup = 2000,
  control = list(
    adapt_delta = 0.95,
    max_treedepth = 12
  ),
  seed = 1234
)

summary(med_fit)
fixef(med_fit, summary = TRUE)
```
```{r}
library(posterior)
library(dplyr)

draws <- as_draws_df(med_fit)

draws <- draws %>%
  mutate(
    indirect = b_examsenti_EVPE * b_regratio_exam_senti,
    direct   = b_regratio_EVPE,
    total    = direct + indirect
  )
```
```{r}
draws %>%
  summarise(
    indirect_est = median(indirect),
    indirect_l95 = quantile(indirect, .025),
    indirect_u95 = quantile(indirect, .975),
    p_positive   = mean(indirect > 0)
  )
```
#####Mediation zero-inflated
```{r}
m_reg <- brm(
  bf(
    reg_ratio ~ EVPE + exam_senti +
      (1 | ID) +
      (1 | exam_num),
    zoi ~ 1,
    coi ~ 1,
    phi ~ 1
  ),
  family = zero_one_inflated_beta(),
  data = df_by_exam_pe_senti,
  chains = 4,
  cores = 4,
  iter = 4000,
  control = list(adapt_delta = 0.99)
)

summary(m_reg)
```
```{r}
m_med <- brm(
  exam_senti ~ EVPE +
    (1 | ID) +
    (1 | exam_num),
  data = df_by_exam_pe_senti
)
```
```{r}
variables(m_reg)
variables(m_med)
```

```{r}
draws_med <- posterior::as_draws_df(m_med)
draws_reg <- posterior::as_draws_df(m_reg)

indirect <-
  draws_med$b_EVPE *
  draws_reg$b_exam_senti

summary(indirect)
```
```{r}
quantile(indirect, c(0.025, 0.5, 0.975))

mean(indirect > 0)
```

```{r}
m_gaussian <- brm(
  reg_ratio ~ EVPE + exam_senti +
    (1 | ID) +
    (1 | exam_num),
  family = gaussian(),
  data = df_by_exam_pe_senti
)
summary(m_gaussian)
```

```{r}
m1 <- add_criterion(m_gaussian, "loo")
m2 <- add_criterion(m_reg, "loo")
loo_compare(m1, m2)
```


```{r}
bf_med <- bf(exam_senti ~ EVPE + (1 | ID) + (1 | exam_num))

bf_reg <- bf(
  reg_ratio ~ EVPE + exam_senti + (1 | ID) + (1 | exam_num),
  zoi ~ 1,
  coi ~ 1,
  phi ~ 1
)

fit_joint <- brm(
  bf_med + bf_reg + set_rescor(FALSE),
  family = list(gaussian(), zero_one_inflated_beta()),
  data = df_by_exam_pe_senti
)
```

### model plotting
```{r}
tab_model(EVPE_reg_word_model_senti_int, PE_1_reg_word_senti_inx,pe2_reg_senti_model_inx, dv.labels = "Regulation proportion")
```
```{r}
library(tibble)
add_stars <- function(p) {
  case_when(
    p < 0.001 ~ "***",
    p < 0.01  ~ "**",
    p < 0.05  ~ "*",
    TRUE ~ ""
  )
}
```

```{r}
library(tibble)
library(gt)
library(webshot2)

df_exp <- tribble(
  ~Predictor, ~EVPE_est, ~EVPE_ci, ~EVPE_p, ~PE1_est, ~PE1_ci, ~PE1_p, ~PE2_est, ~PE2_ci, ~PE2_p,

  "(Intercept)", 0.457, "[0.422, 0.491]", "<.001***",
                 0.460, "[0.425, 0.495]", "<.001***",
                 0.472, "[0.438, 0.506]", "<.001***",

  "PE / EVPE", 0.004, "[0.003, 0.005]", "<.001***",
               -0.001, "[-0.002, 0.000]", ".112",
               0.001, "[0.000, 0.002]", ".047*",

  "exam_senti", -0.127, "[-0.157, -0.096]", "<.001***",
                0.081, "[0.052, 0.110]", "<.001***",
                0.002, "[-0.026, 0.030]", ".902",

  "Interaction", 0.010, "[0.009, 0.012]", "<.001***",
                 0.010, "[0.008, 0.012]", "<.001***",
                 0.013, "[0.011, 0.015]", "<.001***"
)

gt_exp <- df_exp %>%
  gt(rowname_col = "Predictor") %>%
  tab_spanner("EVPE model", columns = c(EVPE_est, EVPE_ci, EVPE_p)) %>%
  tab_spanner("PE1 model", columns = c(PE1_est, PE1_ci, PE1_p)) %>%
  tab_spanner("PE2 model", columns = c(PE2_est, PE2_ci, PE2_p)) %>%
  cols_label(
    EVPE_est = "Estimate",
    EVPE_ci  = "95% CI",
    EVPE_p   = md("*p*"),
    PE1_est  = "Estimate",
    PE1_ci   = "95% CI",
    PE1_p    = md("*p*"),
    PE2_est  = "Estimate",
    PE2_ci   = "95% CI",
    PE2_p    = md("*p*")
  ) %>%
  fmt_number(columns = c(EVPE_est, PE1_est, PE2_est), decimals = 3) %>%
  cols_align("center", everything()) %>%
  tab_options(
    table.font.names = c("Times New Roman", "Times", "serif"),
    table.border.top.width = px(1.5),
    table.border.bottom.width = px(1.5)
  ) %>%
  tab_header(
    title = "Table VI. Effects of Prediction Error and Exam Sentiment on Expression Proportion"
  ) %>%
  tab_source_note(
    source_note = md("*Note.* *p* < .05 *, *p* < .01 **, *p* < .001 ***")
  )

gtsave(
  gt_exp,
  "expression_proportion_new.pdf",
  vwidth = 1500,
  vheight = 650,
  zoom = 2
)
```
```{r}
gt_exp
```

```{r}
library(tibble)
library(gt)
library(webshot2)

df_reg <- tribble(
  ~Predictor, ~EVPE_est, ~EVPE_ci, ~EVPE_p, ~PE1_est, ~PE1_ci, ~PE1_p, ~PE2_est, ~PE2_ci, ~PE2_p,

  "(Intercept)", 0.324, "[0.286, 0.362]", "<.001***",
                 0.311, "[0.276, 0.346]", "<.001***",
                 0.308, "[0.272, 0.344]", "<.001***",

  "PE / EVPE", -0.004, "[-0.005, -0.003]", "<.001***",
               0.001, "[-0.000, 0.002]", ".097",
               -0.001, "[-0.002, -0.000]", ".023*",

  "exam_senti", 0.144, "[0.116, 0.172]", "<.001***",
                -0.071, "[-0.099, -0.043]", "<.001***",
                0.015, "[-0.011, 0.041]", ".259",

  "Interaction", -0.011, "[-0.012, -0.010]", "<.001***",
                 -0.011, "[-0.013, -0.009]", "<.001***",
                 -0.013, "[-0.015, -0.012]", "<.001***"
)

gt_reg <- df_reg %>%
  gt(rowname_col = "Predictor") %>%
  tab_spanner(label = "EVPE model", columns = c(EVPE_est, EVPE_ci, EVPE_p)) %>%
  tab_spanner(label = "PE1 model", columns = c(PE1_est, PE1_ci, PE1_p)) %>%
  tab_spanner(label = "PE2 model", columns = c(PE2_est, PE2_ci, PE2_p)) %>%
  cols_label(
    EVPE_est = "Estimate",
    EVPE_ci  = "95% CI",
    EVPE_p   = md("*p*"),
    PE1_est  = "Estimate",
    PE1_ci   = "95% CI",
    PE1_p    = md("*p*"),
    PE2_est  = "Estimate",
    PE2_ci   = "95% CI",
    PE2_p    = md("*p*")
  ) %>%
  fmt_number(columns = c(EVPE_est, PE1_est, PE2_est), decimals = 3) %>%
  cols_align(align = "center", columns = everything()) %>%
  tab_options(
    table.font.names = c("Times New Roman", "Times", "serif"),
    table.border.top.width = px(1.5),
    table.border.bottom.width = px(1.5)
  ) %>%
  tab_header(
    title = "Table V. Effects of Prediction Error and Exam Sentiment on Regulation Proportion"
  ) %>%
  tab_source_note(
    source_note = md("*Note.* *p* < .05 *, *p* < .01 **, *p* < .001 ***")
  )

gtsave(
  gt_reg,
  "regulation_proportion_new.pdf",
  vwidth = 1500,
  vheight = 650,
  zoom = 2
)
```
```{r}
gt_reg
```


```{r}
library(gt)

gt_table <- df %>%
  gt(rowname_col = "Predictor") %>%

  # Column groups
  tab_spanner("EVPE model", columns = c(EVPE_est, EVPE_ci, EVPE_p)) %>%
  tab_spanner("PE1 model", columns = c(PE1_est, PE1_ci, PE1_p)) %>%
  tab_spanner("PE2 model", columns = c(PE2_est, PE2_ci, PE2_p)) %>%

  # Column labels
  cols_label(
    EVPE_est = "Estimate", EVPE_ci = "CI", EVPE_p = "p",
    PE1_est = "Estimate", PE1_ci = "CI", PE1_p = "p",
    PE2_est = "Estimate", PE2_ci = "CI", PE2_p = "p"
  ) %>%

  # Format numbers
  fmt_number(columns = c(EVPE_est, PE1_est, PE2_est), decimals = 3) %>%

  cols_align("center", everything()) %>%

  # 👇 KEY: Times New Roman
  tab_options(
    table.font.names = c("Times New Roman", "Times", "serif"),
    table.border.top.width = px(2),
    table.border.bottom.width = px(2)
  ) %>%

  tab_header(
    title = "Effects of Prediction Error and Exam Sentiment on Language Use"
  )
```
```{r}
library(gt)
library(webshot2)

gt_table <- df %>%
  gt(rowname_col = "Predictor") %>%
  tab_spanner("EVPE model", columns = c(EVPE_est, EVPE_ci, EVPE_p)) %>%
  tab_spanner("PE1 model", columns = c(PE1_est, PE1_ci, PE1_p)) %>%
  tab_spanner("PE2 model", columns = c(PE2_est, PE2_ci, PE2_p)) %>%
  cols_label(
    EVPE_est = "Estimate", EVPE_ci = "CI", EVPE_p = "p",
    PE1_est = "Estimate", PE1_ci = "CI", PE1_p = "p",
    PE2_est = "Estimate", PE2_ci = "CI", PE2_p = "p"
  ) %>%
  fmt_number(columns = c(EVPE_est, PE1_est, PE2_est), decimals = 3) %>%
  cols_align("center", everything()) %>%
  tab_options(
    table.font.names = c("Times New Roman", "Times", "serif")
  )

gtsave(gt_table, "lmer_results_new.pdf", zoom = 2)
gt_table
```

```{r}
tab_model(EVPE_exp_word_senti_model_int, PE_1_exp_ratio_senti_inx,PE2_exp_word_senti_model_inx, dv.labels = "Expression proportion")
```
```{r}
anova(reg_senti_model, EVPE_reg_word_model,EVPE_reg_word_model_senti,EVPE_reg_word_model_senti_int)
AIC(reg_senti_model,EVPE_reg_word_model,EVPE_reg_word_model_senti,EVPE_reg_word_model_senti_int)
BIC(reg_senti_model,EVPE_reg_word_model,EVPE_reg_word_model_senti,EVPE_reg_word_model_senti_int)
```
```{r}
library(tibble)
library(dplyr)

evpe_model_table <- tribble(
  ~Outcome,            ~Model,                      ~AIC,     ~BIC,      ~logLik, ~Chisq,    ~Df, ~p,
  "Expression proportion",  "EVPE",                      -1123.6,  -1095.8,   566.81,  NA,        NA,  NA,
  "Expression proportion",  "EVPE + exam_senti",         -1126.8,  -1093.3,   569.38,  5.1423,    1,   0.02335,
  "Expression proportion",  "EVPE * exam_senti",         -1321.5,  -1282.5,   667.76,  196.7552,  1,   NA,

  "Regulation proportion",  "EVPE",                      -1369.4,  -1341.6,   689.71,  NA,        NA,  NA,
  "Regulation proportion",  "EVPE + exam_senti",         -1378.3,  -1344.9,   695.15,  10.8640,   1,   0.0009807,
  "Regulation proportion",  "EVPE * exam_senti",         -1634.2,  -1595.2,   824.08,  257.8680,  1,   NA
) %>%
  group_by(Outcome) %>%
  mutate(Delta_AIC = AIC - min(AIC)) %>%
  ungroup() %>%
  mutate(
    p_label = case_when(
      is.na(p) & Model %in% c("EVPE") ~ "—",
      Model == "EVPE * exam_senti" ~ "< .001",
      p < .001 ~ "< .001",
      TRUE ~ sprintf("%.3f", p)
    ),
    Chisq_label = ifelse(is.na(Chisq), "—", sprintf("%.2f", Chisq)),
    Df_label = ifelse(is.na(Df), "—", as.character(Df))
  )
```
```{r}
library(gt)

evpe_gt_tbl <- evpe_model_table %>%
  select(Outcome, Model, AIC, BIC, logLik, Delta_AIC, Chisq_label, Df_label, p_label) %>%
  gt(groupname_col = "Outcome") %>%
  tab_header(
    title = md("**Table IV**"),
    subtitle = md("Model Comparison of Mixed-Effects Models for EVPE")
  ) %>%
  cols_label(
    Model = "Model predictors",
    AIC = "AIC",
    BIC = "BIC",
    logLik = "logLik",
    Delta_AIC = md("&Delta;AIC (model − final model)"),
    Chisq_label = md("&chi;<sup>2</sup>"),
    Df_label = "Df",
    p_label = md("*p*")
  ) %>%
  fmt_number(
    columns = c(AIC, BIC, logLik, Delta_AIC),
    decimals = 2
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(rows = Delta_AIC == 0)
  ) %>%
  tab_options(
    table.font.size = px(16),
    heading.title.font.size = px(22),
    heading.subtitle.font.size = px(18),
    row_group.font.weight = "bold",
    table.border.top.width = px(2),
    table.border.bottom.width = px(2),
    column_labels.border.bottom.width = px(1.5),
    data_row.padding = px(6),
    table.font.names = "Times New Roman"
  ) %>%
  tab_source_note(
    source_note = md("*Note.* Lower AIC and BIC values indicate better model fit. Bolded rows indicate the best-fitting model within each outcome.")
  )

evpe_gt_tbl
gtsave(evpe_gt_tbl, "EVPE_model_comparison_table_new.pdf")
```

```{r}
library(ggeffects)
library(ggplot2)
```

```{r}
EVPE_reg_word_plot <- ggpredict(EVPE_reg_word_model, terms = "EVPE")
EVPE_reg_word_plot_df <- as.data.frame(EVPE_reg_word_plot)
```
```{r}
ggplot(EVPE_reg_word_plot_df, aes(x = x, y = predicted)) +
  geom_line(color = "skyblue2",linewidth = 1.2) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), fill = "skyblue2", alpha = 0.2) +
  labs(
    title = "Effect of EVPE on regulation ratio within each exam",
    x = "EVPE",
    y = "Regulation Word Ratio"
  ) +
  theme_classic()
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/EVPE_reg_word_ratio.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/EVPE_reg_word_ratio.pdf",height=4, width=6, dpi=300)
```
```{r}
pred_df <- df_by_exam_pe_senti %>%
  mutate(pred = predict(EVPE_reg_word_model, re.form = NULL))
```
```{r}
ggplot() +
  geom_point(
    data = df_by_exam_pe_senti,
    aes(x = EVPE, y = reg_word_ratio),
    alpha = 0.35,
    color = "lightskyblue1",
    size = 2
  ) +
  geom_line(
    data = EVPE_reg_word_plot_df,
    aes(x = x, y = predicted),
    color = "skyblue3",
    linewidth = 1.2
  ) +
  geom_ribbon(
    data = EVPE_reg_word_plot_df,
    aes(x = x, ymin = conf.low, ymax = conf.high),
    fill = "skyblue3",
    alpha = 0.2
  ) +
  coord_cartesian(xlim = c(-40, 40)) +
  labs(
    title = "Effect of PE on Regulation proportion",
    x = "PE",
    y = "Regulation proportion"
  ) +
  theme_classic()
# ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Final_EVPE_reg_word_ratio.png",height=4, width=6, dpi=300)
# ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/Final_EVPE_reg_word_ratio.pdf",height=4, width=6, dpi=300)
# ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/reg_prop_EVPE.png",height=4, width=6, dpi=300)
# ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/reg_prop_EVPE.pdf",height=4, width=6, dpi=300)
# ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/reg_prop_EVPE.eps",height=4, width=6, dpi=300)
```

```{r}
EVPE_senti_model <- lmer(exam_senti ~ EVPE + (1 | ID)+(1|exam_num), data = df_by_exam_pe_senti)

summary(EVPE_senti_model)
```
```{r}
plot_model(model, type = "pred", terms = "Days")
```

```{r}
EVPE_reg_word_senti_int_model <- lmer(reg_word_ratio ~ EVPE + exam_senti+EVPE*exam_senti + (1 | ID) +(1|exam_num), data = df_by_exam_pe_senti)

summary(EVPE_reg_word_senti_int_model)
```
```{r}
pp_check(EVPE_reg_word_senti_int_model)
```
```{r}
plot_model(EVPE_reg_word_senti_int_model, type = "int")
```
```{r}
EVPE_senti_reg_word_int_plot <- ggpredict(EVPE_reg_word_senti_int_model, terms = c("EVPE", "exam_senti [-0.9, 0.9]"))
EVPE_senti_reg_word_int_plot_df <- as.data.frame(EVPE_senti_reg_word_int_plot)
```
```{r}
ggplot(EVPE_senti_reg_word_int_plot_df, aes(x = x, y = predicted, color = group, fill = group)) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, color = NA) +
  labs(
    title = "Interaction effect of EVPE and exam sentiment on regulation ratio",
    x = "Prediction error",
    y = "Regulation proportion",
    color = "Exam sentiment",
    fill = "Exam sentiment"
  ) +
  scale_color_manual(
    values = c("-0.9" = "#00BFC4", "0.9" = "#F8766D"),
    labels = c("-0.9" = "Negative",
               "0.9"  = "Positive")
  ) +
  scale_fill_manual(
    values = c("-0.9" = "#00BFC4", "0.9" = "#F8766D"),
    labels = c("-0.9" = "Negative",
               "0.9"  = "Positive")
  ) +
  theme_classic()
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/EVPE_senti_reg_word_ratio_int.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/EVPE_senti_reg_word_ratio_int.pdf",height=4, width=6, dpi=300)
```
```{r}
ggplot(EVPE_senti_reg_word_int_plot_df, aes(x = x, y = predicted, color = group, fill = group)) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, color = NA) +
  labs(
    title = "Interaction effect of EVPE and exam sentiment on regulation ratio",
    x = "Prediction error",
    y = "Regulation proportion",
    color = "Exam sentiment",
    fill = "Exam sentiment"
  ) +
  coord_cartesian(xlim = c(-40, 40)) +
  scale_color_manual(
    values = c("-0.9" = "#F8766D", "0.9" = "#00BFC4"),
    labels = c("-0.9" = "Negative",
               "0.9"  = "Positive")
  ) +
  scale_fill_manual(
    values = c("-0.9" = "#F8766D", "0.9" = "#00BFC4"),
    labels = c("-0.9" = "Negative",
               "0.9"  = "Positive")
  ) +
  theme_classic()
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/flip_EVPE_senti_reg_word_ratio_int.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/flip_EVPE_senti_reg_word_ratio_int.pdf",height=4, width=6, dpi=300)
```


```{r}
m <- EVPE_reg_word_senti_int_model

fixef(m)
```
```{r}
b0 <- fixef(m)[1]
b1 <- fixef(m)["EVPE"]
b2 <- fixef(m)["exam_senti"]
b3 <- fixef(m)["EVPE:exam_senti"]
```
```{r}
s1 <- -0.9
s2 <- 0.9

intercept1 <- b0 + b2*s1
slope1 <- b1 + b3*s1

intercept2 <- b0 + b2*s2
slope2 <- b1 + b3*s2
```
```{r}
# 1. Exact Coordinates
x_cross <- (intercept2 - intercept1) / (slope1 - slope2)
y_cross <- slope1 * x_cross + intercept1

# 2. Add the bridge point to the data frame
plot_df_final <- plot_df %>%
  bind_rows(
    # We add the point for both groups to ensure no gaps in any path
    expand.grid(group = unique(plot_df$group), x = x_cross) %>%
      mutate(predicted = y_cross, 
             group_num = as.numeric(as.character(group)),
             conf.low = y_cross, 
             conf.high = y_cross)
  ) %>%
  arrange(group, x) %>%
  mutate(congruency = case_when(
    group_num < 0 & x <= x_cross ~ "Incongruent",
    group_num < 0 & x >= x_cross ~ "Congruent",
    group_num > 0 & x <= x_cross ~ "Congruent",
    group_num > 0 & x >= x_cross ~ "Incongruent"
  ))

# 3. Plot with the "Weld" point
ggplot(plot_df_final, aes(x = x, y = predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, group = group),
              fill = "grey85", alpha = 0.2, color = NA) +
  
  # The "Weld": This point fills the pixel gap where colors swap.
  # 'inherit.aes = FALSE' prevents the "predicted not found" error.
  geom_point(data = data.frame(x = x_cross, y = y_cross),
             aes(x = x, y = y), 
             color = "firebrick3", size = 1.3, 
             inherit.aes = FALSE) + 
  geom_point(data = data.frame(x = x_cross, y = y_cross),
             aes(x = x, y = y), 
             color = "steelblue3", size = 1.3, 
             inherit.aes = FALSE) + 

  # The lines: 'lineend = "round"' is the key to a seamless look
  geom_line(aes(color = congruency, group = interaction(group, congruency)),
            linewidth = 1.2, lineend = "round") +
  
  geom_vline(xintercept = x_cross, linetype = "dashed", color = "grey40") +
  scale_color_manual(values = c("Congruent" = "steelblue3", "Incongruent" = "firebrick3")) +
  theme_classic() +
  labs(title = "Interaction Effect of EVPE and Exam Sentiment",
       x = "EVPE", y = "Regulation proportion", color = "Congruency")
```


```{r}
ggplot(plot_df, aes(x = x, y = predicted)) +
  geom_ribbon(
    aes(ymin = conf.low, ymax = conf.high, group = group),
    fill = "grey85",
    alpha = 0.25,
    color = NA
  ) +
  geom_line(
    aes(color = congruency, group = segment),
    linewidth = 1.2
  ) +
  geom_vline(xintercept = x_cross, linetype = "dashed", color = "grey40") +
  scale_color_manual(values = c(
    "Congruent" = "steelblue3",
    "Incongruent" = "firebrick3"
  )) +
  labs(
    title = "Interaction Effect of EVPE and Exam Sentiment on Regulation Ratio",
    x = "EVPE",
    y = "Regulation proportion",
    color = "Congruency"
  ) +
  theme_classic()
```

```{r}
library(dplyr)
library(ggplot2)

plot_df <- EVPE_reg_word_senti_plot_df
plot_df$group_num <- as.numeric(as.character(plot_df$group))

b <- fixef(EVPE_reg_word_senti_int_model)

b0 <- b["(Intercept)"]
b1 <- b["EVPE"]
b2 <- b["exam_senti"]
b3 <- b["EVPE:exam_senti"]

s1 <- -0.9
s2 <-  0.9

intercept1 <- b0 + b2 * s1
slope1     <- b1 + b3 * s1

intercept2 <- b0 + b2 * s2
slope2     <- b1 + b3 * s2

x_cross <- (intercept2 - intercept1) / (slope1 - slope2)

# 1. Create crossing points for ALL groups in your data
# We calculate the specific 'predicted' value for each group at the crossing point
crossing_points <- plot_df %>%
  distinct(group, group_num) %>%
  mutate(
    x = x_cross,
    predicted = case_when(
      group_num == s1 ~ slope1 * x_cross + intercept1,
      group_num == s2 ~ slope2 * x_cross + intercept2,
      TRUE ~ b0 + b1*x_cross + b2*group_num + b3*x_cross*group_num
    ),
    # We leave CI as NA or approximate it to keep the ribbon gap-free
    conf.low = predicted, 
    conf.high = predicted
  )

# 2. Merge, Sort, and Re-label
plot_df_final <- bind_rows(plot_df, crossing_points) %>%
  arrange(group, x) %>%
  mutate(congruency = case_when(
    group_num < 0 & x <= x_cross ~ "Congruent",
    group_num > 0 & x >= x_cross ~ "Congruent",
    TRUE ~ "Incongruent"
  )) %>%
  # IMPORTANT: The segment must be unique to the group AND the congruency 
  # to prevent ggplot from trying to connect the two red lines across the middle.
  mutate(segment_id = paste0(group, "_", congruency))

# 3. Plot
ggplot(plot_df_final, aes(x = x, y = predicted)) +
  geom_ribbon(
    aes(ymin = conf.low, ymax = conf.high, group = group),
    fill = "grey85", alpha = 0.25, color = NA
  ) +
  geom_line(
    aes(color = congruency, group = segment_id), # Use the new segment_id
    linewidth = 1.2,
    lineend = "round"
  ) +
  geom_vline(xintercept = x_cross, linetype = "dashed", color = "grey40") +
  scale_color_manual(values = c(
    "Congruent" = "steelblue3",
    "Incongruent" = "firebrick3"
  )) +
  labs(
    title = "Interaction Effect of EVPE and Exam Sentiment on Regulation Ratio",
    x = "EVPE", y = "Regulation proportion", color = "Congruency"
  ) +
  theme_classic()
```


```{r}
glmer_EVPE_senti_reg_word_nb <- glmer.nb(reg_word_ratio ~ EVPE*exam_senti +(1|ID) ,offset = log(exam_total_word), data = df_by_exam_pe_senti)
summary(glmer_EVPE_senti_reg_word_nb)
```
```{r}
pp_check(glmer_EVPE_senti_reg_word_nb)
```

```{r}
PE_2_reg_word_senti_model <- lmer(reg_word_ratio ~ PE_2 + exam_senti+PE_2*exam_senti + (1 | ID) +(1|exam_num), data = df_by_exam_pe_senti)

summary(PE_2_reg_word_senti_model)
```
```{r}
plot_model(PE_2_reg_word_senti_model, type = "int")
```

```{r}
EVPE_val_reg_model <- lmer(reg_ratio ~ EVPE_val + (1 | ID), data = df_by_exam_pe)

summary(EVPE_val_reg_model)
```
```{r}
EVPE_mag_reg_model <- lmer(reg_ratio ~ EVPE_mag + 0+ (1 | ID), data = df_by_exam_pe)

summary(EVPE_mag_reg_model)
```
```{r}
EVPE_val_mag_reg_model <- lmer(reg_ratio ~ EVPE_val + EVPE_mag +EVPE_val*EVPE_mag + 0+ (1 | ID), data = df_by_exam_pe)

summary(EVPE_val_mag_reg_model)
```
```{r}
plot_model(EVPE_val_mag_reg_model)
```
```{r}
pp_check(EVPE_val_mag_reg_model)
```


```{r}
EVPE_val_mag_reg_model_total <- lmer(reg_ratio ~ EVPE_val + EVPE_mag +EVPE_val*EVPE_mag +total+ (1 | ID) + (1|exam_num), data = df_by_exam_pe)

summary(EVPE_val_mag_reg_model_total)
```
```{r}
pp_check(EVPE_val_mag_reg_model_total)
```
```{r}
plot_model(EVPE_val_mag_reg_model_total, type="int")
```

```{r}
describe(df_by_exam_pe$reg_ratio)
```


### EVPE vs. exp_ratio
```{r}
EVPE_exp_word_model <- lmer(exp_word_ratio ~ EVPE + (1 | ID) + (1|exam_num), data = df_by_exam_pe_senti)

summary(EVPE_exp_word_model)
```

```{r}
EVPE_exp_word_senti_model <- lmer(exp_word_ratio ~ EVPE + exam_senti + (1 | ID)+ (1|exam_num), data = df_by_exam_pe_senti)

summary(EVPE_exp_word_senti_model)
```

```{r}
EVPE_exp_word_senti_model_int <- lmer(exp_word_ratio ~ EVPE * exam_senti + (1 | ID) +(1|exam_num), data = df_by_exam_pe_senti)

summary(EVPE_exp_word_senti_model_int)
```

```{r}
EVPE_val_mag_exp_model <- lmer(exp_ratio ~ EVPE_val + EVPE_mag + EVPE_val*EVPE_mag + 0 + (1 | ID), data = df_by_exam_pe)

summary(EVPE_val_mag_exp_model)
```

##exam_level: exp~ GAD
```{r}
GAD_exp_model <- lmer(exp_ratio ~ GAD + (1 | ID), data = df_by_exam_pe)

summary(GAD_exp_model)
```
```{r}
GAD_EVPE_exp_model <- lmer(exp_ratio ~ GAD * EVPE + (1 | ID), data = df_by_exam_pe)

summary(GAD_exp_model)
```
```{r}
df_by_exam_pe_mood <- inner_join(df_by_exam_pe, df_mood, by = "ID")
```
```{r}
GAD_score_exp_model <- lmer(exp_ratio ~ GAD_score * EVPE + (1 | ID) + (1|exam_num), data = df_by_exam_pe_mood)

summary(GAD_score_exp_model)
```

## Response level: exp_ratio ~ GAD
```{r}
GAD_exp_resp_model <- lmer(exp_word_ratio ~ GAD*EVPE  + (1 | ID) + (1|exam_num), data = df_by_resp_word_count_wide_PE)

summary(GAD_exp_resp_model)
```
```{r}
df_by_resp_word_count_wide_PE_mood <- inner_join(df_by_resp_word_count_wide_PE, df_mood, by = c("ID"))
```

```{r}
GAD_score_exp_resp_model <- lmer(exp_word_ratio ~ GAD_score*EVPE  + (1 | ID) + (1|exam_num), data = df_by_resp_word_count_wide_PE_mood)

summary(GAD_score_exp_resp_model)
```


####EVPE exp comparison
```{r}
anova(EVPE_exp_word_model,EVPE_exp_word_senti_model,EVPE_exp_word_senti_model_int)
AIC(EVPE_exp_word_model,EVPE_exp_word_senti_model,EVPE_exp_word_senti_model_int)
BIC(EVPE_exp_word_model,EVPE_exp_word_senti_model,EVPE_exp_word_senti_model_int)
```

### PE+exam_num vs. reg_ratio
```{r}
pe_exam_reg_model <- lmer(reg_ratio ~ PE_1 + exam_num + (1 | ID), data = df_by_exam_pe)

summary(pe_exam_reg_model)
```


# Brm()
### PE_1 vs. regulation_count (poisson)
```{r}
fit1_baye <- brm(Regulation ~ PE_1 + exam_num + (1|ID), data = df_by_exam_pe, family = poisson())

summary(fit1_baye)
```

```{r}
df_tmp <- df_by_exam_pe %>% filter(!is.na(PE_1))
```

### PE_1 + exam_num vs. regulation_count (negbin)
```{r}
fit1_baye_neg <- brm(Regulation ~ PE_1 + exam_num + (1|ID), data = df_by_exam_pe %>% filter(!is.na(PE_1)), family = negbinomial())

summary(fit1_baye_neg)
```
```{r}
plot(fit1_baye_neg)
```

### PE_1 + exam_num vs. regulation_count (zero_inflated)
```{r}
fit1_baye_zib <- brm(reg_ratio ~ PE_1 + exam_num + (1|ID), data = df_by_exam_pe, family = zero_one_inflated_beta())

summary(fit1_baye_zib)
```

### Compare poisson and nb
```{r}
loo(fit1_baye, fit1_baye_neg)
```

## PE_1 vs. expression_count
```{r}
fit2_baye <- brm(Expression ~ PE_1 + exam_num + (1|ID), data = df_by_exam_pe, family = poisson())

summary(fit2_baye)
```

# Temporal model
## Reg onset and PE
```{r}
# Use the reg position within a response as the onset indicate
df_row_idx <- df_no_na %>% group_by(ID, exam_num, ResponseNumber) %>% dplyr::mutate(phrase_idx =row_number()) %>% ungroup()
```
```{r}
# Find the first phrase_idx with regulation
first_reg_position <- df_row_idx %>% group_by(ID, exam_num) %>% summarise(first_reg = min(phrase_idx[label_api_text == "Regulation"], na.rm = TRUE),
total_phrases = n(),
.groups = "drop") %>% mutate(first_reg_norm = first_reg/total_phrases)
```
```{r}
# If no reg, first_reg = inf. Replace inf with NA
first_reg_position <- first_reg_position %>%
  mutate(first_reg = ifelse(is.infinite(first_reg), NA, first_reg),
         first_reg_norm = first_reg / total_phrases)

```

```{r}
# Combine transcription with PE
df_first_reg_PE <- first_reg_position %>%
  left_join(df_PE, by = c("ID","exam_num"))
```

```{r}
fit_reg_pos_PE1 <- lmer(first_reg_norm ~ PE_1 + exam_num + (1 | ID), data = df_first_reg_PE)
summary(fit_reg_pos_PE1)
```
```{r}
fit_reg_pos_PE_nb <- glmer.nb(first_reg_norm ~ PE_1 + exam_num + (1 | ID), data = df_first_reg_PE)
summary(fit_reg_pos_PE_nb)
```

```{r}
pp_check(fit_reg_pos_PE_nb)
```
```{r}
fit_reg_pos_PE2 <- lmer(first_reg_norm ~ PE_2 + exam_num + (1 | ID), data = df_first_reg_PE)
summary(fit_reg_pos_PE2)
```

```{r}
if (require("ggplot2") && require("see")) {
  pp_check(fit1_baye_zib)
}
```
```{r}
pp_check(fit1_baye_neg)
```
```{r}
pp_check(fit_reg_pos_PE)
```

##PE vs. exam word count
```{r}
# The total word count of each label, per exam
df_by_exam_word_count <- df_select %>% group_by(ID, exam_num, label_api_text) %>% summarise(sum_word_count = sum(word_count), .groups = "drop")

# The wide format
df_by_exam_word_count_wide <- df_by_exam_word_count %>% group_by(ID, exam_num) %>% pivot_wider(names_from = label_api_text, values_from = sum_word_count)

df_by_exam_word_count_wide <- df_by_exam_word_count_wide %>% mutate(across(where(is.numeric), ~replace(.,is.na(.), 0)))

df_by_exam_word_count_wide <- df_by_exam_word_count_wide %>% group_by(ID, exam_num) %>%
  mutate(exam_total_word = sum(Expression + Regulation + Neither),
         exp_word_ratio = Expression/exam_total_word,
         reg_word_ratio = Regulation/exam_total_word,
         nei_word_ratio = Neither/exam_total_word)
```
```{r}
df_by_exam_word_count_PE <- inner_join(df_by_exam_word_count, df_PE_correct, by=c("ID", "exam_num"))
df_by_exam_word_count_wide_PE <- inner_join(df_by_exam_word_count_wide, df_PE, by = c("ID", "exam_num"))
```
### PE_1 vs. reg_word_ratio
####lmer
```{r}
# Using word_ratio
m1_PE1_reg_word_ratio <- lmer(reg_word_ratio ~ PE_1 +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m1_PE1_reg_word_ratio)
```
```{r}
pp_check(m1_PE1_reg_word_ratio)
```
```{r}
plot_model(m1_PE1_reg_word_ratio)
```

```{r}
m1_PE1_reg_word <- lmer(Regulation ~ PE_1 + exam_total_word + (1|ID) , data = df_by_exam_word_count_wide_PE)
summary(m1_PE1_reg_word)
```
```{r}
pp_check(m1_PE1_reg_word)
```
####glmer.nb
```{r}
m1_PE1_reg_word_nb <- glmer.nb(Regulation ~ PE_1 + (1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m1_PE1_reg_word_nb)
```
```{r}
pp_check(m1_PE1_reg_word_nb)
```
###PE_1_val vs. reg_word_ratio
####lmer
```{r}
m1_PE1_val_reg_word_ratio <- lmer(reg_word_ratio ~ PE_1_val +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m1_PE1_val_reg_word_ratio)
```
```{r}
emmeans(m1_PE1_val_reg_word_ratio, pairwise~PE_1_val, adjust = "none")
```

```{r}
m1_PE1_val_reg_word <- lmer(Regulation ~ PE_1_val + exam_total_word + 0 + (1|ID), data = df_by_exam_word_count_wide_PE)
summary(m1_PE1_val_reg_word)
```
```{r}
pp_check(m1_PE1_val_reg_word)
```
```{r}
plot_model(m1_PE1_val_reg_word, title = "PE_1_valence vs. Regulation ratio")
```

####glmer.nb
```{r}
m1_PE1_val_reg_word_nb <- glmer.nb(Regulation ~ PE_1_val + 0+ (1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m1_PE1_val_reg_word_nb)
```
```{r}
pp_check(m1_PE1_val_reg_word_nb)
```
####zero-inflated
```{r}
m2_ZINB <- glmmTMB(Regulation ~ PE_1_val + (1|ID),
                  ziformula = ~1,
                  offset = log(exam_total_word),
                  data = df_by_exam_word_count_wide_PE,
                  family = nbinom2)

# To see the model summary
summary(m2_ZINB)
```
```{r}
install.packages("DHARMa")
library(DHARMa)

simulationOutput <- simulateResiduals(m2_ZINB)

# Plot the PPC
plot(simulationOutput)
```

### PE_1_mag vs. reg_word_ratio
####lmer
```{r}
# Using word_ratio
m1_PE1_mag_reg_word_ratio <- lmer(reg_word_ratio ~ PE_1_mag +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m1_PE1_mag_reg_word_ratio)
```
```{r}
pp_check(m1_PE1_mag_reg_word_ratio)
```
```{r}
m1_PE1_mag_reg_word <- lmer(Regulation ~ PE_1_mag + exam_total_word + (1|ID) , data = df_by_exam_word_count_wide_PE)
summary(m1_PE1_mag_reg_word)
```
```{r}
pp_check(m1_PE1_mag_reg_word)
```
####glmer.nb
```{r}
m1_PE1_mag_reg_word_nb <- glmer.nb(Regulation ~ PE_1_mag +(1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m1_PE1_mag_reg_word_nb)
```
```{r}
pp_check(m1_PE1_mag_reg_word_nb)
```

###PE_1_val * PE_1_mag
####lmer
```{r}
m1_PE1_val_mag_reg_word <- lmer(Regulation ~ PE_1_val + PE_1_mag +PE_1_val*PE_1_mag + 0 + exam_total_word + (1|ID) , data = df_by_exam_word_count_wide_PE)
summary(m1_PE1_val_mag_reg_word)
```
```{r}
pp_check(m1_PE1_val_mag_reg_word)
```
####glmer.nb
```{r}
m1_PE1_val_mag_reg_word_nb <- glmer.nb(Regulation ~ PE_1_val + PE_1_mag +PE_1_val*PE_1_mag + exam_total_word + 0 + (1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m1_PE1_val_mag_reg_word_nb)
```
```{r}
pp_check(m1_PE1_val_mag_reg_word_nb)
```
### PE_1 vs. exp_word_ratio
####lmer
```{r}
# Using word_ratio
m2_PE1_exp_word_ratio <- lmer(exp_word_ratio ~ PE_1 +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m2_PE1_exp_word_ratio)
```

```{r}
pp_check(m2_PE1_exp_word_ratio)
```

```{r}
m2_PE1_exp_word <- lmer(Expression ~ PE_1 + exam_total_word + (1|ID) , data = df_by_exam_word_count_wide_PE)
summary(m2_PE1_exp_word)
```

```{r}
pp_check(m2_PE1_exp_word)
```
####glmer.nb
```{r}
m2_PE1_exp_word_nb <- glmer.nb(Expression ~ PE_1 +(1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m2_PE1_exp_word_nb)
```

```{r}
pp_check(m2_PE1_exp_word_nb)
```

### PE_1_val vs. exp_word_ratio
```{r}
m2_PE1_val_exp_word_ratio <- lmer(exp_word_ratio ~ PE_1_val +0 +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m2_PE1_val_exp_word_ratio)
```
```{r}
emmeans(m2_PE1_val_exp_word_ratio, pairwise~PE_1_val, adjust = "none")
```

```{r}
m2_PE1_val_exp_word <- lmer(Expression ~ PE_1_val + exam_total_word + 0 + (1|ID), data = df_by_exam_word_count_wide_PE)
summary(m2_PE1_val_exp_word)
```
```{r}
pp_check(m2_PE1_val_exp_word)
```
```{r}
m2_PE1_val_exp_word_nb <- glmer.nb(Expression ~ PE_1_val + 0+ (1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m2_PE1_val_exp_word_nb)
```
```{r}
pp_check(m2_PE1_val_exp_word_nb)
```
####zero-inflated
```{r}
m2_ZINB <- glmmTMB(Expression ~ PE_1_val + (1|ID),
                  ziformula = ~1,
                  offset = log(exam_total_word),
                  data = df_by_exam_word_count_wide_PE,
                  family = nbinom2)

# To see the model summary
summary(m2_ZINB)
```
```{r}
# install.packages("DHARMa")
# library(DHARMa)

simulationOutput <- simulateResiduals(m2_ZINB)

# Plot the PPC
plot(simulationOutput)
```
### PE_1_mag
```{r}
m2_PE1_mag_exp_word_ratio <- lmer(exp_word_ratio ~ PE_1_mag +  + 0 + (1|ID), data = df_by_exam_word_count_wide_PE)
summary(m2_PE1_mag_exp_word_ratio)
```

```{r}
m2_PE1_mag_exp_word <- lmer(Expression ~ PE_1_mag + exam_total_word + 0 + (1|ID), data = df_by_exam_word_count_wide_PE)
summary(m2_PE1_mag_exp_word)
```
```{r}
m2_PE1_mag_exp_word_nb <- glmer.nb(Expression ~ PE_1_mag +(1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m2_PE1_mag_exp_word_nb)
```


### PE_1_val * PE_1_mag
```{r}
m2_PE1_val_mag_exp <- lmer(exp_word_ratio ~ PE_1_val*PE_1_mag  + 0 + (1|ID), data = df_by_exam_word_count_wide_PE)
summary(m2_PE1_val_mag_exp)
```

```{r}
m2_PE1_val_mag_exp_word <- lmer(Expression ~ PE_1_val*PE_1_mag + exam_total_word + 0 + (1|ID), data = df_by_exam_word_count_wide_PE)
summary(m2_PE1_val_mag_exp_word)
```
```{r}
m2_PE_1_val_mag_exp_word_nb <- glmer.nb(Expression ~ PE_1_val * PE_1_mag + 0 +(1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m2_PE_1_val_mag_exp_word_nb)
```
### PE_2 vs. reg_word_ratio
####lmer
```{r}
# Using word_ratio
m3_PE2_reg_word_ratio <- lmer(reg_word_ratio ~ PE_2 +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_reg_word_ratio)

```

```{r}
pp_check(m3_PE2_reg_word_ratio)
```

```{r}
m3_PE2_reg_word <- lmer(Regulation ~ PE_2 + exam_total_word + (1|ID) , data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_reg_word)

```

```{r}
pp_check(m3_PE2_reg_word)
```
####glmer.nb
```{r}
m3_PE2_reg_word_nb <- glmer.nb(Regulation ~ PE_2 +(1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_reg_word_nb)
```
```{r}
pp_check(m3_PE2_reg_word_nb)
```
### PE_2_val vs. reg_word_ratio
####lmer
```{r}
m3_PE2_val_reg_word_ratio <- lmer(reg_word_ratio ~ PE_2_val +0 +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_val_reg_word_ratio)
```
```{r}
emmeans(m3_PE2_val_reg_word_ratio, pairwise~PE_2_val, adjust = "none")
```

```{r}
df_by_exam_word_count_wide_PE$PE_2_val <- relevel(df_by_exam_word_count_wide_PE$PE_2_val, ref = "negative")
```

```{r}
m3_PE2_val_reg_word <- lmer(Regulation ~ PE_2_val + exam_total_word + 0 + (1|ID), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_val_reg_word)
```
```{r}
pp_check(m3_PE2_val_reg_word)
```
```{r}
plot_model(m3_PE2_val_reg_word, title = "PE_2_valence vs. Regulation ratio")
```
####glmer.nb
```{r}
m3_PE2_val_reg_word_nb <- glmer.nb(Regulation ~ PE_2_val + 0+ (1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_val_reg_word_nb)
```
```{r}
pp_check(m3_PE2_val_reg_word_nb)
```
####zero-inflated
```{r}
m3_ZINB <- glmmTMB(Regulation ~ PE_2_val + (1|ID),
                  ziformula = ~1,
                  offset = log(exam_total_word),
                  data = df_by_exam_word_count_wide_PE,
                  family = nbinom3)

# To see the model summary
summary(m3_ZINB)
```
```{r}
install.packages("DHARMa")
library(DHARMa)

simulationOutput <- simulateResiduals(m3_ZINB)

# Plot the PPC
plot(simulationOutput)
```
###PE_2_mag vs. reg_word_ratio
####lmer
```{r}
m3_PE2_mag_reg_word_ratio <- lmer(reg_word_ratio ~ PE_2_mag +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_mag_reg_word_ratio)
```
```{r}
pp_check(m3_PE2_mag_reg_word_ratio)
```

```{r}
m3_PE2_mag_reg_word <- lmer(Regulation ~ PE_2_mag + exam_total_word  + (1|ID), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_mag_reg_word)
```
```{r}
pp_check(m3_PE2_mag_reg_word)
```
####glmer.nb
```{r}
m3_PE2_mag_reg_word_nb <- glmer.nb(Regulation ~ PE_2_mag + (1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_mag_reg_word_nb)
```
```{r}
pp_check(m3_PE2_mag_reg_word_nb)
```
####zero-inflated
```{r}
m3_ZINB <- glmmTMB(Regulation ~ PE_2_mag + (1|ID),
                  ziformula = ~1,
                  offset = log(exam_total_word),
                  data = df_by_exam_word_count_wide_PE,
                  family = nbinom3)

# To see the model summary
summary(m3_ZINB)
```
```{r}
install.packages("DHARMa")
library(DHARMa)

simulationOutput <- simulateResiduals(m3_ZINB)

# Plot the PPC
plot(simulationOutput)
```

###PE_2_val*PE_2_mag
####lmer
```{r}
m3_PE2_val_mag_reg_word_ratio <- lmer(reg_word_ratio ~ PE_2_val + PE_2_mag + PE_2_val*PE_2_mag +0 +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_val_reg_word_ratio)
```
```{r}
m3_PE2_val_reg_word <- lmer(Regulation ~ PE_2_val*PE_2_mag + exam_total_word + 0 + (1|ID), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_val_reg_word)
```
```{r}
pp_check(m3_PE2_val_reg_word)
```
```{r}
plot_model(m3_PE2_val_reg_word, type = "int")
```

m1<-brms(Regulation ~ t2(PE_2_mag, by = PE_2_val)...)
conditional_effects(m1)

####glmer.nb
```{r}
m3_PE2_val_mag_reg_word_nb <- glmer.nb(Regulation ~ PE_2_val + PE_2_mag + PE_2_val*PE_2_mag + 0+ (1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_val_mag_reg_word_nb)
```
```{r}
pp_check(m3_PE2_val_mag_reg_word_nb)
```
### PE_2 vs. exp_word
####lmer
```{r}
# Using word_ratio
m3_PE2_exp_word_ratio <- lmer(exp_word_ratio ~ PE_2 +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_exp_word_ratio)
```
```{r}
pp_check(m3_PE2_exp_word_ratio)
```
```{r}
m3_PE2_exp_word <- lmer(Expression ~ PE_2 + exam_total_word + (1|ID) , data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_exp_word)
```
```{r}
pp_check(m3_PE2_exp_word)
```
#### glmer.nb
```{r}
m3_PE2_exp_word_nb <- glmer.nb(Expression ~ PE_2 +(1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_exp_word_nb)
```
```{r}
pp_check(m3_PE2_exp_word_nb)
```
### PE_2_val vs. exp_word
```{r}
m3_PE2_val_exp_word_ratio <- lmer(exp_word_ratio ~ PE_2_val +0 +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_val_exp_word_ratio)
```
```{r}
emmeans(m3_PE2_val_exp_word_ratio, pairwise~PE_2_val, adjust = "none")
```

```{r}
m3_PE2_val_exp_word <- lmer(Expression ~ PE_2_val + exam_total_word + 0 + (1|ID), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_val_exp_word)
```
```{r}
pp_check(m3_PE2_val_exp_word)
```
```{r}
m3_PE2_val_exp_word_nb <- glmer.nb(Expression ~ PE_2_val + 0+ (1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_val_exp_word_nb)
```
```{r}
pp_check(m3_PE2_val_exp_word_nb)
```
####zero-inflated
```{r}
m3_ZINB <- glmmTMB(Expression ~ PE_2_val + (1|ID),
                  ziformula = ~1,
                  offset = log(exam_total_word),
                  data = df_by_exam_word_count_wide_PE,
                  family = nbinom3)

# To see the model summary
summary(m3_ZINB)
```
```{r}
install.packages("DHARMa")
library(DHARMa)

simulationOutput <- simulateResiduals(m3_ZINB)

# Plot the PPC
plot(simulationOutput)
```
### PE_2_mag vs. exp_word_ratio
####lmer
```{r}
m3_PE2_mag_exp_word_ratio <- lmer(exp_word_ratio ~ PE_2_mag +0 +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_mag_exp_word_ratio)
```
```{r}
m3_PE2_mag_exp_word <- lmer(Expression ~ PE_2_mag + exam_total_word + 0 + (1|ID), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_mag_exp_word)
```
```{r}
pp_check(m3_PE2_mag_exp_word)
```
###glmer.nb
```{r}
m3_PE2_mag_exp_word_nb <- glmer.nb(Expression ~ PE_2_mag + 0 + (1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_mag_exp_word_nb)
```
```{r}
pp_check(m3_PE2_mag_exp_word_nb)
```
####zero-inflated
```{r}
m3_ZINB <- glmmTMB(Expression ~ PE_2_mag + (1|ID),
                  ziformula = ~1,
                  offset = log(exam_total_word),
                  data = df_by_exam_word_count_wide_PE,
                  family = nbinom3)

# To see the model summary
summary(m3_ZINB)
```
```{r}
install.packages("DHARMa")
library(DHARMa)

simulationOutput <- simulateResiduals(m3_ZINB)

# Plot the PPC
plot(simulationOutput)
```
### PE_2_val * PE_2_mag
```{r}
df_by_exam_word_count_wide_PE$PE_2_val <- as.factor(df_by_exam_word_count_wide_PE$PE_2_val)
df_by_exam_word_count_wide_PE$PE_2_val <- relevel(df_by_exam_word_count_wide_PE$PE_2_val, ref = "positive")
```

```{r}
m3_PE2_val_mag_exp<- lmer(exp_word_ratio ~ PE_2_val * PE_2_mag + 0+ (1|ID) , data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_val_mag_exp)
```
```{r}
m3_PE2_val_mag_exp_word <- lmer(Expression ~ PE_2_val * PE_2_mag + exam_total_word+ 0+ (1|ID) , data = df_by_exam_word_count_wide_PE)
summary(m3_PE2_val_mag_exp_word)
```
```{r}
pp_check(m3_PE2_val_mag_exp_word)
```
```{r}
m3_PE_2_val_mag_exp_word_nb <- glmer.nb(Expression ~ PE_2_val * PE_2_mag +(1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m3_PE_2_val_mag_exp_word_nb)
```

###EVPE vs. reg_word_ratio
####lmer
```{r}
# Using word_ratio
m4_EVPE_reg_word_ratio <- lmer(reg_word_ratio ~ EVPE +(1|ID) + (1|exam_num), data = df_by_exam_word_count_wide_PE)
summary(m4_EVPE_reg_word_ratio)
```
```{r}
pp_check(m4_EVPE_reg_word_ratio)
```
### I add df_mood here
#### Exam
```{r}
df_senti_full <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/emaData_F24_phrase_sentiment_v5.csv")
# It wierd that there is a cate as "-0.5", I think it is mixed too.
df_senti_full <- df_senti_full %>% mutate(api_val_text = (case_when(api_val == 1.0 ~"POSITIVE",
                                                               api_val == 0.5 ~ "MIXED",
                                                               api_val == -0.5 ~ "MIXED",
                                                               api_val == 0 ~ "NEUTRAL",
                                                               api_val == -1 ~ "NEGATIVE")
  
))
```
```{r}
df_senti_full <- df_senti_full %>% mutate(api_senti_score = api_val * api_intensity)

df_senti_exam_tmp <- df_senti_full %>% dplyr::group_by(ID, exam_num) %>% dplyr::mutate(senti_exam = mean(api_senti_score))
df_senti_exam <- df_senti_exam_tmp %>% select("ID", "exam_num", "senti_exam")
df_senti_exam_unique <- unique(df_senti_exam)
```



```{r}
df_mood <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/survey_data_f24/processed/premedEMA_exit_mood_final.csv")
```

```{r}
df_by_exam_word_count_wide_PE_senti <- inner_join(df_by_exam_word_count_wide_PE,df_senti_exam_unique, by = c("ID", "exam_num") )

df_by_exam_word_count_wide_PE_senti_gad <- inner_join(df_by_exam_word_count_wide_PE_senti, df_mood, by = "ID")
```

Exam-wise
```{r}
m_senti_EVPE_gad <- lmer(senti_exam ~ GAD*EVPE+ (1|ID) + (1|exam_num), data = df_by_exam_word_count_wide_PE_senti)
summary(m_senti_EVPE_gad)
```
```{r}
m_senti_EVPE_gad_score <- lmer(senti_exam ~ GAD_score*EVPE+ (1|ID) + (1|exam_num), data = df_by_exam_word_count_wide_PE_senti_gad)
summary(m_senti_EVPE_gad_score)
```

```{r}
m_senti_gad_score <- lmer(senti_exam ~ GAD_score + (1|ID) + (1|exam_num), data = df_by_exam_word_count_wide_PE_senti_gad)
summary(m_senti_gad_score)
```
```{r}
anova(m_senti_gad_score, m_senti_EVPE_gad_score)
```


```{r}
m_senti_gad<- lmer(senti_exam ~ GAD + (1|ID) + (1|exam_num), data = df_by_exam_word_count_wide_PE_senti)
summary(m_senti_gad)
```

```{r}
m_senti_EVPE_gad <- lmer(senti_exam ~ EVPE+GAD_score + (1|ID) + (1|exam_num), data = df_by_exam_word_count_wide_PE_senti_gad)
summary(m_senti_EVPE_gad)
```

```{r}
m_senti_EVPE_reg_ratio_gad <- lmer(senti_exam ~ EVPE+reg_word_ratio+GAD_score + (1|ID) + (1|exam_num), data = df_by_exam_word_count_wide_PE_senti_gad)
summary(m_senti_EVPE_reg_ratio_gad)
```
```{r}
pp_check(m_senti_EVPE_reg_ratio_gad)
```

####response
```{r}
# The total word count of each label, per exam
df_by_resp_word_count <- df_select %>% dplyr::group_by(ID, exam_num,ResponseNumber, label_api_text) %>% summarise(sum_word_count = sum(word_count), .groups = "drop")

# The wide format
df_by_resp_word_count_wide <- df_by_resp_word_count %>% group_by(ID, exam_num, ResponseNumber) %>% pivot_wider(names_from = label_api_text, values_from = sum_word_count)

df_by_resp_word_count_wide <- df_by_resp_word_count_wide %>% mutate(across(where(is.numeric), ~replace(.,is.na(.), 0)))

df_by_resp_word_count_wide <- df_by_resp_word_count_wide %>% dplyr::group_by(ID, exam_num, ResponseNumber) %>%
  mutate(exam_total_word = sum(Expression + Regulation + Neither),
         exp_word_ratio = Expression/exam_total_word,
         reg_word_ratio = Regulation/exam_total_word,
         nei_word_ratio = Neither/exam_total_word)
```

```{r}
df_by_resp_word_count_PE <- inner_join(df_by_resp_word_count, df_PE_correct, by=c("ID", "exam_num"))
df_by_resp_word_count_wide_PE <- inner_join(df_by_resp_word_count_wide, df_PE, by = c("ID", "exam_num"))
```

```{r}
df_senti_response_tmp <- df_senti_full %>% dplyr::group_by(ID, exam_num, ResponseNumber) %>% dplyr::mutate(avg_senti_resp = mean(api_senti_score))

df_senti_response_tmp <- df_senti_response_tmp %>% select(ID, exam_num, ResponseNumber, avg_senti_resp)

df_senti_response <- unique(df_senti_response_tmp)
```

```{r}
df_mood <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/survey_data_f24/processed/premedEMA_exit_mood_final.csv")
```

```{r}
df_by_resp_word_count_wide_PE_senti <- inner_join(df_by_resp_word_count_wide_PE,df_senti_response, by = c("ID", "exam_num", "ResponseNumber") )

df_by_resp_word_count_wide_PE_senti_gad <- inner_join(df_by_resp_word_count_wide_PE_senti, df_mood, by = "ID")
```
```{r}
df_by_resp_word_count_wide_PE_senti_gad <- df_by_resp_word_count_wide_PE_senti_gad %>% dplyr::group_by(ID, exam_num, ResponseNumber) %>% dplyr::mutate(delta_resp_senti = lead(avg_senti_resp) - avg_senti_resp)
```
```{r}
m_resp_senti_GAD <- lmer(avg_senti_resp ~ GAD + (1|exam_num) + (1|ID) + (1|ResponseNumber), data = df_by_resp_word_count_wide_PE_senti)
summary(m_resp_senti_GAD)
```

```{r}
m_resp_senti_GAD_EVPE <- lmer(avg_senti_resp ~ GAD*EVPE + (1|exam_num) + (1|ID) + (1|ResponseNumber), data = df_by_resp_word_count_wide_PE_senti)
summary(m_resp_senti_GAD_EVPE)
```
```{r}
p <-plot_model(m_resp_senti_GAD_EVPE, type = "int")
p
```
```{r}
library(ggeffects)
library(lme4)
pred_orig <- ggpredict(m_resp_senti_GAD_EVPE, terms = c("EVPE", "GAD"))
plot(pred_orig)
```


```{r}
m_resp_senti_GAD_score <- lmer(avg_senti_resp ~ GAD_score + (1|exam_num) + (1|ID) + (1|ResponseNumber), data = df_by_resp_word_count_wide_PE_senti_gad)
summary(m_resp_senti_GAD_score)
```
```{r}
m_resp_senti_GAD_score_EVPE <- lmer(avg_senti_resp ~ GAD_score*EVPE + (1|exam_num) + (1|ID) + (1|ResponseNumber), data = df_by_resp_word_count_wide_PE_senti_gad)
summary(m_resp_senti_GAD_score_EVPE)
```
```{r}
m_resp_senti_EVPE_reg_ratio_gad <- lmer(avg_senti_resp ~ EVPE*reg_word_ratio+GAD_score + (1|ID) + (1|exam_num), data = df_by_resp_word_count_wide_PE_senti_gad)

summary(m_resp_senti_EVPE_reg_ratio_gad)
```
```{r}
pp_check(m_resp_senti_EVPE_reg_ratio_gad)
```
##TBD
```{r}
df_response <- df %>%
  distinct(ID, exam_num, responseNumber, avg_senti_resp) %>%
  arrange(ID, exam_num, responseNumber) %>%
  group_by(ID, exam_num) %>%
  mutate(
    delta_senti = avg_senti_resp - lag(avg_senti_resp)
  ) %>%
  ungroup()
```


```{r}
m4_EVPE_reg_word <- lmer(Regulation ~ EVPE + exam_total_word + (1|ID) , data = df_by_exam_word_count_wide_PE)
summary(m4_EVPE_reg_word)

```
```{r}
pp_check(m4_EVPE_reg_word)
```
####glmer.nb
```{r}
m4_EVPE_reg_word_nb <- glmer.nb(Regulation ~ EVPE +(1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m4_EVPE_reg_word_nb)
```
```{r}
pp_check(m4_EVPE_reg_word_nb)
```

###EVPE_val vs. reg_word_ratio
```{r}
m4_EVPE_val_reg_word_ratio <- lmer(reg_word_ratio ~ EVPE_val +0 +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m4_EVPE_val_reg_word_ratio)
```
```{r}
pp_check(m4_EVPE_val_reg_word_ratio)
```
```{r}
plot_models(m4_EVPE_val_reg_word_ratio, title = "EVPE_val vs. Regulation ratio")
```

```{r}
emmeans(m4_EVPE_val_reg_word_ratio, pairwise~EVPE_val, adjust = "none")
```
```{r}
m4_EVPE_reg_val_word <- lmer(Regulation ~ EVPE_val + exam_total_word + 0 + (1|ID), data = df_by_exam_word_count_wide_PE)
summary(m4_EVPE_reg_val_word)
```
```{r}
m4_EVPE_reg_val_word_nb <- glmer.nb(Regulation ~ EVPE_val + 0 + (1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m4_EVPE_reg_val_word_nb)
```
```{r}
pp_check(m4_EVPE_reg_val_word)
```

###EVPE_mag vs. reg_word_ratio
####lmer
```{r}
m4_EVPE_mag_reg_word_ratio <- lmer(reg_word_ratio ~ EVPE_mag +0 +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m4_EVPE_mag_reg_word_ratio)
```
```{r}
pp_check(m4_EVPE_mag_reg_word_ratio)
```
```{r}
df_by_exam_word_count_wide_PE$EVPE_val <- as.factor(df_by_exam_word_count_wide_PE$EVPE_val)
df_by_exam_word_count_wide_PE$EVPE_val <- relevel(df_by_exam_word_count_wide_PE$EVPE_val, ref = "positive")
```

```{r}
m4_EVPE_val_mag_reg_word_ratio <- lmer(reg_word_ratio ~ EVPE_val*EVPE_mag+0 +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m4_EVPE_val_mag_reg_word_ratio)
```
```{r}
df_by_exam_word_count_wide_PE_filter <- df_by_exam_word_count_wide_PE %>% filter(reg_word_ratio !=0)
```

```{r}
m4_EVPE_val_mag_reg_word_ratio_nozero <- lmer(reg_word_ratio ~ EVPE_val*EVPE_mag +(1|ID), data = df_by_exam_word_count_wide_PE_filter)
summary(m4_EVPE_val_mag_reg_word_ratio_nozero)
```
```{r}
pp_check(m4_EVPE_val_mag_reg_word_ratio_nozero)
```

```{r}
plot_model(m4_EVPE_val_mag_reg_word_ratio_nozero, type = "int")
```

```{r}
plot_model(m4_EVPE_val_mag_reg_word_ratio, type = "int")
```
```{r}
hist(df_by_exam_word_count_wide_PE$reg_word_ratio)
```

###EVPE vs. exp
```{r}
# Using word_ratio
m4_EVPE_exp_word_ratio <- lmer(exp_word_ratio ~ EVPE +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m4_EVPE_exp_word_ratio)
```
```{r}
pp_check(m4_EVPE_exp_word_ratio)
```
```{r}
m4_EVPE_exp_word <- lmer(Expression ~ EVPE + exam_total_word + (1|ID) , data = df_by_exam_word_count_wide_PE)
summary(m4_EVPE_exp_word)
```
```{r}
pp_check(m4_EVPE_exp_word)
```
#### glmer.nb
```{r}
m4_EVPE_exp_word_nb <- glmer.nb(Expression ~ EVPE +(1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m4_EVPE_exp_word_nb)
```
```{r}
pp_check(m4_EVPE_exp_word_nb)
```
#### EVPE_val vs. exp_word
```{r}
m3_EVPE_val_exp_word_ratio <- lmer(exp_word_ratio ~ EVPE_val +0 +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m3_EVPE_val_exp_word_ratio)
```
```{r}
emmeans(m3_EVPE_val_exp_word_ratio, pairwise~EVPE_val, adjust = "none")
```

```{r}
m3_EVPE_val_exp_word <- lmer(Expression ~ EVPE_val + exam_total_word + 0 + (1|ID), data = df_by_exam_word_count_wide_PE)
summary(m3_EVPE_val_exp_word)
```
```{r}
pp_check(m3_EVPE_val_exp_word)
```
```{r}
m3_EVPE_val_exp_word_nb <- glmer.nb(Expression ~ EVPE_val + 0+ (1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m3_EVPE_val_exp_word_nb)
```
```{r}
pp_check(m3_EVPE_val_exp_word_nb)
```
####EVPE_mag vs. exp_word
```{r}
m4_EVPE_mag_exp_word_ratio <- lmer(exp_word_ratio ~ EVPE_mag +0 +(1|ID), data = df_by_exam_word_count_wide_PE)
summary(m4_EVPE_mag_exp_word_ratio)
```

```{r}
m4_EVPE_mag_exp_word <- lmer(Expression ~ EVPE_mag + exam_total_word + 0 + (1|ID), data = df_by_exam_word_count_wide_PE)
summary(m4_EVPE_mag_exp_word)
```

```{r}
m4_EVPE_mag_exp_word_nb <- glmer.nb(Expression ~ EVPE_mag + 0+ (1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m4_EVPE_mag_exp_word_nb)
```
#### EVPE_val * EVPE_mag
```{r}
m4_EVPE_val_mag_exp_word <- lmer(exp_word_ratio ~ EVPE_val * EVPE_mag + 0+ (1|ID) , data = df_by_exam_word_count_wide_PE)
summary(m4_EVPE_val_mag_exp_word)
```
```{r}
m4_EVPE_val_mag_exp_word <- lmer(Expression ~ EVPE_val * EVPE_mag + exam_total_word+ 0+ (1|ID) , data = df_by_exam_word_count_wide_PE)
summary(m4_EVPE_val_mag_exp_word)
```
```{r}
m4_EVPE_val_mag_exp_word_nb <- glmer.nb(Expression ~ EVPE_val * EVPE_mag +exam_total_word + 0+ (1|ID), offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m4_EVPE_val_mag_exp_word_nb)
```

```{r}
m5_PE_2_EVPE_reg_word_ratio <- lmer(reg_word_ratio ~ PE_2 + EVPE + (1|ID) , data = df_by_exam_word_count_wide_PE)
summary(m5_PE_2_EVPE_reg_word_ratio)
```
```{r}
m5_PE_2_EVPE_reg_word <- lmer(Regulation ~ PE_2 + EVPE + exam_total_word+ (1|ID) , data = df_by_exam_word_count_wide_PE)
summary(m5_PE_2_EVPE_reg_word)
```
```{r}
m5_PE_2_EVPE_reg_word_nb <- glmer.nb(Regulation ~ PE_2 + EVPE +(1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m5_PE_2_EVPE_reg_word_nb)
```
```{r}
plot_model(m5_PE_2_EVPE_reg_word_nb)
```

```{r}
m5_PE_2_EVPE_val_mag_reg_word_ratio <- lmer(reg_word_ratio ~ PE_2_val*PE_2_mag + EVPE_val*EVPE_mag + (1|ID) , data = df_by_exam_word_count_wide_PE)
summary(m5_PE_2_EVPE_val_mag_reg_word_ratio)
```
```{r}
plot_model(m5_PE_2_EVPE_val_mag_reg_word_ratio, type = "int")
```
```{r}
m5_PE_2_EVPE_val_mag_reg_word_nb <- glmer.nb(Regulation ~ PE_2_val*PE_2_mag + EVPE_val*EVPE_mag +(1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m5_PE_2_EVPE_val_mag_reg_word_nb)
```
```{r}
plot_model(m5_PE_2_EVPE_val_mag_reg_word_nb, type = "int")
```

```{r}
m5_PE_1_EVPE_reg_word_ratio <- lmer(reg_word_ratio ~ PE_1 + EVPE + (1|ID) , data = df_by_exam_word_count_wide_PE)
summary(m5_PE_1_EVPE_reg_word_ratio)
```
```{r}
m5_PE_1_EVPE_reg_word <- lmer(Regulation ~ PE_1 + EVPE + exam_total_word+ (1|ID) , data = df_by_exam_word_count_wide_PE)
summary(m5_PE_1_EVPE_reg_word)
```

```{r}
m5_PE_1_EVPE_reg_word_nb <- glmer.nb(Regulation ~ PE_1 + EVPE +(1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m5_PE_1_EVPE_reg_word_nb)
```
```{r}
m5_PE_1_PE_2_EVPE_reg_word_nb <- glmer.nb(Regulation ~ PE_1 +PE_2+ EVPE +(1|ID) ,offset = log(exam_total_word), data = df_by_exam_word_count_wide_PE)
summary(m5_PE_1_PE_2_EVPE_reg_word_nb)
```

## Brms
### Loess
#### PE_2
```{r}
brm_PE_2_val_mag_ratio <- brm(reg_word_ratio ~ t2(PE_2_mag, by = PE_2_val),
            data = df_by_exam_word_count_wide_PE, chains = 4)
summary(brm_PE_2_val_mag_ratio)
plot(conditional_effects(brm_PE_2_val_mag_ratio), ask = FALSE)
```
```{r}
brm_PE_2_val_mag <- brm(Regulation ~ t2(PE_2_mag, by = PE_2_val) + exam_total_word,
            data = df_by_exam_word_count_wide_PE, chains = 4)
summary(brm_PE_2_val_mag)
plot(conditional_effects(brm_PE_2_val_mag), ask = FALSE)
```
#### PE_1
```{r}
brm_PE_1_val_mag_ratio <- brm(reg_word_ratio ~ t2(PE_1_mag, by = PE_1_val),
            data = df_by_exam_word_count_wide_PE, chains = 4)
summary(brm_PE_1_val_mag_ratio)
plot(conditional_effects(brm_PE_1_val_mag_ratio), ask = FALSE)
```
```{r}
brm_PE_1_val_mag <- brm(Regulation ~ t2(PE_1_mag, by = PE_1_val) + exam_total_word,
            data = df_by_exam_word_count_wide_PE, chains = 4)
summary(brm_PE_1_val_mag)
plot(conditional_effects(brm_PE_1_val_mag), ask = FALSE)
```
#### EVPE
```{r}
brm_EVPE_val_mag <- brm(Regulation ~ t2(EVPE_mag, by = EVPE_val) + exam_total_word,
            data = df_by_exam_word_count_wide_PE, chains = 4)
summary(brm_EVPE_val_mag)
plot(conditional_effects(brm_EVPE_val_mag), ask = FALSE)
```
```{r}
pp_check(brm_EVPE_val_mag)
```
```{r}
brm_EVPE_val_mag_ratio <- brm(reg_word_ratio ~ t2(EVPE_mag, by = EVPE_val),
            data = df_by_exam_word_count_wide_PE, chains = 4)
summary(brm_EVPE_val_mag_ratio)
plot(conditional_effects(brm_EVPE_val_mag_ratio), ask = FALSE)
```
```{r}
pp_check(brm_EVPE_val_mag_ratio)
```

####PE<40
```{r}
df_by_exam_word_count_wide_EVPE_ub <- df_by_exam_word_count_wide_PE %>% filter(EVPE_mag<=40)
brm_EVPE_val_mag_ratio_ub <- brm(reg_word_ratio ~ t2(EVPE_mag, by = EVPE_val),
            data = df_by_exam_word_count_wide_EVPE_ub, chains = 4)
summary(brm_EVPE_val_mag_ratio_ub)
plot(conditional_effects(brm_EVPE_val_mag_ratio_ub), ask = FALSE)
```
```{r}
brm_EVPE_val_mag_ub <- brm(Regulation ~ t2(EVPE_mag, by = EVPE_val) + exam_total_word,
            data = df_by_exam_word_count_wide_EVPE_ub, chains = 4)
summary(brm_EVPE_val_mag_ub)
plot(conditional_effects(brm_EVPE_val_mag_ub), ask = FALSE)
```
```{r}
df_by_exam_word_count_wide_PE_2_ub <- df_by_exam_word_count_wide_PE %>% filter(PE_2_mag<=20)
brm_PE_2_val_mag_ratio_ub <- brm(reg_word_ratio ~ t2(PE_2_mag, by = PE_2_val),
            data = df_by_exam_word_count_wide_PE_2_ub, chains = 4)
summary(brm_PE_2_val_mag_ratio_ub)
plot(conditional_effects(brm_PE_2_val_mag_ratio_ub), ask = FALSE)
```
```{r}
brm_PE_2_val_mag_ub <- brm(Regulation ~ t2(PE_2_mag, by = PE_2_val) + exam_total_word,
            data = df_by_exam_word_count_wide_PE_2_ub, chains = 4)
summary(brm_PE_2_val_mag_ub)
plot(conditional_effects(brm_PE_2_val_mag_ub), ask = FALSE)
```
```{r}
df_by_exam_word_count_wide_PE_2_posneg <- df_by_exam_word_count_wide_PE %>% filter(PE_2_val != "zero" & PE_2_mag <=40)
df_by_exam_word_count_wide_PE_2_posneg$PE_2_val <- relevel(df_by_exam_word_count_wide_PE_2_posneg$PE_2_val, ref = "positive")
brm_PE_2_val_mag_ratio_posneg <- brm(reg_word_ratio ~ t2(PE_2_mag, by = PE_2_val),
            data = df_by_exam_word_count_wide_PE_2_posneg, chains = 4)
summary(brm_PE_2_val_mag_ratio_posneg)
plot(conditional_effects(brm_PE_2_val_mag_ratio_posneg), ask = FALSE)
```

```{r}
brm_PE_2_val_mag_posneg <- brm(Regulation ~ t2(PE_2_mag, by = PE_2_val) + exam_total_word,
            data = df_by_exam_word_count_wide_PE_2_posneg, chains = 4)
summary(brm_PE_2_val_mag_posneg)
plot(conditional_effects(brm_PE_2_val_mag_posneg), ask = FALSE)
```

```{r}
df_by_exam_word_count_wide_PE_1_ub <- df_by_exam_word_count_wide_PE %>% filter(PE_1_mag<=40)
brm_PE_1_val_mag_ratio_ub <- brm(reg_word_ratio ~ t2(PE_1_mag, by = PE_1_val),
            data = df_by_exam_word_count_wide_PE_1_ub, chains = 4)
summary(brm_PE_1_val_mag_ratio_ub)
plot(conditional_effects(brm_PE_1_val_mag_ratio_ub), ask = FALSE)
```
```{r}
brm_PE_1_val_mag_ub <- brm(Regulation ~ t2(PE_1_mag, by = PE_1_val) + exam_total_word,
            data = df_by_exam_word_count_wide_PE_1_ub, chains = 4)
summary(brm_PE_1_val_mag_ub)
plot(conditional_effects(brm_PE_1_val_mag_ub), ask = FALSE)
```
```{r}
df_by_exam_word_count_wide_PE_1_posneg <- df_by_exam_word_count_wide_PE %>% filter(PE_1_val != "zero" & PE_1_mag <=40)
df_by_exam_word_count_wide_PE_1_posneg$PE_1_val <- as.factor(df_by_exam_word_count_wide_PE_1_posneg$PE_1_val)
df_by_exam_word_count_wide_PE_1_posneg$PE_1_val <- relevel(df_by_exam_word_count_wide_PE_1_posneg$PE_1_val, ref = "positive")
brm_PE_1_val_mag_ratio_posneg <- brm(reg_word_ratio ~ t2(PE_1_mag, by = PE_1_val),
            data = df_by_exam_word_count_wide_PE_1_posneg, chains = 4)
summary(brm_PE_1_val_mag_ratio_posneg)
plot(conditional_effects(brm_PE_1_val_mag_ratio_posneg), ask = FALSE)
```
```{r}
brm_PE_1_val_mag_posneg <- brm(Regulation ~ t2(PE_1_mag, by = PE_1_val) + exam_total_word,
            data = df_by_exam_word_count_wide_PE_1_posneg, chains = 4)
summary(brm_PE_1_val_mag_posneg)
plot(conditional_effects(brm_PE_1_val_mag_posneg), ask = FALSE)
```
### Linear
#### PE_2
```{r}
zoib_PE_2_reg_ratio_formula <- bf(reg_ratio ~ PE_2_mag*PE_2_val, 
                                 phi ~ 1,
                                 zoi~1,
                                 coi~1)
```
```{r}
df_by_exam_word_count_wide_PE2 <- df_by_exam_word_count_wide_PE %>% filter(PE_2_val!="zero")
```
```{r}
df_by_exam_pe_pe2 <- df_by_exam_pe %>% filter(PE_2_val !="zero")
df_by_exam_pe_pe2 <- df_by_exam_pe_pe2 %>% filter(PE_2_mag <=60)
```
```{r}
brm_linear_PE_2_val_mag_ratio_60 <- brm(zoib_PE_2_reg_ratio_formula,
            data = df_by_exam_pe_pe2, family = zero_one_inflated_beta())
summary(brm_linear_PE_2_val_mag_ratio_60)
plot(conditional_effects(brm_linear_PE_2_val_mag_ratio_60), ask = FALSE)
pp_check(brm_linear_PE_2_val_mag_ratio_60)
```
```{r}
brm_linear_PE_2_val_mag_ratio <- brm(zoib_PE_2_reg_ratio_formula,
            data = df_by_exam_pe_pe2, family = zero_one_inflated_beta())
summary(brm_linear_PE_2_val_mag_ratio)
plot(conditional_effects(brm_linear_PE_2_val_mag_ratio), ask = FALSE)
pp_check(brm_linear_PE_2_val_mag_ratio)
```
#### Plotting
```{r}
PE_2_val_mag_reg_phrase_ratio_plotting <- conditional_effects(brm_linear_PE_2_val_mag_ratio)
PE_2_val_mag_reg_phrase_ratio_plotting_list <- plot(PE_2_val_mag_reg_phrase_ratio_plotting, plot = FALSE)
PE_2_val_mag_reg_phrase_ratio_plotting_main <- PE_2_val_mag_reg_phrase_ratio_plotting_list[[3]]
```

```{r}
PE_2_val_mag_reg_ratio_phrase_plot_main_fn <- PE_2_val_mag_reg_phrase_ratio_plotting_main +
  labs(#title = "Interaction effect of PE 2 valence and magnitude on regulation",
    x = "|PE|",
    y = "Regulation proportion",
    color = "PE valence",
    fill = "PE valence") +
  theme_classic() +
  theme(
    plot.caption = element_text(
      size = 10,
      hjust = 0
    )
  )
PE_2_val_mag_reg_ratio_phrase_plot_main_fn
```
```{r}
brm_linear_PE_2_pos_neg_mag_ratio <- brm(zoib_PE_2_reg_ratio_formula,
            data = df_by_exam_word_count_wide_PE2, family = zero_one_inflated_beta())
summary(brm_linear_PE_2_pos_neg_mag_ratio)
plot(conditional_effects(brm_linear_PE_2_pos_neg_mag_ratio), ask = FALSE)
pp_check(brm_linear_PE_2_pos_neg_mag_ratio)
```

```{r}
brm_PE_2_val_mag <- brm(Regulation ~ t2(PE_2_mag, by = PE_2_val) + exam_total_word,
            data = df_by_exam_pe, chains = 4)
summary(brm_PE_2_val_mag)
plot(conditional_effects(brm_PE_2_val_mag), ask = FALSE)
```

```{r}
zoib_EVPE_only_reg_ratio_formula <- bf(reg_word_ratio ~ EVPE, 
                                 phi ~ 1,
                                 zoi~1,
                                 coi~1)
```

```{r}
brm_linear_EVPE_ratio <- brm(zoib_EVPE_only_reg_ratio_formula,
            data = df_by_exam_word_count_wide_PE, family = zero_one_inflated_beta())
summary(brm_linear_EVPE_ratio)
plot(conditional_effects(brm_linear_EVPE_ratio), ask = FALSE)
pp_check(brm_linear_EVPE_ratio)
get_prior(brm_linear_EVPE_ratio)
```
#### Final model: reg_ratio ~ EVPE_val * EVPE_mag


```{r}
zoib_EVPE_reg_phrase_ratio_formula <- bf(reg_ratio ~ EVPE_mag*EVPE_val, 
                                 phi ~ 1,
                                 zoi~1,
                                 coi~1)
```

```{r}
brm_linear_EVPE_val_mag_reg_phrase_ratio <- brm(zoib_EVPE_reg_phrase_ratio_formula,
            data = df_by_exam_pe, family = zero_one_inflated_beta())
summary(brm_linear_EVPE_val_mag_reg_phrase_ratio)
plot(conditional_effects(brm_linear_EVPE_val_mag_reg_phrase_ratio), ask = FALSE)
pp_check(brm_linear_EVPE_val_mag_reg_phrase_ratio)
get_prior(brm_linear_EVPE_val_mag_reg_phrase_ratio)
```
#### Plotting
```{r}
EVPE_val_mag_reg_phrase_ratio_plotting <- conditional_effects(brm_linear_EVPE_val_mag_reg_phrase_ratio)
EVPE_val_mag_reg_phrase_ratio_plotting_list <- plot(EVPE_val_mag_reg_phrase_ratio_plotting, plot = FALSE)
EVPE_val_mag_reg_phrase_ratio_plotting_main <- EVPE_val_mag_reg_phrase_ratio_plotting_list[[3]]
```

```{r}
EVPE_val_mag_reg_ratio_phrase_plot_main_fn <- EVPE_val_mag_reg_phrase_ratio_plotting_main +
  labs(#title = "Interaction effect of PE valence and magnitude on regulation",
    x = "|PE|",
    y = "Regulation proportion",
    color = "PE valence",
    fill = "PE valence") +
  theme_classic() +
  theme(
    plot.caption = element_text(
      size = 10,
      hjust = 0
    )
  )
EVPE_val_mag_reg_ratio_phrase_plot_main_fn
ggsave(file = "/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/interaction_EVPE_val_mag_reg_ratio_phrase_abs.png",plot = EVPE_val_mag_reg_ratio_phrase_plot_main_fn, width = 6, heigh = 4, dpi = 300)

ggsave(file = "/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/interaction_EVPE_val_mag_reg_ratio_phrase_abs.pdf",plot = EVPE_val_mag_reg_ratio_phrase_plot_main_fn, width = 6, heigh = 4, dpi = 300)

ggsave(file = "/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/interaction_EVPE_val_mag_reg_ratio_phrase_abs.eps",plot = EVPE_val_mag_reg_ratio_phrase_plot_main_fn, width = 6, heigh = 4, dpi = 300)
```

```{r}
zoib_EVPE_reg_ratio_formula <- bf(reg_word_ratio ~ EVPE_mag*EVPE_val, 
                                 phi ~ 1,
                                 zoi~1,
                                 coi~1)
```

```{r}
brm_linear_EVPE_val_mag_ratio <- brm(zoib_EVPE_reg_ratio_formula,
            data = df_by_exam_word_count_wide_PE, family = zero_one_inflated_beta())
summary(brm_linear_EVPE_val_mag_ratio)
plot(conditional_effects(brm_linear_EVPE_val_mag_ratio), ask = FALSE)
pp_check(brm_linear_EVPE_val_mag_ratio)
get_prior(brm_linear_EVPE_val_mag_ratio)
```
```{r}
plot(brm_linear_EVPE_val_mag_ratio)
```
```{r}
plot(conditional_effects(brm_linear_EVPE_val_mag_ratio, method = "posterior_epred"), points = TRUE)
```
```{r}
library(bayesplot)
library(tidybayes)

# Extract draws on the response/probability scale
draws <- as_draws_df(brm_linear_EVPE_val_mag_ratio)
names(draws)
interaction_draws <- draws$`b_EVPE_mag:EVPE_valpositive`
mean(interaction_draws > 0)
```

```{r}
EVPE_val_mag_reg_ratio_plotting <- conditional_effects(brm_linear_EVPE_val_mag_ratio)
EVPE_val_mag_reg_ratio_plotting_list <- plot(EVPE_val_mag_reg_ratio_plotting, plot = FALSE)
EVPE_val_mag_reg_ratio_plot_main <- EVPE_val_mag_reg_ratio_plotting_list[[3]]
```

```{r}
EVPE_val_mag_reg_ratio_plot_main_fn <- EVPE_val_mag_reg_ratio_plot_main +
  labs(title = "Interaction effect of PE valence and magnitude on regulation",
    x = "｜PE｜",
    y = "Regulation proportion",
    color = "PE valence",
    fill = "PE valence") +
  theme_classic() +
  theme(
    plot.caption = element_text(
      size = 10,
      hjust = 0
    )
  )
EVPE_val_mag_reg_ratio_plot_main_fn
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/interaction_EVPE_val_mag_reg_ratio_abs.png",plot = EVPE_val_mag_reg_ratio_plot_main_fn, width = 6, heigh = 4, dpi = 300)

ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/interaction_EVPE_val_mag_reg_ratio_abs.pdf",plot = EVPE_val_mag_reg_ratio_plot_main_fn, width = 6, heigh = 4, dpi = 300)

ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/interaction_EVPE_val_mag_reg_ratio_abs.eps",plot = EVPE_val_mag_reg_ratio_plot_main_fn, width = 6, heigh = 4, dpi = 300)
```

```{r}
lmer_linear_EVPE_val_mag_ratio <- lmer(reg_word_ratio ~ EVPE_mag*EVPE_val+(1|ID)+(1|exam_num), data = df_by_exam_word_count_wide_PE)

summary(lmer_linear_EVPE_val_mag_ratio)
```
```{r}
AIC(lmer_linear_EVPE_val_mag_ratio, brm_linear_EVPE_val_mag_ratio)
BIC(lmer_linear_EVPE_val_mag_ratio, brm_linear_EVPE_val_mag_ratio)
```
#### reg_word_ratio ~ EVPE_val * EVPE_mag * GAD
```{r}
zoib_EVPE_reg_ratio_GAD_formula <- bf(reg_word_ratio ~ EVPE_mag*EVPE_val*GAD + (1|ID) + (1|exam_num), 
                                 phi ~ 1,
                                 zoi~1,
                                 coi~1)
```

```{r}
brm_linear_EVPE_val_mag_ratio_GAD <- brm(zoib_EVPE_reg_ratio_GAD_formula,
            data = df_by_exam_word_count_wide_PE, family = zero_one_inflated_beta())
summary(brm_linear_EVPE_val_mag_ratio_GAD)
plot(conditional_effects(brm_linear_EVPE_val_mag_ratio_GAD), ask = FALSE)
pp_check(brm_linear_EVPE_val_mag_ratio_GAD)
get_prior(brm_linear_EVPE_val_mag_ratio_GAD)
```

```{r}
df_zoib <- df_by_exam_word_count_wide_PE %>%
  dplyr::mutate(
    EVPE_mag_z = as.numeric(scale(EVPE_mag)),
    GAD_z = as.numeric(scale(GAD)),
    EVPE_val = factor(EVPE_val)
  )
```
```{r}
priors <- c(
  prior(normal(0, 0.5), class = "b"),
  prior(normal(0, 1), class = "Intercept"),
  prior(normal(0, 1), class = "phi"),
  prior(normal(0, 1), class = "Intercept", dpar = "zoi"),
  prior(normal(0, 1), class = "Intercept", dpar = "coi")
)
```
```{r}
zoib_EVPE_reg_ratio_GAD_formula <- bf(
  reg_word_ratio ~ EVPE_mag_z * EVPE_val * GAD_z,
  phi ~ 1,
  zoi ~ 1,
  coi ~ 1
)

brm_linear_EVPE_val_mag_ratio_GAD <- brm(
  zoib_EVPE_reg_ratio_GAD_formula,
  data = df_zoib,
  family = zero_one_inflated_beta(),
  chains = 4,
  cores = 4,
  iter = 4000,
  control = list(adapt_delta = 0.95, max_treedepth = 15),
  init = 0
)
```

```{r}
summary(brm_linear_EVPE_val_mag_ratio_GAD)
plot(conditional_effects(brm_linear_EVPE_val_mag_ratio_GAD), ask = FALSE)
pp_check(brm_linear_EVPE_val_mag_ratio_GAD)
```
#### reg_phrase_ratio ~ EVPE_val * EVPE_mag * GAD
```{r}
df_zoib_reg_phrase <- df_by_exam_pe %>%
  dplyr::mutate(
    EVPE_mag_z = as.numeric(scale(EVPE_mag)),
    GAD_z = as.numeric(scale(GAD)),
    EVPE_val = factor(EVPE_val)
  )
```

```{r}
priors <- c(
  prior(normal(0, 0.5), class = "b"),
  prior(normal(0, 1), class = "Intercept"),
  prior(normal(0, 1), class = "phi"),
  prior(normal(0, 1), class = "Intercept", dpar = "zoi"),
  prior(normal(0, 1), class = "Intercept", dpar = "coi")
)
```
```{r}
zoib_EVPE_reg_phrase_ratio_GAD_formula <- bf(
  reg_ratio ~ EVPE_mag_z * EVPE_val * GAD_z,
  phi ~ 1,
  zoi ~ 1,
  coi ~ 1
)

brm_linear_EVPE_val_mag_phrase_ratio_GAD <- brm(
  zoib_EVPE_reg_phrase_ratio_GAD_formula,
  data = df_zoib_reg_phrase,
  family = zero_one_inflated_beta(),
  chains = 4,
  cores = 4,
  iter = 4000,
  control = list(adapt_delta = 0.95, max_treedepth = 15),
  init = 0
)
```
```{r}
summary(brm_linear_EVPE_val_mag_phrase_ratio_GAD)
plot(conditional_effects(brm_linear_EVPE_val_mag_phrase_ratio_GAD), ask = FALSE)
pp_check(brm_linear_EVPE_val_mag_phrase_ratio_GAD)
```
#### reg_ratio ~ EVPE_val * EVPE_mag* GAD_score
```{r}
df_zoib_GAD_score <- inner_join(df_zoib, df_mood, by = "ID")
``` 
```{r}
df_zoib_GAD_score <- df_zoib_GAD_score %>%
  dplyr::mutate(
    GAD_score_z = as.numeric(scale(GAD_score))
  )
```

```{r}
priors <- c(
  prior(normal(0, 0.5), class = "b"),
  prior(normal(0, 1), class = "Intercept"),
  prior(normal(0, 1), class = "phi"),
  prior(normal(0, 1), class = "Intercept", dpar = "zoi"),
  prior(normal(0, 1), class = "Intercept", dpar = "coi")
)
```
```{r}
zoib_EVPE_reg_ratio_GAD_score_formula <- bf(
  reg_word_ratio ~ EVPE_mag_z * EVPE_val * GAD_score_z,
  phi ~ 1,
  zoi ~ 1,
  coi ~ 1
)

brm_linear_EVPE_val_mag_ratio_GAD_score <- brm(
  zoib_EVPE_reg_ratio_GAD_score_formula,
  data = df_zoib_GAD_score,
  family = zero_one_inflated_beta(),
  chains = 4,
  cores = 4,
  iter = 4000,
  control = list(adapt_delta = 0.95, max_treedepth = 15),
  init = 0
)
```

```{r}
summary(brm_linear_EVPE_val_mag_ratio_GAD_score)
plot(conditional_effects(brm_linear_EVPE_val_mag_ratio_GAD_score), ask = FALSE)
pp_check(brm_linear_EVPE_val_mag_ratio_GAD_score)
```

#### PE_1
```{r}
df_by_exam_word_count_wide_PE1 <- df_by_exam_word_count_wide_PE %>% filter(PE_1_val!="zero")
```

```{r}
zoib_PE_1_reg_ratio_formula <- bf(reg_word_ratio ~ PE_1_mag*PE_1_val, 
                                 phi ~ 1,
                                 zoi~1,
                                 coi~1)
```

```{r}
brm_linear_PE_1_val_mag_ratio <- brm(zoib_PE_1_reg_ratio_formula,
            data = df_by_exam_word_count_wide_PE, family = zero_one_inflated_beta())
summary(brm_linear_PE_1_val_mag_ratio)
plot(conditional_effects(brm_linear_PE_1_val_mag_ratio), ask = FALSE)
pp_check(brm_linear_PE_1_val_mag_ratio)
```
```{r}
brm_linear_PE_1_pos_neg_mag_ratio <- brm(zoib_PE_1_reg_ratio_formula,
            data = df_by_exam_word_count_wide_PE1, family = zero_one_inflated_beta())
summary(brm_linear_PE_1_pos_neg_mag_ratio)
plot(conditional_effects(brm_linear_PE_1_pos_neg_mag_ratio), ask = FALSE)
pp_check(brm_linear_PE_1_pos_neg_mag_ratio)
```
####Plotting
```{r}
EVPE_val_mag_reg_ratio_plotting <- conditional_effects(brm_linear_EVPE_val_mag_ratio)
EVPE_val_mag_reg_ratio_plotting_list <- plot(EVPE_val_mag_reg_ratio_plotting, plot = FALSE)
EVPE_val_mag_reg_ratio_plot_main <- EVPE_val_mag_reg_ratio_plotting_list[[3]]
```
```{r}
EVPE_val_mag_reg_ratio_plot_main_fn <- EVPE_val_mag_reg_ratio_plot_main +
  labs(title = "Interaction effect of EVPE valence and magnitude on regulation",
    x = "The magnitude of EVPE",
    y = "Regulation-related word ratio",
    color = "EVPE valence",
    fill = "EVPE valence") +
  theme_classic() +
  theme(
    plot.caption = element_text(
      size = 10,
      hjust = 0
    )
  )
EVPE_val_mag_reg_ratio_plot_main_fn
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/interaction_EVPE_val_mag_reg_ratio.png",plot = EVPE_val_mag_reg_ratio_plot_main_fn, width = 6, heigh = 4, dpi = 300)

ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/interaction_EVPE_val_mag_reg_ratio.pdf",plot = EVPE_val_mag_reg_ratio_plot_main_fn, width = 6, heigh = 4, dpi = 300)
```



# discarded
```{r, include = FALSE}
# fit_word_count_label <- lmer(sum_word_count ~ label_api_text  + (1|ID), data = df_by_exam_word_count_PE)
# 
# summary(fit_word_count_label)

# emmeans(fit_word_count_label, pairwise~label_api_text, adjust = "none")

# fit_word_count_label_exam <- lmer(sum_word_count ~ label_api_text+exam_num+label_api_text*exam_num  + 0+ (1|ID), data = df_by_exam_word_count_PE)

# summary(fit_word_count_label_exam)

# pp_check(fit_word_count_label_exam)
```

```{r, include = FALSE}
# fit_word_count_label_nb <- glmer.nb(sum_word_count ~ label_api_text + (1|ID), data = df_by_exam_word_count_PE)
# summary(fit_word_count_label_nb)

# pp_check(fit_word_count_label_nb)

# fit_word_count_label_exam_nb <- glmer.nb(sum_word_count ~ label_api_text + exam_num + label_api_text*exam_num + (1|ID), data = df_by_exam_word_count_PE)
# summary(fit_word_count_label_exam_nb)

# pp_check(fit_word_count_label_exam_nb)
```

```{r, include = FALSE}
fit_word_count_PE1 <- lmer(sum_word_count ~ PE_1 + label_api_text+label_api_text*PE_1 + (1|ID), data = df_by_exam_word_count_PE)

summary(fit_word_count_PE1)

fit_word_count_PE2 <- lmer(sum_word_count ~ PE_2 + label_api_text+label_api_text*PE_2 + (1|ID), data = df_by_exam_word_count_PE)

summary(fit_word_count_PE2)

# fit_word_count_exam_PE <- lmer(sum_word_count ~ exam_num+label_api_text + (1|ID), data = df_by_exam_word_count_PE)
# 
# summary(fit_word_count_exam_PE)
```

```{r, include = FALSE}
# fit_word_count_cat_exam_PE_nb <- glmer.nb(sum_word_count ~ exam_num+label_api_text + (1|ID), data = df_by_exam_word_count_PE)
# 
# summary(fit_word_count_cat_exam_PE_nb)

# pp_check(fit_word_count_cat_exam_PE_nb)

# fit_word_count_label_PE1_nb <- glmer.nb(sum_word_count ~ label_api_text + PE_1 + label_api_text*PE_1 + (1|ID), data = df_by_exam_word_count_PE)
# 
# summary(fit_word_count_label_PE1_nb)
# pp_check(fit_word_count_label_PE1_nb)

# fit_word_count_label_PE2_nb <- glmer.nb(sum_word_count ~ label_api_text + PE_2 + exam_num+ label_api_text*PE_2*exam_num + (1|ID), data = df_by_exam_word_count_PE)
# 
# summary(fit_word_count_label_PE2_nb)
# pp_check(fit_word_count_label_PE2_nb)

# fit_word_count_label_PE2_exam_nb <- glmer.nb(sum_word_count ~ label_api_text + PE_2 + exam_num+ label_api_text*PE_2*exam_num + (1|ID), data = df_by_exam_word_count_PE)
# 
# summary(fit_word_count_label_PE2_exam_nb)
# pp_check(fit_word_count_label_PE2_exam_nb)
```

##Temporal Autocorrelation
### acf()
*** padding the exam_resp data***
```{r}
# Pad the dataset with NA
# Because the acf() function assumes each data point is equally separate, adding NA rows to even the number of data point
# The max data is 18, therefore, analyze 17 lags. Adding more rows (18) between each sample unit in the dataset (why?)
df_by_exam_resp_expand <- df_by_exam_resp %>% group_by(ID) %>% complete(exam_resp = 1:36) 
```
```{r}
df_by_exam_resp_PE <- inner_join(df_by_exam_resp, df_PE_correct, by=c("ID", "exam_num"))
```

```{r}
fit_acf_brms <- brm(Regulation ~ PE_1 + exam_num + (1|ID), data = df_by_exam_resp_PE %>% filter(!is.na(PE_1)), family = negbinomial())

df_by_exam_resp_PE_no_na <- df_by_exam_resp_PE %>% filter(!is.na(PE_1))

df_by_exam_resp_PE_no_na$res <- residuals(fit_acf_brms)
```

```{r}
df_by_exam_resp_PE_no_na_expand <- df_by_exam_resp_PE_no_na %>% group_by(ID) %>% complete(exam_resp = 1:36) 

acf(df_by_exam_resp_PE_no_na_expand$res, lag.max = 17, na.action = na.pass, ci = 0)

```
## brms temporal Autocorrelation


```{r}
rows_to_jitter <- df_by_resp_time_tmp %>%
  group_by(ID, time_since_grade_reveal_mins) %>%
  filter(n() > 1) %>% # This identifies groups with duplicates
  ungroup() %>%
  pull(original_row_index)
```
```{r}
set.seed(123) # For reproducibility of the jitter
df_by_resp_time$time_since_grade_reveal_mins[rows_to_jitter] <-
  df_by_resp_time$time_since_grade_reveal_mins[rows_to_jitter] +
  runif(length(rows_to_jitter), 0.001, 0.005)

# check
# duplicated_times_after_jitter <- df_by_resp_time %>%
#   group_by(ID, time_since_grade_reveal_mins) %>%
#   filter(n() > 1) %>%
#   ungroup()
# 
# duplicated_times_after_jitter
```
```{r}
df_PE_correct$ID <- as.factor(df_PE_correct$ID)
```

```{r}
fit_time_reg_word_response <- brm(bf(reg_word_count ~ 1 +  ar(time = time_since_grade_reveal_mins, gr = ID, p = 1), family = negbinomial()), data = df_by_resp_time)

summary(fit_time_reg_word_response)
```
*** ar[1] (autoregressive coefficient) = 0.06: reg_word_count is weakly correlated with previous time_point. 95%CI include 0, indicating no significant relationships.
*** sderr(standard deviation of the random effects for ar):
estimate = 0.05, small variation in the autoregressive effect across subjects. 

```{r}
fit_time_reg_count_response <- brm(bf(reg_count ~ abs(PE_1)+(1|ID/exam_num) + ar(time = time_since_grade_reveal_mins, gr = ID:exam_num, p = 1), family = negbinomial()), data = df_by_resp_time_PE)

summary(fit_time_reg_count_response)
```
```{r}
plot(fit_time_reg_count_response, type = "acf")
```

### PE vs Reg_ratio, Response
```{r}
df_by_resp_time_PE$reg_ratio_tran <- (df_by_resp_time_PE$reg_ratio*(n-1)+0.5)/n
b1_reg_ratio_response_PE <- brm(reg_ratio_tran ~ PE_2 + (1|ID) + (1|ResponseNumber) + (1|exam_num), data = df_by_resp_time_PE, family = zero_inflated_beta())

summary(b1_reg_ratio_response_PE)
```

## Reg_ratio vs. GAD

```{r}
df_mood <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/survey_data_f24/processed/premedEMA_exit_mood_final.csv")
```

```{r}
df_by_exam_pe_gad <- inner_join(df_by_exam_pe, df_mood, by = "ID")
```

```{r}
fit_reg_word_GAD <- lmer(reg_word_ratio ~ GAD_score + EVPE+ (1|ID) + (1|exam_num), data = df_by_exam_pe_gad)
summary(fit_reg_word_GAD)
```
```{r}
fit_reg_word_ERQ <- lmer(reg_ratio ~ ERQ_score + EVPE+ (1|ID) + (1|exam_num), data = df_by_exam_pe_gad)
summary(fit_reg_word_ERQ)
```
```{r}
fit_reg_word_PHQ <- lmer(reg_ratio ~ PHQ_score + EVPE+ (1|ID) + (1|exam_num), data = df_by_exam_pe_gad)
summary(fit_reg_word_PHQ)
```

```{r}
fit_reg_word_PQB <- lmer(reg_ratio ~ PQB_score + EVPE+ (1|ID) + (1|exam_num), data = df_by_exam_pe_gad)
summary(fit_reg_word_PQB)
```


