---
title: "emoLearn_F24_senti_analysis"
author: "Runan Wang"
date: "2026-02-19"
output: html_document
---

```{r setup, include=FALSE}
library(afex)
library(emmeans)
library(knitr)
library(tidyverse)
library(compute.es)
library(car)
library(ggplot2)
library(multcomp)
library(pastecs)
library(WRS2)
library(Hmisc)
library(tidyverse)
library(SuppDists)
library(ggpubr)
library(readxl)
library(ez)
library(lme4)
library(dplyr)
library(corrplot)
library(psych)
library(ggpubr) # for Q plot (normality check)
library(openxlsx)
library(colorspace)
library(ggrepel)
library(directlabels)
library(ggplot2)
library(reshape2)
library(plyr)
library(scales)
library(wesanderson)
library(brms)
library(stringr)
library(performance)
library(see)
library(tidyr)
library(lubridate)
library(tibble)
library(bayesplot)
library(janitor)
library(sjPlot)
`select` <- dplyr::select
`recode` <- dplyr::recode
`summarise` <- dplyr::summarise
`describe` <- psych::describe
knitr::opts_chunk$set(echo = TRUE)
```
# Load in BERT sentiment file
I didn't test the accordance between chatGPT and bert models. I deleted the section fo code that test it, if I want to add them back later, see emoLearn_F24_senti_analysis.Rmd.
Colnames:
df_senti_full: contain API label, sentiment analysis from roberta, disilBERT, emoRoberta, and go_emoRoberta
***Roberta***: 
phrase_valCat_main: NEGATIVE, NEUTRAL, POSITIVE

***distilBERT***
phrase_distl_main: joy, enger, sadness, fear, love, suprise

***emoRoberta***
phrase_emo_main
***go_emoRoberta***
phrase_go_emo_mai
```{r cars}
df_senti_full <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/emaData_F24_phrase_sentiment_v5.csv")
# It wierd that there is a cate as "-0.5", I think it is mixed too.
df_senti_full <- df_senti_full %>% mutate(api_val_num = api_val)
df_senti_full <- df_senti_full %>% mutate(api_val = (case_when(api_val == 1.0 ~"POSITIVE",
                                                               api_val == 0.5 ~ "MIXED",
                                                               api_val == -0.5 ~ "MIXED",
                                                               api_val == 0 ~ "NEUTRAL",
                                                               api_val == -1 ~ "NEGATIVE")
  
))
# df_response_full <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/processed/EMA_API_response_sentiment.csv")
```
```{r}
df_senti_full <- df_senti_full %>% mutate(label_api_text = case_when(label_api == -1 ~ "Expression",
                                                           label_api == 0 ~ "Neither",
                                                           label_api == 1 ~ "Regulation"))
```

```{r}
df_mood <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/survey_data_f24/processed/premedEMA_exit_mood_final.csv")
```

```{r cars}
df_PE <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/survey_data_f24/premedEMA_f2024_predictors_df.csv")
colnames(df_PE)[1] = "ID"
# drop the wrong grade
df_PE <- df_PE %>% filter(shown_wrong !="1")
```

## Chat_GPT
```{r}
gpt_label_count <- df_senti_full %>%
  dplyr::count(api_val)

ggplot(gpt_label_count, aes(x=api_val, y = n, fill = api_val)) +
  geom_bar(stat = "identity") +
  labs(title = "chatGPT label frequency", x = "Valence", y = "Count") +
  scale_x_discrete(guide = guide_axis(angle = 45))+
  theme_classic()
```

## Collapsed

```{r}
library(dplyr)
library(tibble)

collapse_text_by_label <- function(label_api_text, api_senti) {
  r <- rle(label_api_text)
  block_id <- rep(seq_along(r$lengths), r$lengths)

  tibble(
    block_id = block_id,
    label_api_text = label_api_text,
    api_senti = api_senti
  ) %>%
    group_by(block_id) %>%
    summarise(
      text_type = first(label_api_text),
      length = n(),
      score_sum = sum(api_senti),
      score_avg = mean(api_senti),
      score_peak = api_senti[which.max(abs(api_senti))],
      score_end = last(api_senti),
      score_lead = first(api_senti),
      .groups = "drop"
    ) %>%
    mutate(
      block_sentiment = case_when(
        score_avg > 0 ~ "POSITIVE",
        score_avg < 0 ~ "NEGATIVE",
        TRUE ~ "NEUTRAL"
      )
    )
}

```

```{r}
library(dplyr)
library(tibble)

collapse_text_by_label_ratio <- function(label_api_text, api_senti) {
  r <- rle(label_api_text)
  block_id <- rep(seq_along(r$lengths), r$lengths)

  tibble(
    block_id = block_id,
    label_api_text = label_api_text,
    api_senti = api_senti
  ) %>%
    group_by(block_id) %>%
    summarise(
      text_type = first(label_api_text),
      length = n(),
      exp_sum = sum(exp_word),
      nei_sum = sum(nei_word),
      reg_sum = sum(reg_word),
      total_sum = sum(total_word),
      .groups = "drop"
    )
}

```


```{r}
# df_senti_full <- df_senti_full %>% mutate(api_val_num = case_when(api_val == "POSITIVE" ~ 1,
#                                                                   api_val == "NEUTRAL" ~ 0,
#                                                                   api_val == "MIXED" ~ 0.5,
#                                                                   api_val == "NEGATIVE" ~ -1))
```

```{r}
df_senti_full <- df_senti_full %>% mutate(api_senti_score = api_val_num * api_intensity)
```


```{r}
df_senti_full_collapsed <- df_senti_full %>%
  dplyr::group_by(ID, exam_num, ResponseNumber) %>%
  summarise(blocks = list(collapse_text_by_label(label_api_text, api_senti_score)), .groups = "drop") %>%
  tidyr::unnest(blocks)
```


```{r}
df_transitions_reg <- df_senti_full_collapsed %>%
  mutate(prev_sentiment = lag(block_sentiment),
         next_sentiment = lead(block_sentiment)) %>% filter(text_type == "Regulation") %>%
  dplyr::count(prev_sentiment, block_sentiment, next_sentiment)

df_transitions_reg <- df_transitions_reg %>%
  dplyr::mutate(
    prev_sentiment = toupper(prev_sentiment),
    block_sentiment = toupper(block_sentiment),
    next_sentiment = toupper(next_sentiment)
  )
```
```{r}
library(networkD3)
#Work on it later
#library(ggsankey)
# Prepare nodes and links
nodes <- data.frame(name = unique(c(df_transitions_reg$prev_sentiment,
                                    df_transitions_reg$block_sentiment,
                                    df_transitions_reg$next_sentiment)))
df_tmp <- df_transitions_reg[,1:3]
df_tmp_long <- df_tmp %>% make_long(prev_sentiment, next_sentiment)

plot_sankey_reg <- ggplot(df_tmp_long, aes(x = x,
                               next_x = next_x,
                               node = node,
                               next_node = next_node,
                               fill = factor(node))) +
  theme_classic()
plot_sankey_reg + geom_sankey(flow.alpha = 0.5,
                   node.color = "black",
                   show.legend = TRUE)
plot_sankey_reg
# Create link table
# links <- df_transitions_reg %>%
#   dplyr::count(prev_sentiment, block_sentiment) %>%
#   dplyr::rename(source = prev_sentiment, target = block_sentiment, value = n) %>%
#   bind_rows(
#     df_transitions_reg %>%
#       dplyr::count(block_sentiment, next_sentiment) %>%
#       dplyr::rename(source = block_sentiment, target = next_sentiment, value = n)
#   ) %>%
#   mutate(source = match(source, nodes$name) - 1,
#          target = match(target, nodes$name) - 1)

sankeyNetwork(Links = links, Nodes = nodes,
              Source = "source", Target = "target",
              Value = "value", NodeID = "name",
              fontSize = 12, nodeWidth = 30)

```

## Phrase-wise
```{r}
df_senti_full_single <- df_senti_full %>% group_by(ID, exam_num,ResponseNumber) %>% 
  mutate(prev_senti = lag(api_val),
         prev_intense = lag(api_intensity),
         next_senti = lead(api_val),
         next_intense = lead(api_intensity)) %>% ungroup()
df_senti_full_single_reg <- df_senti_full_single %>% filter(label_api_text == "Regulation")

```
```{r}
#library(ggsankey)
labels <- c("prev_senti" = "before_reg_valence",
            "api_val" = "regulation_valence",
            "next_senti" = "after_reg_valence")
df_tmp_single <- df_senti_full_single_reg %>% select(prev_senti, api_val,next_senti)
df_senti_full_single_reg_long <- df_tmp_single %>% make_long(prev_senti, api_val, next_senti)

plot_sankey_reg_single <- ggplot(df_senti_full_single_reg_long, aes(x = x,
                               next_x = next_x,
                               node = node,
                               next_node = next_node,
                               fill = factor(node))) +
  scale_x_discrete(labels = labels) +
  theme_classic()
plot_sankey_reg_single + geom_sankey(flow.alpha = 0.5,
                   node.color = "black",
                   show.legend = TRUE)
plot_sankey_reg_single
```
```{r}
library(ggsankey)
labels <- c("prev_senti" = "before_reg_valence",
            "next_senti" = "after_reg_valence")
df_tmp_single_pre_post <- df_senti_full_single_reg %>% select(prev_senti, next_senti)
df_tmp_single_pre_post_long <- df_tmp_single_pre_post %>% make_long(prev_senti, next_senti)

plot_sankey_pre_post_single <- ggplot(df_tmp_single_pre_post_long, aes(x = x,
                               next_x = next_x,
                               node = node,
                               next_node = next_node,
                               fill = factor(node))) +
  scale_x_discrete(labels = labels) +
  scale_fill_discrete(name = "Sentiemnt") + 
  labs(x = "Text type",
       title = "Sankey plot: Transition in sentiment before and after regulation") +
  theme_classic()
plot_sankey_pre_post_single + geom_sankey(flow.alpha = 0.5,
                   node.color = "black",
                   show.legend = TRUE)
plot_sankey_pre_post_single
```


## Interactive sankey
```{r}
# library(dplyr)
# df_links <- df_senti_full_single_reg_long %>%
#   filter(!is.na(next_node)) %>%
#   mutate(
#     source_label = paste(node, x, sep = "_"),
#     target_label = paste(next_node, next_x, sep = "_")
#   )
# 
# df_link_counts <- df_links %>%
#   dplyr::count(source_label, target_label, name = "value")
# 
# nodes <- data.frame(name = unique(c(df_link_counts$source_label, df_link_counts$target_label)))
# 
# links <- df_link_counts %>%
#   dplyr::mutate(
#     source = match(source_label, nodes$name) - 1,
#     target = match(target_label, nodes$name) - 1
#   ) %>%
#   dplyr::count(source, target, name = "value")
# 
# library(networkD3)
# 
# sankeyNetwork(Links = links, Nodes = nodes,
#               Source = "source", Target = "target",
#               Value = "value", NodeID = "name",
#               fontSize = 12, nodeWidth = 30)

```
# Modelling
## sentiment change vs. text_type
### phrase
#### data prep
```{r}
library(dplyr)
df_senti_score <- df_senti_full
df_senti_score <- df_senti_score %>% dplyr::group_by(ID, exam_num, ResponseNumber) %>% dplyr::mutate(val_score_delta = lead(api_senti_score) - api_senti_score) %>% ungroup()
# val_score_delta = lead(api_val_score): how does the sentiment change after current phrase. 
# the more positive the score is, the sentiment became more positive after the current phrase
```
#### model
##### valence~text_type
```{r}
df_senti_score_cat <- df_senti_score %>% dplyr::group_by(ID, exam_num, ResponseNumber) %>% dplyr::mutate(val_cat = lead(api_val))
```
valence(categorical) ~ text_type(categorical)
```{r}
m_cat_val_text_type <- brm(val_cat ~ label_api_text + (1|ID) + (1|exam_num), family = categorical(), data = df_senti_score_cat)
summary(m_cat_val_text_type)
```
```{r}
m_cat_val_curr_text_type <- brm(val_cat ~ label_api_text +api_val + (1|ID) + (1|exam_num), family = categorical(), data = df_senti_score_cat)
summary(m_cat_val_curr_text_type)
```


#### Plot
```{r}
library(dplyr)
library(brms)
library(ggplot2)
library(tidyr)

df_senti_score_cat <- df_senti_score_cat %>%
  mutate(
    label_api_text = factor(
      label_api_text,
      levels = c("Expression", "Neither", "Regulation")
    ),
    val_cat = factor(val_cat)
  )
```
```{r}
m_cat_val_text_type <- brm(
  val_cat ~ label_api_text +
    (1 | ID) +
    (1 | exam_num),
  family = categorical(),
  data = df_senti_score_cat
)
summary(m_cat_val_text_type)
```
```{r}
ce_text_type <- conditional_effects(
  m_cat_val_text_type,
  effects = "label_api_text",
  categorical = TRUE
)

p <- plot(
  ce_text_type,
  points = TRUE,
  plot = FALSE
)[[1]]
class(p)
```

```{r}
p_edit <- p +
  labs(
    x = "Phrase text category",
    y = "Predicted probability",
    color = "Valence",
    fill = "Valence",
    title = "Predicted valence by phrase category"
  ) +
  scale_x_discrete(
    labels = c(
      "Expression" = "Expression",
      "Neither" = "Neither",
      "Regulation" = "Regulation"
    )
  ) +
  scale_fill_manual(values = c(
  "NEGATIVE" = "#F8766D",
  "POSITIVE" = "#C77CFF",
    "MIXED"    = "#7CAE00",
  "NEUTRAL"  = "#00BFC4"
)) +
  scale_y_continuous(
    limits = c(0, 0.6),
    breaks = seq(0, 1, 0.2),
    labels = scales::percent_format(accuracy = 1)
  ) +
  theme_classic(base_size = 14) +
  theme(
    plot.title = element_text(
      hjust = 0.5
    ),
    
    axis.text.x = element_text(
      angle = 0,
      hjust = 0.5
    ),
    legend.position = "right",
    strip.background = element_blank(),
  )
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/phrase_val_text_type.png",plot = p_edit, width = 6, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/phrase_val_text_type.pdf",plot = p_edit, width = 6, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/phrase_val_text_type.eps",plot = p_edit, width = 6, heigh = 4, dpi = 300)
p_edit
```
```{r}
library(brms)
library(dplyr)
library(tidyr)
library(ggplot2)

# Check the actual factor levels first
levels(df_senti_score_cat$label_api_text)
levels(df_senti_score_cat$val_cat)

# Make one prediction row for each label_api_text category
newdata <- data.frame(
  label_api_text = levels(df_senti_score_cat$label_api_text)
)

# Posterior expected probabilities
# Dimensions: posterior draws × label_api_text levels × val_cat categories
epred <- posterior_epred(
  m_cat_val_text_type,
  newdata = newdata,
  re_formula = NA
)

dim(epred)
dimnames(epred)
```
```{r}
levels(df_senti_score_cat$label_api_text)
levels(df_senti_score_cat$val_cat)
```

```{r}
posterior_summary(m_cat_val_text_type_cur)
```
```{r}
df_senti_score_cat <- df_senti_score_cat %>%
  mutate(
    label_api_text = factor(
      label_api_text,
      levels = c("Expression", "Neither", "Regulation")
    ),
    val_cat = factor(val_cat)
  )
```
```{r}
df_senti_score_cat$val_cat <- relevel(df_senti_score_cat$val_cat, ref = "NEUTRAL")
levels(df_senti_score_cat$val_cat)
```
#### ***final model***
```{r}
df_senti_score_cat$api_val<- as.factor(df_senti_score_cat$api_val)
df_senti_score_cat$api_val <- relevel(df_senti_score_cat$api_val, ref = "NEGATIVE")
df_senti_score_cat$val_cat <- as.factor(df_senti_score_cat$val_cat  )
df_senti_score_cat$val_cat  <- relevel(df_senti_score_cat$val_cat , ref = "NEGATIVE")
m_cat_val_text_type_neg_neg_ref <- brm(val_cat ~ label_api_text*api_val + (1|ID) + (1|exam_num), family = categorical(), data = df_senti_score_cat)
summary(m_cat_val_text_type_neg_neg_ref)
```
```{r}
df_senti_score_cat$api_val<- as.factor(df_senti_score_cat$api_val)
df_senti_score_cat$api_val <- relevel(df_senti_score_cat$api_val, ref = "NEUTRAL")
df_senti_score_cat$val_cat <- as.factor(df_senti_score_cat$val_cat  )
df_senti_score_cat$val_cat  <- relevel(df_senti_score_cat$val_cat , ref = "NEUTRAL")
m_cat_val_text_type_neu_neu_ref <- brm(val_cat ~ label_api_text*api_val + (1|ID) + (1|exam_num), family = categorical(), data = df_senti_score_cat)
summary(m_cat_val_text_type_neu_neu_ref)a
```
```{r}
#***final model***
df_resp_senti_full <-read.csv("/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/ER/emaData_F24_senti_resp.csv")
df_resp_senti_full$next_valence<- as.factor(df_resp_senti_full$next_valence)
df_resp_senti_full$next_valence <- relevel(df_resp_senti_full$next_valence, ref = "NEGATIVE")
levels(df_resp_senti_full$next_valence)
df_resp_senti_full$api_val_text<- as.factor(df_resp_senti_full$api_val_text)
df_resp_senti_full$api_val_text <- relevel(df_resp_senti_full$api_val_text, ref = "NEGATIVE")
# for multiple responses exam
brm_resp_reg_curr_val_neg_neg_ref <- brm(next_valence ~ reg_ratio*api_val_text + (1+reg_ratio|ID) + (1|exam_num), family = categorical(),
                        data = df_resp_senti_full)
```


```{r}
summary(brm_resp_reg_curr_val_neg_neg_ref)
```
```{r}
summary(brm_resp_reg_curr_val_ref_neu)
```
```{r}
#***final model***
df_resp_senti_full$next_valence <- relevel(df_resp_senti_full$next_valence, ref = "NEUTRAL")
levels(df_resp_senti_full$next_valence)
df_resp_senti_full$api_val_text<- as.factor(df_resp_senti_full$api_val_text)
df_resp_senti_full$api_val_text <- relevel(df_resp_senti_full$api_val_text, ref = "NEUTRAL")
levels(df_resp_senti_full$api_val_text)
# for multiple responses exam
brm_resp_reg_curr_val_neu_neu <- brm(next_valence ~ reg_ratio*api_val_text + (1+reg_ratio|ID) + (1|exam_num), family = categorical(),
                        data = df_resp_senti_full)
summary(brm_resp_reg_curr_val_neu_neu)
```


```{r}
df_senti_score_cat$val_cat <- relevel(df_senti_score_cat$val_cat, ref = "NEGATIVE")
levels(df_senti_score_cat$val_cat)
m_cat_val_text_type_neg_ref <- brm(val_cat ~ label_api_text*api_val + (1|ID) + (1|exam_num), family = categorical(), data = df_senti_score_cat)
summary(m_cat_val_text_type_neg_ref)
```
```{r}
df_resp_senti_full$next_valence <- relevel(df_resp_senti_full$next_valence, ref = "NEUTRAL")
df_resp_senti_full$next_valence <- as.factor(df_resp_senti_full$next_valence)
levels(df_resp_senti_full$next_valence)
df_resp_senti_full$api_val_text <- relevel(df_resp_senti_full$api_val_text, ref = "MIXED")
# for multiple responses exam
brm_resp_reg_curr_val_ref_neu <- brm(next_valence ~ reg_ratio*api_val_text + (1|ID) + (1|exam_num), family = categorical(),
                        data = df_resp_senti_full)
```
```{r}
summary(brm_resp_reg_curr_val_ref_neu)
```

```{r}
# Check levels
levels(df_resp_senti_full$next_valence)
levels(df_resp_senti_full$api_val_text)

# Cross-tabulation
table(
  df_resp_senti_full$api_val_text,
  df_resp_senti_full$next_valence,
  useNA = "ifany"
)
```

```{r}
table(df_resp_senti_full$next_valence)
table(df_resp_senti_full$api_val_text)

with(
  df_resp_senti_full,
  table(api_val_text, next_valence)
)
```


```{r}
levels(df_resp_senti_full$next_valence)
# "NEUTRAL" "NEGATIVE" "MIXED" "POSITIVE"

levels(df_resp_senti_full$api_val_text)
# "MIXED" "NEGATIVE" "NEUTRAL" "POSITIVE"
```

```{r}
summary(brm_resp_reg_curr_val_ref_neu)
```

```{r}
summary(brm_resp_reg_curr_val_ref_neg)
```

```{r}
m_cat_val_text_type_cur_add <- brm(val_cat ~ label_api_text+api_val + (1|ID) + (1|exam_num), family = categorical(), data = df_senti_score_cat)
summary(m_cat_val_text_type_cur_add)
```
```{r}
m_cat_val_text_type_cur_int <- brm(val_cat ~ label_api_text*api_val + (1|ID) + (1|exam_num), family = categorical(), data = df_senti_score_cat)
summary(m_cat_val_text_type_cur_int)
```
```{r}
ce_all <- conditional_effects(
  m_cat_val_text_type_cur,
  conditions = "label_api_text:api_val",
  categorical = TRUE
)

ce_all[[1]]
```
```{r}
ce_all
```

```{r}
m_cat_val_text_type_cur_noref <- brm(val_cat ~ 0+label_api_text*api_val + (1|ID) + (1|exam_num), family = categorical(), data = df_senti_score_cat)
summary(m_cat_val_text_type_cur_noref)
```

#### model comparison
```{r}
model1_phrase <- add_criterion(m_cat_val_text_type_neg_ref, "loo")
model2_phrase <- add_criterion(m_cat_val_text_type_cur_add, "loo")
model3_phrase <- add_criterion(m_cat_val_text_type_cur_int, "loo")

model_comparison <- loo_compare(model1_phrase, model2_phrase,model3_phrase, criterion = "loo")
print(model_comparison, simplify = FALSE)
```

```{r}
m1_sentidelta_label <- lmer(val_score_delta ~ label_api_text + (1|exam_num) + (1|ResponseNumber)+ (1+label_api_text|ID), data = df_senti_score)
summary(m1_sentidelta_label)
```

```{r}
pp_check(m1_sentidelta_label)
```

```{r}
# Only negative sentiment
df_senti_score_neg <- df_senti_score %>% filter (api_val == "NEGATIVE")
```
```{r}
m1_neg_sentidelta_label <- lmer(val_score_delta ~ label_api_text + 0+ (1|exam_num) + (1|ResponseNumber)+ (1+label_api_text|ID), data = df_senti_score_neg)
summary(m1_neg_sentidelta_label)
```
```{r}
pp_check(m1_neg_sentidelta_label)
```
### Phrase-level: next_valence ~ reg*curr_val*GAD_trait
```{r}
df_senti_score_cat_select <- df_senti_score_cat %>% select(ID, exam_num, ResponseNumber, Transcription, text,text_phrase, label_api, label_api_text, word_count, api_val, api_intensity,api_val_num, api_val_score, val_score_delta, val_cat)

df_senti_score_cat_mood <- inner_join(df_senti_score_cat_select, df_mood, by = c("ID"))
```

```{r}
df_senti_score_cat_mood$api_val <- as.factor(df_senti_score_cat_mood$api_val)
df_senti_score_cat_mood$val_cat <- as.factor(df_senti_score_cat_mood$val_cat)
levels(df_senti_score_cat_mood$val_cat)
#m_cat_val_text_type_cur_GAD_score <- lmer(val_cat ~ 0+label_api_text*api_val*GAD_score + (1|ID) + (1|exam_num), data = df_senti_score_cat_mood)
#summary(m_cat_val_text_type_cur_GAD_score)
```
```{r}
m_cat_val_text_type_cur <- brm(
  val_cat ~ label_api_text + api_val+ exam_num +
    (1 | ID),
  family = categorical(),
  data = df_senti_score_cat_mood
)
summary(m_cat_val_text_type_cur)
```


```{r}
m_cat_val_text_type_cur_GAD_score <- brm(
  val_cat ~ label_api_text*api_val*GAD_score +
    (1 | ID) +
    (1 | exam_num),
  family = categorical(),
  data = df_senti_score_cat_mood
)
summary(m_cat_val_text_type_cur_GAD_score)
```
```{r}
ce_all <- brms::conditional_effects(
  m_cat_val_text_type_cur_GAD_score,
  categorical = TRUE
)

names(ce_all)
```


```{r}
library(brms)
library(dplyr)
library(tidyr)
library(ggplot2)

# Low and high GAD: 25th and 75th percentiles
gad_values <- quantile(
  df_senti_score_cat_mood$GAD_score,
  probs = c(.25, .75),
  na.rm = TRUE
)

# All combinations of phrase type, current valence, and GAD level
newdata <- tidyr::expand_grid(
  label_api_text = levels(df_senti_score_cat_mood$label_api_text),
  api_val = levels(df_senti_score_cat_mood$api_val),
  GAD_score = as.numeric(gad_values)
)

newdata$GAD_level <- factor(
  newdata$GAD_score,
  levels = as.numeric(gad_values),
  labels = c("Low GAD", "High GAD")
)

epred <- posterior_epred(
  m_cat_val_text_type_cur_GAD_score,
  newdata = newdata,
  re_formula = NA
)

dim(epred)

outcome_levels <- dimnames(epred)[[3]]

# Fallback if the array does not retain category names
if (is.null(outcome_levels)) {
  outcome_levels <- levels(df_senti_score_cat_mood$val_cat)
}

pred_df <- bind_rows(
  lapply(seq_along(outcome_levels), function(k) {

    data.frame(
      newdata,
      val_cat = outcome_levels[k],
      estimate = apply(epred[, , k], 2, mean),
      lower = apply(epred[, , k], 2, quantile, probs = .025),
      upper = apply(epred[, , k], 2, quantile, probs = .975)
    )
  })
)

ggplot(
  pred_df,
  aes(
    x = label_api_text,
    y = estimate,
    color = api_val,
    group = api_val
  )
) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  facet_grid(val_cat ~ GAD_level) +
  scale_y_continuous(
    limits = c(0, 1),
    labels = scales::percent
  ) +
  labs(
    x = "Phrase type",
    y = "Predicted probability",
    color = "Current valence"
  ) +
  theme_classic(base_size = 14)
```
```{r}
m2_cat_val_text_type_cur_GAD_score <- brm(
  val_cat ~ label_api_text*api_val*GAD_score +
    (1 | ID),
  family = categorical(),
  data = df_senti_score_cat_mood
)
summary(m2_cat_val_text_type_cur_GAD_score)
```
#### Final: valence ~ regulation*GAD
```{r}
m3_cat_val_text_type_cur_GAD_score <- brm(val_cat ~ label_api_text*GAD_score+api_val + exam_num + (1|ID),
                                          family = categorical(),
                                          data = df_senti_score_cat_mood)
summary(m3_cat_val_text_type_cur_GAD_score)
```
```{r}
library(tidyr)

newdata <- expand_grid(
  label_api_text = "Regulation",
  GAD_score = seq(
    min(df_senti_score_cat_mood$GAD_score, na.rm = TRUE),
    max(df_senti_score_cat_mood$GAD_score, na.rm = TRUE),
    length.out = 100
  ),
  api_val = "NEGATIVE",      # or whichever reference level you prefer
  exam_num = median(df_senti_score_cat_mood$exam_num)
)

epred <- posterior_epred(
  m3_cat_val_text_type_cur_GAD_score,
  newdata = newdata,
  re_formula = NA
)

outcomes <- levels(df_senti_score_cat_mood$val_cat)

pred_df <- bind_rows(
  lapply(seq_along(outcomes), function(i){

    data.frame(
      GAD_score = newdata$GAD_score,
      FutureValence = outcomes[i],
      estimate = apply(epred[,,i],2,mean),
      lower = apply(epred[,,i],2,quantile,.025),
      upper = apply(epred[,,i],2,quantile,.975)
    )

  })
)
```
```{r}
dimnames(epred)[[3]]
p_neg <- epred[, , "NEGATIVE"]
p_neg

pred_summary <- data.frame(
  newdata,
  estimate = apply(p_neg, 2, median),
  lower = apply(p_neg, 2, quantile, probs = .025),
  upper = apply(p_neg, 2, quantile, probs = .975)
)

pred_summary
```

```{r}
library(ggplot2)

plot_GAD_later_valence <- ggplot(
  pred_df,
  aes(
    x = GAD_score,
    y = estimate,
    color = FutureValence,
    fill = FutureValence
  )
) +
  geom_line(size = 1.3) +
  geom_ribbon(
    aes(
      ymin = lower,
      ymax = upper
    ),
    alpha = .18,
    colour = NA
  ) +
  scale_color_manual(
    values = c(
      "NEGATIVE" = "#D55E00",
      "NEUTRAL"  = "#666666",
      "POSITIVE" = "#0072B2",
      "MIXED" = "#83c5be"
    )
  ) +
  scale_fill_manual(
    values = c(
      "NEGATIVE" = "#D55E00",
      "NEUTRAL"  = "#666666",
      "POSITIVE" = "#0072B2",
      "MIXED" = "#83c5be"
      
    )
  ) +
  labs(
    #title = "The predicted probability of later valence after regulation vs. GAD",
    x = "GAD score",
    y = "Predicted probability",
    color = "Later valence",
    fill = "Later valence"
  ) +
  theme_classic(base_size = 14)
ggsave(file = "/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/Fig6_valence_GAD.png",plot = plot_GAD_later_valence, width = 6, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/Fig6_valence_GAD.pdf",plot = plot_GAD_later_valence, width = 6, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/Fig6_valence_GAD.eps",plot = plot_GAD_later_valence, width = 6, heigh = 4, dpi = 300)
```

```{r}
ggplot(
  pred_df,
  aes(
    GAD_score,
    estimate,
    color = label_api_text,
    fill = label_api_text
  )
) +
  geom_line(size = 1.2) +
  geom_ribbon(
    aes(ymin = lower, ymax = upper),
    alpha = .15,
    color = NA
  ) +
  facet_wrap(~val_cat) +
  labs(
    y = "Predicted probability",
    x = "GAD score",
    color = "Current phrase",
    fill = "Current phrase"
  ) +
  theme_classic(base_size = 14)
```
```{r}
df_senti_score_cat_mood$val_cat <- relevel(
  factor(df_senti_score_cat_mood$val_cat),
  ref = "NEUTRAL"
)
m4_cat_val_text_type_cur_GAD_score_neuref <- brm(val_cat ~ label_api_text*GAD_score+api_val + exam_num + (1|ID),
                                          family = categorical(),
                                          data = df_senti_score_cat_mood)
summary(m4_cat_val_text_type_cur_GAD_score_neuref)
```
```{r}
library(tidyr)

newdata <- expand_grid(
  label_api_text = levels(df_senti_score_cat_mood$label_api_text),
  GAD_score = seq(
    min(df_senti_score_cat_mood$GAD_score, na.rm = TRUE),
    max(df_senti_score_cat_mood$GAD_score, na.rm = TRUE),
    length.out = 100
  ),
  api_val = "NEGATIVE",      # or whichever reference level you prefer
  exam_num = median(df_senti_score_cat_mood$exam_num)
)

epred <- posterior_epred(
  m4_cat_val_text_type_cur_GAD_score_neuref,
  newdata = newdata,
  re_formula = NA
)

outcomes <- levels(df_senti_score_cat_mood$val_cat)

pred_df <- bind_rows(
  lapply(seq_along(outcomes), function(i){

    cbind(
      newdata,
      val_cat = outcomes[i],
      estimate = apply(epred[,,i],2,mean),
      lower = apply(epred[,,i],2,quantile,.025),
      upper = apply(epred[,,i],2,quantile,.975)
    )

  })
)
```
```{r}
ggplot(
  pred_df,
  aes(
    GAD_score,
    estimate,
    color = label_api_text,
    fill = label_api_text
  )
) +
  geom_line(size = 1.2) +
  geom_ribbon(
    aes(ymin = lower, ymax = upper),
    alpha = .15,
    color = NA
  ) +
  facet_wrap(~val_cat) +
  labs(
    y = "Predicted probability",
    x = "GAD score",
    color = "Current phrase",
    fill = "Current phrase"
  ) +
  theme_classic(base_size = 14)
```
```{r}
df_senti_score_cat_mood$val_cat <- relevel(
  factor(df_senti_score_cat_mood$val_cat),
  ref = "MIXED"
)
m4_cat_val_text_type_cur_GAD_score_mixref <- brm(val_cat ~ label_api_text*GAD_score+api_val + exam_num + (1|ID),
                                          family = categorical(),
                                          data = df_senti_score_cat_mood)
summary(m4_cat_val_text_type_cur_GAD_score_mixref)
```

#### Phrase_leve: valence ~ PE
```{r}
df_senti_score_cat_select_PE <- inner_join(df_senti_score_cat_select, df_PE, by = c("ID","exam_num"))
df_senti_score_cat_select_PE$api_val <- as.factor(df_senti_score_cat_select_PE$api_val)
```
```{r}
m_phrase_val_PE <- brm(
  val_cat ~ EVPE +
    (1 | ID) +
    (1 | exam_num),
  family = categorical(),
  data = df_senti_score_cat_select_PE
)
summary(m_phrase_val_PE)
```
####Plotting
```{r}
library(brms)
library(ggplot2)

ce <- conditional_effects(
  m_phrase_val_PE,
  effects = "EVPE",
  categorical = TRUE
)

plot_df <- ce$EVPE

head(plot_df)
```
```{r}
names(plot_df)
```
```{r}
ggplot(
  plot_df,
  aes(
    x = EVPE,
    y = estimate__,
    color = cats__,
    fill = cats__
  )
) +
  geom_ribbon(
    aes(ymin = lower__, ymax = upper__),
    alpha = 0.15,
    color = NA
  ) +
  geom_line(linewidth = 1.2) +
  labs(
    x = "PE",
    y = "Predicted Probability",
    color = "Phrase Valence",
    fill = "Phrase Valence",
    title = "Effect of PE on Phrase Valence"
  ) +
  theme_classic()
ggsave(file = "/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/Fig3_phrase_valence_PE_titled.pdf", width = 6, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Library/CloudStorage/Box-Box/A_Manetee_lab/Projects/Learning_emotion_regulation/journal_submit/plots/Fig3_phrase_valence_PE_titled.png", width = 6, heigh = 4, dpi = 300)
```

***Two-part modelling***
```{r}
mix <- mixture(gaussian(), gaussian())

brm(
  bf(val_score_delta ~ label_api_text + (1|exam_num)+ (1 | ID)),
  data = df_senti_score,
  family = mix,
  chains = 4, cores = 4
)
```

### collapsed phrase
#### data prep: func to collapse and score blocks

```{r}
df_collapsed_senti_score <- df_senti_full_collapsed
```

```{r}
df_collapsed_senti_score <- df_collapsed_senti_score %>% dplyr::group_by(ID, exam_num) %>% dplyr::mutate(
       val_avg_delta = lead(score_avg) - score_avg,
       val_peak_delta = lead(score_peak) - score_peak,
       val_end_delta = lead(score_end) - score_end,
       ) %>% ungroup()
```

#### model
```{r}
m1_avgdelta_collap_label <- lmer(val_avg_delta ~ text_type + 0+ (1|ResponseNumber)+ (1|exam_num) + (1|ID), data = df_collapsed_senti_score)
summary(m1_avgdelta_collap_label)
```
```{r}
pp_check(m1_avgdelta_collap_label)
```

```{r}
m1_avgdelta_collap_label_nointer <- lmer(val_avg_delta ~ text_type + (1|ResponseNumber)+ (1|exam_num) + (1|ID), data = df_collapsed_senti_score)
summary(m1_avgdelta_collap_label_nointer)
```
```{r}
pp_check(m1_avgdelta_collap_label_nointer)
```


```{r}
m2_peakdelta_collap_label <- lmer(val_peak_delta ~ text_type + (1|ResponseNumber) + (1|exam_num) + (1|ID), data = df_collapsed_senti_score)
summary(m2_peakdelta_collap_label)
```
```{r}
pp_check(m2_peakdelta_collap_label)
```

```{r}
m3_enddelta_collap_label <- lmer(val_end_delta ~ text_type + (1|exam_num) + (1|ID), data = df_collapsed_senti_score)
summary(m3_enddelta_collap_label)
```
##### Pre-post Regulation
***For text block before and after regulation***
```{r}
df_pre_post_collapsed <- df_collapsed_senti_score %>% dplyr::group_by(ID, exam_num, ResponseNumber) %>%
  dplyr::mutate(prev_senti = lag(score_avg),
         post_senti = lead(score_avg),
         prev_peak = lag(score_peak),
         post_peak = lead(score_peak),
         prev_end = lag(score_end),
         post_end = lead(score_end),
         prev_lead = lag(score_lead),
         post_lead = lead(score_lead),
         prev_type = lag(text_type),
         post_type = lead(text_type),
         prev_block_id = lag(block_id),
         post_block_id = lead(block_id),
         pre_block_senti = lag(block_sentiment),
         post_block_senti = lead(block_sentiment)
      ) %>%
  ungroup()

#%>% filter(collapsed_text_type == "Regulation")

df_pre_post_collapsed <- df_pre_post_collapsed %>% dplyr::mutate(
  pre_post_avg = post_senti-prev_senti,
  pre_post_peak = post_peak-prev_peak,
  pre_post_end = post_end-prev_end,
  pre_post_end_lead = post_lead-prev_end)
```

```{r}
m1_pre_post_avg_collapsed_reg <- lmer(pre_post_avg ~ 1 + (1|ID) + (1|exam_num) + (1|ResponseNumber), data = df_pre_post_collapsed)
summary(m1_pre_post_avg_collapsed_reg)
```

```{r}
m2_pre_post_peak_collapsed <- lmer(pre_post_peak ~ 1 + (1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed)
summary(m2_pre_post_peak_collapsed)
```
```{r}
m3_pre_post_end_collapsed <- lmer(pre_post_end ~ 1 + (1|ID) + (1|exam_num)+(1|ResponseNumber), data = df_pre_post_collapsed)
summary(m3_pre_post_end_collapsed)
```
```{r}
sjPlot::sjplot(m3_pre_post_end_collapsed)
```

```{r}
m4_pre_post_avg_senti_collapsed <- lmer(pre_post_avg ~ score_avg + (1|ID) + +(1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed)
summary(m4_pre_post_avg_senti_collapsed)
```

```{r}
m5_pre_post_avg_senti_collapsed_text <- lmer(pre_post_avg ~ 0+text_type + (1|ID) + +(1|exam_num) + (1|ResponseNumber), data = df_pre_post_collapsed)
summary(m5_pre_post_avg_senti_collapsed_text)
```
```{r}
m5_pre_post_peak_senti_collapsed_text <- lmer(pre_post_peak ~ text_type + (1|ID) + +(1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed)
summary(m5_pre_post_peak_senti_collapsed_text)
```

```{r}
m5_pre_post_end_senti_collapsed_text <- lmer(pre_post_end ~ text_type + (1|ID) + +(1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed)
summary(m5_pre_post_end_senti_collapsed_text)
```
```{r}
m5_pre_post_end_lead_senti_collapsed_text <- lmer(pre_post_end_lead ~ text_type + (1|ID) + +(1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed)
summary(m5_pre_post_end_lead_senti_collapsed_text)
```

```{r}
m6_pre_post_avg_senti_collapsed_text_bloksenti <- lmer(pre_post_avg ~ text_type + pre_block_senti +text_type*pre_block_senti + (1|ID) +(1|exam_num) + (1|ResponseNumber), data = df_pre_post_collapsed)
summary(m6_pre_post_avg_senti_collapsed_text_bloksenti)
```

#### valence check after regulation
```{r}
df_pre_post_collapsed_reg_senti <- df_pre_post_collapsed %>% filter(
  pre_block_senti == "POSITIVE",
  text_type == "Regulation")
```
```{r}
df_counts_post <- df_pre_post_collapsed_reg_senti %>%
  dplyr::count(post_block_senti)

df_counts_current <- df_pre_post_collapsed_reg_senti %>%
  dplyr::count(block_sentiment)
```

```{r}
ggplot(df_counts_post, aes(x = post_block_senti, y = n, fill = post_block_senti)) +
  geom_bar(stat = "identity", width = 0.6) +
  labs(
    title = "Proportion of Sentiment After Regulation\n(Previous = Positive)",
    x = "Post-Regulation Block Sentiment",
    y = "Proportion"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```


```{r}
ggplot(df_counts_current, aes(x = block_sentiment, y = n, fill = block_sentiment)) +
  geom_bar(stat = "identity", width = 0.6) +
  labs(
    title = "Proportion of Sentiment After Regulation\n(Previous = Positive)",
    x = "Regulation Block Sentiment",
    y = "Proportion"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```
If the number of Positive-negative/positive-neutral transition correlated with GAD and reg ratio.

```{r}
df_pre_post_collapsed_nei_senti <- df_pre_post_collapsed %>% filter(
  pre_block_senti == "POSITIVE",
  text_type == "Neither")
```

```{r}
df_counts_post <- df_pre_post_collapsed_nei_senti %>%
  dplyr::count(post_block_senti)

df_counts_current <- df_pre_post_collapsed_nei_senti %>%
  dplyr::count(block_sentiment)
```

```{r}
ggplot(df_counts_post, aes(x = post_block_senti, y = n, fill = post_block_senti)) +
  geom_bar(stat = "identity", width = 0.6) +
  labs(
    title = "Proportion of Sentiment After Neither \n(Previous = Positive)",
    x = "Post-Neither Block Sentiment",
    y = "Proportion"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

```{r}
ggplot(df_counts_current, aes(x = block_sentiment, y = n, fill = block_sentiment)) +
  geom_bar(stat = "identity", width = 0.6) +
  labs(
    title = "Proportion of Sentiment After Neither\n(Previous = Positive)",
    x = "Neither Block Sentiment",
    y = "Proportion"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```
```{r}
df_pre_post_collapsed_exp_senti <- df_pre_post_collapsed %>% filter(
  pre_block_senti == "POSITIVE",
  text_type == "Expression")
```

```{r}
df_counts_post <- df_pre_post_collapsed_exp_senti %>%
  dplyr::count(post_block_senti)

df_counts_current <- df_pre_post_collapsed_exp_senti %>%
  dplyr::count(block_sentiment)
```

```{r}
ggplot(df_counts_post, aes(x = post_block_senti, y = n, fill = post_block_senti)) +
  geom_bar(stat = "identity", width = 0.6) +
  labs(
    title = "Proportion of Sentiment After Expression \n(Previous = Positive)",
    x = "Post-Expression Block Sentiment",
    y = "Proportion"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```
```{r}
ggplot(df_counts_current, aes(x = block_sentiment, y = n, fill = block_sentiment)) +
  geom_bar(stat = "identity", width = 0.6) +
  labs(
    title = "Proportion of Sentiment After Expression\n(Previous = Positive)",
    x = "Expression Block Sentiment",
    y = "Proportion"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```
##### Pre-post Expression
***For block before and after expression***
```{r}
df_pre_post_collapsed_exp <- df_collapsed_senti_score %>% dplyr::group_by(ResponseNumber) %>%
  mutate(prev_senti = lag(score_avg),
         post_senti = lead(score_avg),
         prev_peak = lag(score_peak),
         post_peak = lead(score_peak),
         prev_end = lag(score_end),
         post_end = lead(score_end),
         prev_type = lag(collapsed_text_type),
         post_type = lead(collapsed_text_type),
         prev_block_id = lag(block_id),
         post_block_id = lead(collapsed_text_type)
      ) %>%
  ungroup %>% filter(collapsed_text_type == "Expression")

df_pre_post_collapsed_exp <- df_pre_post_collapsed_exp %>% mutate(
  pre_post_exp_avg = post_senti-prev_senti,
  pre_post_exp_peak = post_peak-prev_peak,
  pre_post_exp_end = post_end-prev_end)
```

```{r}
m1_pre_post_avg_collapsed_exp <- lmer(pre_post_exp_avg ~ 1 + (1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed_exp)
summary(m1_pre_post_avg_collapsed_exp)
```

```{r}
m2_pre_post_peak_collapsed_exp <- lmer(pre_post_exp_peak ~ 1 + (1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed_exp)
summary(m2_pre_post_peak_collapsed_exp)
```
```{r}
m3_pre_post_end_collapsed_exp <- lmer(pre_post_exp_end ~ 1 + (1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed_exp)
summary(m3_pre_post_end_collapsed_exp)
```
##### Pre-post Neither
***For block before and after neither***
```{r}
df_pre_post_collapsed_nei <- df_collapsed_senti_score %>% group_by(ResponseNumber) %>%
  mutate(prev_senti = lag(score_avg),
         post_senti = lead(score_avg),
         prev_peak = lag(score_peak),
         post_peak = lead(score_peak),
         prev_end = lag(score_end),
         post_end = lead(score_end),
         prev_type = lag(collapsed_text_type),
         post_type = lead(collapsed_text_type),
         prev_block_id = lag(block_id),
         post_block_id = lead(collapsed_text_type)
      ) %>%
  ungroup %>% filter(collapsed_text_type == "Neither")

df_pre_post_collapsed_nei <- df_pre_post_collapsed_nei %>% mutate(
  pre_post_nei_avg = post_senti-prev_senti,
  pre_post_nei_peak = post_peak-prev_peak,
  pre_post_nei_end = post_end-prev_end)
```

```{r}
m1_pre_post_avg_collapsed_nei <- lmer(pre_post_nei_avg ~ 1 + (1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed_nei)
summary(m1_pre_post_avg_collapsed_nei)
```

```{r}
m2_pre_post_peak_collapsed_nei <- lmer(pre_post_nei_peak ~ 1 + (1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed_nei)
summary(m2_pre_post_peak_collapsed_nei)
```

```{r}
m3_pre_post_end_collapsed_nei <- lmer(pre_post_nei_end ~ 1 + (1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed_nei)
summary(m3_pre_post_end_collapsed_nei)
```
***A full model for pre-post score***
```{r}
df_pre_post_collapsed_all <- df_collapsed_senti_score %>% dplyr::group_by(ResponseNumber) %>%
  mutate(prev_senti = lag(score_avg),
         post_senti = lead(score_avg),
         prev_type = lag(collapsed_text_type),
         post_type = lead(collapsed_text_type),
         prev_block_id = lag(block_id),
         post_block_id = lead(collapsed_text_type)
      ) %>%
  ungroup 

df_pre_post_collapsed_all <- df_pre_post_collapsed_all %>% dplyr::mutate(pre_post_avg = post_senti-prev_senti)
```
```{r}
m1_pre_post_collapsed_all <- lmer(pre_post_avg ~ collapsed_text_type + (1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed_all)
summary(m1_pre_post_collapsed_all)
```
#####Plotting
```{r}
library(broom.mixed)

coef_pre_post_collapsed_all <- broom.mixed::tidy(m1_pre_post_collapsed_all, effects = "fixed")
coef_pre_post_collapsed_all
```
```{r}
coef_pre_post_collapsed_all <- coef_pre_post_collapsed_all %>%
  mutate(term = recode(term,
                       '(Intercept)' = "Expression",
                       collapsed_text_typeNeither = "Neither",
                       collapsed_text_typeRegulation = "Regulation"))
```
```{r}
library(wesanderson)
# color selection
library(RColorBrewer)

# check palette
display.brewer.pal(8, "Set2")  # shows the 8 colors in "Set2"

# select specific colors (e.g., 2nd, 4th, and 6th)
my_colors <- brewer.pal(8, "Set2")[c(2, 3, 1)]
```


```{r}
pre_post_text_all_response_plot <- ggplot(coef_pre_post_collapsed_all, aes(x = term, y = estimate, fill = term)) +
  geom_col(width = 0.6, color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error),
                width = 0.2) +
  scale_fill_manual(values = my_colors) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
  labs(
    title = "Effect of Text Type on Sentiment Change (within response)",
    x = "Text Type",
    y = "Change in sentiment score"
  ) +
  theme_classic()
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/pre_post_text_all_response.png",plot = pre_post_text_all_response_plot, width = 6, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/pre_post_text_all_response.pdf",plot = pre_post_text_all_response_plot, width = 6, heigh = 4, dpi = 300)
pre_post_text_all_response_plot
```

#### Last phrase - First phrase
```{r}
# collapsed the df; calculate the dealta score between phrases.
library(dplyr)

collapse_text_blocks_with_delta <- function(label_api_text, sentiment, intensity, exam_num = NULL) {
  # Collapse repeated labels
  r <- rle(label_api_text)
  block_id <- rep(seq_along(r$lengths), r$lengths)

  # Build phrase-level dataframe
  phrase_df <- tibble(
    label_api_text = label_api_text,
    sentiment = sentiment,
    intensity = intensity,
    block_id = block_id
  )

  if (!is.null(exam_num)) {
    phrase_df$exam_num <- exam_num
  }

  # Block-level summary
  block_summary <- phrase_df %>%
    group_by(block_id) %>%
    summarise(
      collapsed_text_type = first(label_api_text),
      length = n(),
      score_sum = sum(sentiment * intensity),
      score_avg = mean(sentiment * intensity),
      score_peak = max(abs(sentiment * intensity)),
      score_end = last(sentiment * intensity),
      score_start = first(sentiment * intensity),
      exam_num = if (!is.null(exam_num)) first(exam_num) else NA,
      .groups = "drop"
    ) %>%
    mutate(
      block_sentiment = case_when(
        score_sum > 0 ~ "POSITIVE",
        score_sum < 0 ~ "NEGATIVE",
        TRUE ~ "NEUTRAL"
      ),
      delta_next_block = lead(score_start) - score_end
    )

  return(block_summary)
}


```
```{r}
df_delta_blocks <- df_senti_full %>%
  dplyr::group_by(ID, ResponseNumber) %>%
  group_modify(~ collapse_text_blocks_with_delta(
    label_api_text = .x$label_api_text,
    sentiment = .x$api_val_num,
    intensity = .x$api_intensity,
    exam_num = .x$exam_num)) %>%
  ungroup()
```

```{r}
m1_last_first_phrase_delta <- lmer(delta_next_block ~ collapsed_text_type + 0 + (1|ID)+(1|ResponseNumber)+(1|exam_num), data = df_delta_blocks)

summary(m1_last_first_phrase_delta)
```
##### exam average
```{r}
m2_last_first_phrase_delta <- lmer(delta_next_block ~ score_avg + (1|ID) + (1|ResponseNumber), data = df_delta_blocks)
summary(m2_last_first_phrase_delta)
```
##### reg and exam_num
```{r}
df_delta_blocks_reg <- df_delta_blocks %>% filter(collapsed_text_type=="Regulation")
m3_last_first_phrase_delta_exam <- lmer(delta_next_block ~ exam_num + (1|ID) + (1|ResponseNumber), data = df_delta_blocks_reg)
summary(m3_last_first_phrase_delta_exam)
```

***For negative sentiment***
Low ratio of regulation; not consecutive
```{r}
m1_avgdelta_neg_collap_label <- lmer(val_avg_delta ~ collapsed_text_type + (1|ResponseNumber)+ (1|exam_num) + (1|ID), data = df_collapsed_neg_senti_score)
summary(m1_avgdelta_neg_collap_label)
```

#### Pre-post score vs. lead(ratio)
#### TBD
```{r}
df_label_ratio_wide$exam_num <- as.factor(df_label_ratio_wide$exam_num)
df_label_ratio_wide <- df_label_ratio_wide %>% relocate(exam_num, .after = ID)
df_label_ratio_wide_per_exam <- df_label_ratio_wide %>% group_by(ID, exam_num) %>%
  arrange(ID, exam_num) %>% 
  summarise(exp_exam_avg = mean(Expression),
    reg_exam_avg = mean(Regulation),
    nei_exam_avg = mean(Neither),
    .groups = 'drop')
#Note: the df is not correctly group by ID and exam_num?? exam4 should have NA as lead score
df_label_ratio_wide_per_exam <- df_label_ratio_wide_per_exam %>%
  group_by(ID) %>%
  arrange(exam_num, .by_group = TRUE) %>%
  mutate(
    is_last = (row_number() == n()),  # TRUE for last row in each group
    lead_exp = ifelse(is_last, NA, lead(exp_exam_avg)),
    lead_reg = ifelse(is_last, NA, lead(reg_exam_avg)),
    lead_nei = ifelse(is_last, NA, lead(nei_exam_avg))
  ) %>%
  select(-is_last) %>%
  ungroup()
df_pre_post_collapsed_ratio <- inner_join(df_pre_post_collapsed_all, df_label_ratio_wide_per_exam, by = c("ID", "exam_num", "ResponseNumber"))
```

```{r}
m1_pre_post_avg_lead_reg_ratio <- lmer(lead_reg ~ pre_post_avg +0+ (1|ID), data = df_pre_post_collapsed_ratio)
summary(m1_pre_post_avg_lead_reg_ratio)

pp_check(m1_pre_post_avg_lead_reg_ratio)
```

```{r}
m1_pre_post_avg_lead_exp_ratio <- lmer(lead_exp ~ pre_post_avg + (1|ID), data = df_pre_post_collapsed_ratio)
summary(m1_pre_post_avg_lead_exp_ratio)

#pp_check(m1_pre_post_avg_lead_reg_ratio)
```
### Response
#### data prep
```{r}
df_response_senti_calculate <- df_senti_full %>% group_by(ID, exam_num, ResponseNumber) %>%
  summarise(
      score_sum = sum(api_val_num * api_intensity),
      score_avg = mean(api_val_num * api_intensity),
      score_peak = max(abs(api_val_num * api_intensity)),
      score_end = last(api_val_num * api_intensity)) %>%
        mutate(
      response_sentiment = case_when(
        score_avg > 0 ~ "POSITIVE",
        score_avg < 0 ~ "NEGATIVE",
        TRUE ~ "NEUTRAL"
      )
    ) 
```
```{r}
# Calculate the ratio of each text_type
df_label_ratio <- df_senti_full %>%
  group_by(ID, exam_num, ResponseNumber, label_api_text) %>%
  summarise(n = n(), .groups = "drop") %>%
  complete(
    label_api_text = unique(df_senti_full$label_api_text),
    fill = list(n = 0)
  ) %>%
  group_by(ID, exam_num, ResponseNumber) %>%
  mutate(ratio = n / sum(n)) %>%
  ungroup()

df_label_ratio_wide <- df_label_ratio %>%
  select(ID, exam_num, ResponseNumber, label_api_text, ratio) %>%
  pivot_wider(names_from = label_api_text, values_from = ratio, values_fill = 0)
```
```{r}
df_response_senti_calculate <- df_response_senti_calculate %>% group_by(ID, exam_num, ResponseNumber) %>% mutate(val_avg_delta = lead(score_avg) - score_avg,
       val_peak_delta = lead(score_peak) - score_peak,
       val_end_delta = lead(score_end) - score_end) %>% ungroup()

df_response_senti_score <- inner_join(df_label_ratio_wide, df_response_senti_calculate, by = c("ID", "exam_num", "ResponseNumber"))

# Calculate the delta score
df_response_senti_score <- df_response_senti_score %>% group_by(ID, exam_num, ResponseNumber) %>% mutate(val_avg_delta = lead(score_avg) - score_avg,
       val_peak_delta = lead(score_peak) - score_peak,
       val_end_delta = lead(score_end) - score_end) %>% ungroup()
```
#### Model
##### sentiment score vs. label ratio within response
```{r}
m1_avgdelta_resp_label <- lmer(val_avg_delta ~ Expression + Regulation + Neither + (1|exam_num) + (1|ID), data = df_response_senti_score)
summary(m1_avgdelta_resp_label)
```
```{r}
pp_check(m1_avgdelta_resp_label)
```

```{r}
m2_peakdelta_resp_label <- lmer(val_peak_delta ~ Expression + Regulation + Neither + (1|exam_num) + (1|ID), data = df_response_senti_score)
summary(m2_peakdelta_resp_label)
```
```{r}
m3_enddelta_resp_label <- lmer(val_end_delta ~ Expression + Regulation + Neither + (1|exam_num) + (1|ID), data = df_response_senti_score)
summary(m3_enddelta_resp_label)
```
```{r}
pp_check(m1_sentidelta_label)
```

#### label ratio
```{r}
# Load in response senti
df_response <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/emaData_F24_resp_sentiment_v5.csv")

df_response <- df_response[,-c(13,14)]

for (i in (1:nrow(df_senti_full))){
  phrase = df_senti_full$text_phrase[i]
  df_senti_full$word_count[i] <- str_count(phrase,'[\\w\']+')
}

df_resp_senti <- df_senti_full
```
## response-level sentiment.
```{r}
df_response <- df_response %>% mutate(api_val_text = (case_when(valence == 1.0 ~"POSITIVE",
                                                               valence == 0.5 ~ "MIXED",
                                                               valence == -0.5 ~ "MIXED",
                                                               valence == 0 ~ "NEUTRAL",
                                                               valence == -1 ~ "NEGATIVE")))
```

```{r}
# calculate regulation ratio of each response
df_resp_word_sum_tmp <- df_resp_senti %>% group_by(ID, exam_num, ResponseNumber, label_api_text) %>% summarise(sum_word_count = sum(word_count), .groups = "drop")
```

```{r}
df_resp_senti <- df_resp_senti %>%
  dplyr::group_by(ID, exam_num, ResponseNumber) %>%
  dplyr::mutate(
    total_words = sum(word_count, na.rm = TRUE)
  )
```

```{r}
df_resp_senti <- df_resp_senti %>% dplyr::group_by (ID, exam_num, ResponseNumber,  time_since_grade_reveal_mins) %>% summarise (exp_count = sum(label_api_text == "Expression"),
    reg_count = sum(label_api_text == "Regulation"),
    nei_count = sum(label_api_text == "Neither"),
    exp_word_count = sum(word_count[label_api_text == "Expression"]),
    # Sum word_count ONLY for phrases with 'regulation' label
    reg_word_count = sum(word_count[label_api_text == "Regulation"]),
    # Sum word_count ONLY for phrases with 'neither' label
    nei_word_count = sum(word_count[label_api_text == "Neither"]),
    total_phrases = n(), 
    total_words   = sum(word_count, na.rm = TRUE),
    .groups = 'drop' # This tells dplyr to remove the grouping structure after summarise
  ) %>%
  dplyr::mutate(
    # Calculate ratios
    exp_word_ratio = exp_word_count / total_words,
    reg_word_ratio = reg_word_count / total_words,
    nei_word_ratio = nei_word_count / total_words,
    exp_ratio = exp_count / total_phrases,
    reg_ratio = reg_count / total_phrases,
    nei_ratio = nei_count / total_phrases
  )

# attach sentiment and response ratio
df_resp_senti$ID <- as.integer(df_resp_senti$ID)
df_resp_senti$exam_num <- as.integer(df_resp_senti$exam_num)
df_resp_senti$ResponseNumber <- as.integer(df_resp_senti$ResponseNumber)
df_resp_senti_full <- inner_join(df_resp_senti, df_response, by = c("ID","exam_num","ResponseNumber"))

df_resp_senti_full_PE <- inner_join(df_resp_senti_full, df_PE, by = c("ID","exam_num"))

df_resp_senti_full_PE_mood <- inner_join(df_resp_senti_full_PE, df_mood, by = "ID")
```
# how regulation ratio influence next response valence
```{r}
# Focus on df_resp_senti_full for now
df_resp_senti_full <- df_resp_senti_full %>% dplyr::group_by (ID, exam_num) %>% dplyr::mutate(next_valence = lead(api_val_text))

df_resp_senti_full$next_valence <- as.factor(df_resp_senti_full$next_valence)
df_resp_senti_full$api_val_text <- as.factor(df_resp_senti_full$api_val_text)
```
```{r}
write.csv(df_resp_senti_full, "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/ER/emaData_F24_senti_resp.csv", row.names = FALSE)
```

```{r}
df_resp_senti_full$next_valence <- relevel(df_resp_senti_full$next_valence, ref = "NEGATIVE")
# for multiple responses exam
brm_resp_reg_val <- brm(next_valence ~ reg_ratio + (1+reg_ratio|ID) + (1|exam_num), family = categorical(),
                        data = df_resp_senti_full)
```
```{r}
summary(brm_resp_reg_val)
```
```{r}
ce <- conditional_effects(
  brm_resp_reg_val,
  effects = "reg_ratio",
  categorical = TRUE
)

plot_df <- ce$reg_ratio
head(plot_df)
table(plot_df$cats__)
```
```{r}
ggplot(plot_df, aes(x = reg_ratio, y = estimate__, color = cats__, fill = cats__)) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.15, color = NA) +
  labs(
    title = "Predicted Probability of Next Valence by Regulation Ratio",
    x = "Regulation Ratio",
    y = "Predicted Probability",
    color = "Next valence",
    fill = "Next valence"
  ) +
  theme_classic()
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/next_senti_reg_word_ratio.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/next_senti_reg_word_ratio.pdf",height=4, width=6, dpi=300)
```
```{r}
plot_df_filtered <- plot_df %>%
  dplyr::filter(cats__ %in% c("NEUTRAL", "MIXED"))

ggplot(plot_df_filtered,
       aes(x = reg_ratio, y = estimate__,
           color = cats__, fill = cats__)) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__),
              alpha = 0.2, color = NA) +
  labs(
    title = "Predicted Probability of Next Valence by Regulation Proportion",
    x = "Regulation Proportion",
    y = "Predicted Probability",
    color = "Following valence",
    fill = "Following valence"
  ) +
  scale_color_manual(values = c(
  "MIXED"    = "#7CAE00",
  "NEUTRAL"  = "#00BFC4"
)) +
scale_fill_manual(values = c(
  "MIXED"    = "#7CAE00",
  "NEUTRAL"  = "#00BFC4"
)) +
  ylim(0,0.7) +
  theme_classic()
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/next_senti_reg_word_ratio_mix_neu.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/next_senti_reg_word_ratio_mix_neu.pdf",height=4, width=6, dpi=300)
```
```{r}
plot_df_filtered <- plot_df %>%
  dplyr::filter(cats__ %in% c("POSITIVE", "NEGATIVE"))

ggplot(plot_df_filtered,
       aes(x = reg_ratio, y = estimate__,
           color = cats__, fill = cats__)) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__),
              alpha = 0.2, color = NA) +
  labs(
    title = "Predicted Probability of Next Valence by Regulation Proportion",
    x = "Regulation Proportion",
    y = "Predicted Probability",
    color = "Following valence",
    fill = "Following valence"
  ) +
  scale_color_manual(values = c(
  "NEGATIVE" = "#F8766D",
  "POSITIVE" = "#C77CFF"
)) +
scale_fill_manual(values = c(
  "NEGATIVE" = "#F8766D",
  "POSITIVE" = "#C77CFF"
)) +
  ylim(0, 0.7)+
  theme_classic()
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/next_senti_reg_word_ratio_pos_neg.png",height=4, width=6, dpi=300)
ggsave("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/API_v5_fullset/next_senti_reg_word_ratio_pos_neg.pdf",height=4, width=6, dpi=300)
```
```{r}
df_resp_senti_full_neg <- df_resp_senti_full %>% filter(api_val_text == "NEGATIVE")
# for multiple responses exam
brm_resp_reg_val_neg <- brm(next_valence ~ reg_ratio + (1+reg_ratio|ID) + (1|exam_num), family = categorical(),
                        data = df_resp_senti_full)
```
```{r}
summary(brm_resp_reg_val_neg)
```
```{r}
ce_neg <- conditional_effects(
  brm_resp_reg_val_neg,
  effects = "reg_ratio",
  categorical = TRUE
)

plot(ce_neg)
```

```{r}
pp_check(brm_resp_reg_val)
```
####***final model***
```{r}
#***final model***
df_resp_senti_full$api_val_text <- relevel(df_resp_senti_full$api_val_text, ref = "NEGATIVE")
df_resp_senti_full$api_val_text <- as.factor(df_resp_senti_full$api_val_text)
# for multiple responses exam
brm_resp_reg_curr_val <- brm(next_valence ~ reg_ratio*api_val_text + (1+reg_ratio|ID) + (1|exam_num), family = categorical(),
                        data = df_resp_senti_full)
```
```{r}
summary(brm_resp_reg_curr_val)
```
```{r}
conditional_effects(brm_resp_reg_curr_val,
                    effects = "reg_ratio:api_val_text",
                    categorical = TRUE)
```
```{r}
brm_resp_reg_curr_val_noref <- brm(next_valence ~ 0+reg_ratio*api_val_text + (1+reg_ratio|ID) + (1|exam_num), family = categorical(),
                        data = df_resp_senti_full)
```
```{r}
summary(brm_resp_reg_curr_val_noref)
```
```{r}
nobs(m_cat_val_text_type)
nobs(m_cat_val_text_type_cur)

m_cat_val_text_type$formula
m_cat_val_text_type_cur$formula

identical(
  model.frame(m_cat_val_text_type)$val_cat,
  model.frame(m_cat_val_text_type_cur)$val_cat
)
```
```{r}
table(model.frame(m_cat_val_text_type)$val_cat)

table(model.frame(m_cat_val_text_type_cur)$val_cat)
```
```{r}
levels(model.frame(m_cat_val_text_type)$val_cat)

levels(model.frame(m_cat_val_text_type_cur)$val_cat)
```

#### model_comparison
```{r}
modelval_phrase <- add_criterion(brm_resp_reg_val, "loo")
modelcurr_phrase <- add_criterion(brm_resp_reg_curr_val, "loo")

model_comparison_resp <- loo_compare(modelval_phrase, modelcurr_phrase, criterion = "loo")
print(model_comparison_resp, simplify = FALSE)
```

#### next_valence~ reg_ratio*api_val_text*GAD_score
```{r}
df_resp_senti_full_mood <- inner_join(df_resp_senti_full, df_mood, by = "ID")
```

```{r}
brm_resp_reg_curr_val_gad <- brm(next_valence ~ reg_ratio*api_val_text*GAD_score + (1+reg_ratio|ID) + (1|exam_num), family = categorical(),
                        data = df_resp_senti_full_mood)

```

```{r}
summary(brm_resp_reg_curr_val_gad)
```
```{r}
gad_mean <- mean(df_resp_senti_full_mood$GAD_score, na.rm = TRUE)
gad_sd   <- sd(df_resp_senti_full_mood$GAD_score, na.rm = TRUE)

gad_vals <- c(gad_mean - gad_sd,
              gad_mean + gad_sd)


```
```{r}
newdat <- expand.grid(
  reg_ratio = seq(min(df_resp_senti_full_mood$reg_ratio),
                  max(df_resp_senti_full_mood$reg_ratio),
                  length.out = 100),
  api_val_text = levels(df_resp_senti_full_mood$api_val_text),
  GAD_score = gad_vals
)

pred <- fitted(brm_resp_reg_curr_val_gad,
               newdata = newdat,
               re_formula = NA,
               summary = TRUE)

library(dplyr)
library(tidyr)

pred_df <- cbind(newdat, as.data.frame(pred))

pred_long <- pred_df %>%
  pivot_longer(
    cols = starts_with("Estimate"),
    names_to = "next_valence",
    values_to = "prob"
  )
```

```{r}
library(ggplot2)

ggplot(pred_long,
       aes(x = reg_ratio,
           y = prob,
           color = next_valence,
           linetype = factor(GAD_score))) +
  geom_line(size = 1.1) +
  facet_wrap(~ api_val_text) +
  labs(
    y = "Predicted Probability of Next Valence",
    x = "Regulation Ratio (Current)",
    linetype = "GAD Level"
  ) +
  theme_minimal()
```

```{r}
brm_resp_reg_word_curr_val_gad <- brm(next_valence ~ reg_word_ratio*api_val_text*GAD_score + (1+reg_ratio|ID) + (1|exam_num), family = categorical(),
                        data = df_resp_senti_full_mood)

```
```{r}
summary(brm_resp_reg_word_curr_val_gad)
```


```{r}
df_resp_senti_full <- df_resp_senti_full %>% dplyr::group_by(ID, exam_num) %>% dplyr::mutate(pre_valence = lag(api_val_text))
```

```{r}
# for multiple responses exam
brm_resp_reg_pre_post_val <- brm(next_valence ~ reg_ratio*pre_valence + (1+reg_ratio|ID) + (1|exam_num), family = categorical(),
                        data = df_resp_senti_full)
```
```{r}
summary(brm_resp_reg_pre_post_val)
```

### Response-level sentiment with sd score
#### response sentiment + sd
```{r}
df_resp_sd <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/emaData_F24_sentiment_resp_sd_full.csv")

df_resp_sd <- df_resp_sd %>% dplyr::group_by (ID, exam_num) %>% dplyr::mutate(
  next_senti = lead(sentiment),
  next_sd = lead(sd))
```
```{r}
df_resp_senti_sd_full <- inner_join(df_resp_senti, df_resp_sd, by = c("ID","exam_num","ResponseNumber"))

df_resp_senti_sd_full_PE <- inner_join(df_resp_senti_sd_full, df_PE, by = c("ID","exam_num"))

df_resp_senti_sd_full_PE_mood <- inner_join(df_resp_senti_sd_full_PE, df_mood, by = "ID")
```
##### 
```{r}
brm_resp_reg_senti_EVPE <- brm(next_senti ~ reg_ratio + EVPE + (1+reg_ratio|ID) + (1|exam_num), data = df_resp_senti_sd_full_PE)
```
```{r}
summary(brm_resp_reg_senti_EVPE)
```
```{r}
pp_check(brm_resp_reg_senti_EVPE)
```
##### senti+sd model
```{r}
brm_resp_reg_senti_sd_EVPE <- brm(next_senti | se(next_sd, sigma = TRUE) ~ EVPE * reg_ratio +(1 + EVPE | ID) +(1 | exam_num),family = gaussian(),data = df_resp_senti_sd_full_PE,chains = 4,cores = 4
)
```
```{r}
summary(brm_resp_reg_senti_sd_EVPE)
```
```{r}
pp_check(brm_resp_reg_senti_sd_EVPE)
```

```{r}
brm_resp_reg_word_senti_sd_EVPE <- brm(next_senti | se(next_sd, sigma = TRUE) ~ EVPE * reg_word_ratio +(1 + EVPE | ID) +(1 | exam_num),family = gaussian(),data = df_resp_senti_sd_full_PE,chains = 4,cores = 4
)

summary(brm_resp_reg_word_senti_sd_EVPE)
```
```{r}
plot(conditional_effects(brm_resp_reg_word_senti_sd_EVPE, effects = "EVPE:reg_word_ratio"))
```
```{r}
library(dplyr)
library(tidyr)
library(tidybayes)
library(ggplot2)

reg_vals <- quantile(
  df_resp_senti_sd_full_PE$reg_word_ratio,
  probs = c(.25, .75),
  na.rm = TRUE
)

newdat <- expand_grid(
  EVPE = seq(
    min(df_resp_senti_sd_full_PE$EVPE, na.rm = TRUE),
    max(df_resp_senti_sd_full_PE$EVPE, na.rm = TRUE),
    length.out = 100
  ),
  reg_word_ratio = quantile(
    df_resp_senti_sd_full_PE$reg_word_ratio,
    probs = c(.25, .75),
    na.rm = TRUE
  )
) |>
  mutate(
    next_sd = mean(df_resp_senti_sd_full_PE$next_sd, na.rm = TRUE),
    reg_level = factor(
      reg_word_ratio,
      levels = reg_vals,
      labels = c("Low regulation", "High regulation")
    )
  )
```

```{r}
pred <- add_epred_draws(
  brm_resp_reg_word_senti_sd_EVPE,
  newdata = newdat,
  re_formula = NA
)
```
```{r}
ggplot(pred, aes(x = EVPE, y = .epred, color = reg_level, fill = reg_level)) +
  stat_lineribbon(.width = 0.95, alpha = 0.25) +
  labs(
    x = "EVPE",
    y = "Predicted next sentiment",
    color = "Regulation ratio",
    fill = "Regulation ratio"
  ) +
  theme_classic()
```

```{r}
brm_resp_reg_word_cur_senti_sd_EVPE <- brm(next_senti | se(next_sd, sigma = TRUE) ~ sentiment*EVPE * reg_word_ratio + sd +(1 + EVPE | ID) +(1 | exam_num),family = gaussian(),data = df_resp_senti_sd_full_PE,chains = 4,cores = 4)

summary(brm_resp_reg_word_cur_senti_sd_EVPE)
```

```{r}
brm_resp_reg_word_cur_senti <- brm(next_senti | se(next_sd, sigma = TRUE) ~ sentiment * reg_word_ratio + time_since_grade_reveal_mins.y + (1 | ID) +(1 | exam_num),family = gaussian(),data = df_resp_senti_sd_full_PE,chains = 4,cores = 4)

summary(brm_resp_reg_word_cur_senti)
```
```{r}
pp_check(brm_resp_reg_word_cur_senti)
```

```{r}
rand_resp_reg_word_cur_senti <- brm(next_senti | se(next_sd, sigma = TRUE) ~ sentiment * reg_word_ratio + (1 + sentiment * reg_word_ratio | ID) +(1 | exam_num),family = gaussian(), data = df_resp_senti_sd_full_PE,chains = 4,cores = 4)

summary(rand_resp_reg_word_cur_senti)
```

##next_senti ~ Sentiment

```{r}
resp_next_senti_cur_senti <- brm(next_senti | se(next_sd, sigma = TRUE) ~ sentiment  + (1 + sentiment| ID) +(1 | exam_num),family = gaussian(), data = df_resp_senti_sd_full_PE,chains = 4,cores = 4)

summary(resp_next_senti_cur_senti)
```
```{r}
resp_next_senti_cur_reg_senti <- brm(next_senti | se(next_sd, sigma = TRUE) ~ sentiment + reg_word_ratio  + (1 + sentiment| ID) +(1 | exam_num),family = gaussian(), data = df_resp_senti_sd_full_PE,chains = 4,cores = 4)

summary(resp_next_senti_cur_reg_senti)
```
```{r}
resp_next_senti_cur_senti_reg_inx <- brm(next_senti | se(next_sd, sigma = TRUE) ~ sentiment * reg_word_ratio  + (1 + sentiment| ID) +(1 | exam_num),family = gaussian(), data = df_resp_senti_sd_full_PE,chains = 4,cores = 4)

summary(resp_next_senti_cur_senti_reg_inx)
```
```{r}
resp_next_senti_cur_senti_EVPE <- brm(next_senti | se(next_sd, sigma = TRUE) ~ sentiment + EVPE + (1 + sentiment| ID) +(1 | exam_num),family = gaussian(), data = df_resp_senti_sd_full_PE,chains = 4,cores = 4)

summary(resp_next_senti_cur_senti_EVPE)
```


```{r}
re_cur_senti <- ranef(rand_resp_reg_word_cur_senti)$ID
```
```{r}
interaction_slope <- re_cur_senti[, "Estimate", "sentiment:reg_word_ratio"]

interaction_df <- data.frame(
  ID = rownames(re_cur_senti),
  interaction_est = interaction_slope
)
```
```{r}
df_corr <- merge(interaction_df, df_mood, by = "ID")
cor.test(df_corr$interaction_est, df_corr$GAD_score)
cor.test(df_corr$interaction_est, df_corr$ERQ_score)
cor.test(df_corr$interaction_est, df_corr$PHQ_score)
cor.test(df_corr$interaction_est, df_corr$OCIR_score)
cor.test(df_corr$interaction_est, df_corr$SIAS_score)
```
```{r}
rand_resp_reg_word_cur_senti_gad <- brm(next_senti | se(next_sd, sigma = TRUE) ~ sentiment * reg_word_ratio *GAD_score + (1+sentiment * reg_word_ratio | ID) +(1 | exam_num),family = gaussian(), data = df_resp_senti_sd_full_PE_mood,chains = 4,cores = 4)

summary(rand_resp_reg_word_cur_senti_gad)
```
#### Centering
```{r}
df_final <- df_resp_senti_sd_full_PE_mood %>%
  group_by(ID) %>%
  mutate(
    # 1. Within-person
    senti_wp = sentiment - mean(sentiment, na.rm = TRUE),
    reg_wp   = reg_word_ratio - mean(reg_word_ratio, na.rm = TRUE),
    
    # 2. Between-person
    senti_bp = mean(sentiment, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  mutate(
    # 3. Level-2 variable
    gad_c = GAD_score - mean(GAD_score, na.rm = TRUE),
    rep_c = ERQ_rep - mean(ERQ_rep, na.rm = TRUE),
    erq_c = ERQ_score - mean(ERQ_score, na.rm = TRUE)
  )
```

```{r}
brm_resp_reg_word_senti_sd_gad_center <- brm(next_senti | se(next_sd, sigma = TRUE) ~ senti_wp+reg_wp*gad_c +(1 + senti_wp*reg_wp | ID) +(1 | exam_num),family = gaussian(),data = df_final,chains = 4,cores = 4
)
```
```{r}
summary(brm_resp_reg_word_senti_sd_gad_center)
```
```{r}
brm_resp_reg_word_senti_sd_gad_center_exam <- brm(next_senti | se(next_sd, sigma = TRUE) ~ senti_wp*reg_wp*gad_c +(1 + senti_wp*reg_wp | ID) +(1 | ID:exam_num),family = gaussian(),data = df_final,chains = 4,cores = 4
)
```

```{r}
summary(brm_resp_reg_word_senti_sd_gad_center_exam)
```
```{r}
comp <- loo_compare(loo(brm_resp_reg_word_senti_sd_gad_center), loo(brm_resp_reg_word_senti_sd_gad_center_exam))
print(comp, simplify = FALSE)
```
#### ERQ
```{r}
brm_resp_reg_word_senti_sd_rep_center <- brm(next_senti | se(next_sd, sigma = TRUE) ~ senti_wp*reg_wp*rep_c +(1 + senti_wp*reg_wp | ID) +(1 | exam_num),family = gaussian(),data = df_final,chains = 4,cores = 4
)
```


```{r}
summary(brm_resp_reg_word_senti_sd_rep_center)
```
```{r}
fit1_baye_zib_reg_ratio_current_senti_gad <- brm(bf(reg_word_ratio ~ sentiment+gad_c + (1|ID) + (1|exam_num), zoi ~ sentiment * gad_c + (1 | ID)),family = zero_one_inflated_beta(), data = df_final)

summary(fit1_baye_zib_reg_ratio_current_senti_gad)
```
```{r}
pp_check(fit1_baye_zib_reg_ratio_current_senti_gad)
```

```{r}
fit_zoib <- brm(
  bf(
    # 1. between 0-1
    reg_word_ratio ~ sentiment * gad_c + (1 | ID) + (1 | exam_num),
    # 1 or zero
    zoi ~ sentiment * gad_c + (1 | ID),
    # probability of 1, not zero
    coi ~ sentiment * gad_c + (1 | ID)
  ),
  data = df_final,
  family = zero_one_inflated_beta(),
  chains = 4, cores = 4, iter = 2000
)
```
```{r}
summary(fit_zoib)
```
```{r}
fit_zoib_pruned <- brm(
  bf(
   
    reg_word_ratio ~ sentiment + gad_c + (1 | ID) + (1 | exam_num),
    
  
    zoi ~ sentiment * gad_c + (1 | ID),
    

    coi ~ sentiment + gad_c + (1 | ID)
  ),
  data = df_final,
  family = zero_one_inflated_beta(),
  chains = 4, cores = 4, iter = 2000
)
```
```{r}
summary(fit_zoib_pruned)
```

```{r}
loo_compare(loo(fit_zoib), loo(fit_zoib_pruned))
```

```{r}
df_final <- df_final %>% dplyr::group_by(ID, exam_num) %>% dplyr::mutate(reg_word_ratio_next = lead(reg_word_ratio))
```

```{r}
fit_zoib_next <- brm(
  bf(
    # 1. between 0-1
    reg_word_ratio_next ~ sentiment * gad_c + (1 | ID) + (1 | exam_num),
    # 1 or zero
    zoi ~ sentiment * gad_c + (1 | ID),
    # probability of 1, not zero
    coi ~ sentiment * gad_c + (1 | ID)
  ),
  data = df_final,
  family = zero_one_inflated_beta(),
  chains = 4, cores = 4, iter = 2000
)
```
```{r}
summary(fit_zoib_next)
```
```{r}
fit_zoib_next_prune <- brm(
  bf(
    # 1. between 0-1
    reg_word_ratio_next ~ sentiment + gad_c + (1 | ID) + (1 | exam_num),
    # 1 or zero
    zoi ~ sentiment * gad_c + (1 | ID),
    # probability of 1, not zero
    coi ~ sentiment * gad_c + (1 | ID)
  ),
  data = df_final,
  family = zero_one_inflated_beta(),
  chains = 4, cores = 4, iter = 2000
)
```
```{r}
summary(fit_zoib_next_prune)
```

```{r}
loo_compare(loo(fit_zoib_next), loo(fit_zoib_next_prune))
```
```{r}
plot(conditional_effects(fit_zoib_pruned, effects = "sentiment", dpar = "mu"), 
     points = TRUE) + 
  ggtitle("Effect on Regulation Intensity (mu)")
```

```{r}
plot(conditional_effects(fit_zoib_pruned, effects = "sentiment:gad_c", dpar = "zoi"), 
     points = TRUE) + 
  ggtitle("Effect on Regulation Intensity (mu)")
```


```{r}
pp_check(fit_zoib_next)
```

#### Individual estimate
```{r}
rand_resp_reg_word_senti_sd_EVPE <- brm(next_senti | se(next_sd, sigma = TRUE) ~ EVPE * reg_word_ratio +(1 + EVPE*reg_word_ratio | ID) +(1 | exam_num),family = gaussian(),data = df_resp_senti_sd_full_PE,chains = 4,cores = 4
)
```
```{r}
summary(rand_resp_reg_word_senti_sd_EVPE)
```

```{r}
re <- ranef(rand_resp_reg_word_senti_sd_EVPE)$ID
```
```{r}
interaction_slope <- re[, "Estimate", "EVPE:reg_word_ratio"]

interaction_df <- data.frame(
  ID = rownames(re),
  interaction_est = interaction_slope
)
```
```{r}
df_corr <- merge(interaction_df, df_mood, by = "ID")
cor.test(df_corr$interaction_est, df_corr$GAD_score)
cor.test(df_corr$interaction_est, df_corr$ERQ_score)
cor.test(df_corr$interaction_est, df_corr$PHQ_score)
cor.test(df_corr$interaction_est, df_corr$OCIR_score)
cor.test(df_corr$interaction_est, df_corr$SIAS_score)
```
```{r}
df_neuro <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/survey_data_f24/negative_emotionality_scores.csv")
df_neu <- merge(interaction_df, df_neuro, by = "ID")
```
```{r}
cor.test(df_neu$interaction_est, df_neu$negative_emotionality)
```


```{r}
library(ggplot2)

ggplot(df_corr, aes(GAD_score, interaction_est)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic()
```



##### sd ~ EVPE*reg_ratio
```{r}
brm_resp_reg_sd_EVPE <- brm(next_sd ~ EVPE * reg_ratio +(1 + EVPE | ID) +(1 | exam_num),family = gaussian(),data = df_resp_senti_sd_full_PE,chains = 4,cores = 4
)

summary(brm_resp_reg_sd_EVPE)
```




### Exam
#### Data prep
```{r}
df_collapsed_senti_score <- df_collapsed_senti_score %>% relocate(exam_num, .after = ID)
df_pre_post_collapsed_reg_exam <- df_collapsed_senti_score %>% dplyr::group_by(ID, exam_num) %>%
  mutate(prev_senti = lag(score_avg),
         post_senti = lead(score_avg),
         prev_peak = lag(score_peak),
         post_peak = lead(score_peak),
         prev_end = lag(score_end),
         post_end = lead(score_end),
         prev_type = lag(collapsed_text_type),
         post_type = lead(collapsed_text_type),
         prev_block_id = lag(block_id),
         post_block_id = lead(collapsed_text_type)
      ) %>%
  ungroup()

#%>% filter(collapsed_text_type == "Regulation")

df_pre_post_collapsed_reg_exam <- df_pre_post_collapsed_reg_exam %>% dplyr::mutate(
  pre_post_reg_avg = post_senti-prev_senti,
  pre_post_reg_peak = post_peak-prev_peak,
  pre_post_reg_end = post_end-prev_end)

df_pre_post_collapsed_reg_exam$exam_num <- as.factor(df_pre_post_collapsed_reg_exam$exam_num)
df_pre_post_collapsed_reg_exam <- df_pre_post_collapsed_reg_exam %>% mutate(responseID = interaction(ID, exam_num, ResponseNumber, sep="_"))
```

#### Pre_post_reg vs. exam_num
```{r}
m1_pre_post_exam_reg <- lmer(pre_post_reg_avg ~ exam_num + 0 + (1 | ID)+ (1|responseID), data = df_pre_post_collapsed_reg_exam)
summary(m1_pre_post_exam_reg)
```

```{r}
plot_model(m1_pre_post_exam_reg, title = "Regulation efficacy across exams")
```

```{r}
emmeans(m1_pre_post_exam_reg, pairwise~exam_num, adjust = "none")
```

```{r}
df_pre_post_collapsed_all$exam_num <- as.factor(df_pre_post_collapsed_all$exam_num)
m1_pre_post_exam_all <- lmer(pre_post_avg ~ exam_num*collapsed_text_type + (1 | ID)+ (1|ResponseNumber), data = df_pre_post_collapsed_all)
summary(m1_pre_post_exam_all)
```

```{r}
pp_check(m1_pre_post_exam_reg)
```
```{r}
m2_pre_post_exam_reg <- brm(pre_post_reg_avg ~ exam_num + (1 | ID)+ (1|ResponseNumber), data = df_pre_post_collapsed_reg,family = gaussian(), chains = 4, cores = 4)
summary(m2_pre_post_exam_reg )
```
```{r}
ggplot(df_pre_post_collapsed_reg, aes(x = as.factor(exam_num), y = pre_post_reg_avg)) +
  geom_boxplot(fill = "skyblue") +
  theme_minimal() +
  labs(x = "Exam Number", y = "Change in Sentiment After Regulation")
```
#### Gender difference
```{r}
# Load in processed qualtrics df
df_mood <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/survey_data_f24/processed/premedEMA_exit_mood_final.csv")
```
```{r}
table(df_mood$sex)
```

```{r}
df_pre_post_collapsed_reg_sex <- inner_join(df_pre_post_collapsed_reg, df_mood, by = "ID")
```
```{r}
m3_pre_post_exam_reg_sex <- lmer(pre_post_reg_avg ~ sex  + (1 | ID)+ (1|responseID), data = df_pre_post_collapsed_reg_sex)
summary(m3_pre_post_exam_reg_sex)
```

```{r}
m3_pre_post_exam_reg_sex <- lmer(pre_post_reg_avg ~ exam_num + sex  + (1 | ID)+ (1|responseID), data = df_pre_post_collapsed_reg_sex)
summary(m3_pre_post_exam_reg_sex)
```
```{r}
ggplot(df_pre_post_collapsed_reg_sex, aes(x = exam_num, y = pre_post_reg_avg, color = sex)) +
  stat_summary(fun = mean, geom = "line", aes(group = sex)) +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.1)
```
```{r}
anova(m3_pre_post_exam_reg_sex, m1_pre_post_exam_reg)
```
```{r}
AIC(m3_pre_post_exam_reg_sex, m1_pre_post_exam_reg)

BIC(m3_pre_post_exam_reg_sex, m_pre_post_exam_reg)
```

####PE vs. Learning rate
```{r}
df_pre_post_collapsed_all <- df_pre_post_collapsed_all %>% group_by(ID, exam_num, ResponseNumber) %>% mutate(pre_post_alpha = lead(pre_post_avg) - pre_post_avg)
```
```{r}
df_pre_post_collapsed_all$exam_num <- as.numeric(df_pre_post_collapsed_all$exam_num)
df_pre_post_collapsed_alpha_cleaned <- df_pre_post_collapsed_all %>%
  group_by(ID) %>%
  filter(exam_num != max(exam_num, na.rm = TRUE)) %>%
  ungroup()
```

```{r}
m1_pre_post_alpha <- lmer(pre_post_alpha ~ collapsed_text_type * as.factor(exam_num) + 0 + (1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed_alpha_cleaned)

summary(m1_pre_post_alpha)
```
```{r}
m2_pre_post_alpha_exam <- lmer(pre_post_alpha ~ as.factor(exam_num) + 0 + (1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed_alpha_cleaned)

summary(m2_pre_post_alpha_exam)
```
##### Regulation
```{r}
df_pre_post_collapsed_reg_alpha <- df_pre_post_collapsed_all %>% filter(collapsed_text_type == "Regulation")

# Remove the maximum exam
df_pre_post_collapsed_reg_alpha_cleaned <- df_pre_post_collapsed_reg_alpha %>%
  group_by(ID) %>%
  filter(exam_num != max(exam_num, na.rm = TRUE)) %>%
  ungroup()
```
```{r}
m2_pre_post_reg_alpha <- lmer(pre_post_alpha ~ as.factor(exam_num) + 0 + (1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed_reg_alpha)
summary(m2_pre_post_reg_alpha)
```

```{r}
pp_check(m2_pre_post_reg_alpha)
```


```{r}
# remove the last exam (no learning rate)
m3_pre_post_reg_alpha_cleaned <- lmer(pre_post_alpha ~ as.factor(exam_num) + 0 + (1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed_reg_alpha_cleaned)

summary(m3_pre_post_reg_alpha_cleaned)
pp_check(m3_pre_post_reg_alpha_cleaned)
```

```{r}
# regulation poly model
m2_pre_post_reg_alpha_poly <- lmer(pre_post_alpha ~ poly(exam_num,2) + 0 + (1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed_reg_alpha)

summary(m2_pre_post_reg_alpha_poly)
```
```{r}
ggplot(df_pre_post_collapsed_reg_alpha, aes(exam_num, pre_post_alpha)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y ~ poly(x, 2))
```

```{r}
nls_model <- nls(pre_post_alpha ~ a * exp(-b * exam_num), data = df_pre_post_collapsed_reg_alpha, start = list(a = -0.1, b = 0.1))

summary(nls_model)
```
```{r}
plot(nls_model)
```

```{r}
#plot(df_pre_post_collapsed_reg_alpha$exam_num, df_pre_post_collapsed_reg_alpha$pre_post_alpha)
#curve(-0.1152 * exp(-0.1005 * x), add = TRUE, col = "red")

library(ggplot2)

ggplot(df_pre_post_collapsed_reg_alpha, aes(x = exam_num, y = pre_post_alpha)) +
  geom_point(alpha = 0.5) +  # Raw data points
  geom_smooth(
    method = "nls",
    formula = y ~ a * exp(-b * x),
    method.args = list(start = c(a = -0.1, b = 0.1)),
    se = FALSE,
    color = "red"
  ) +
  labs(title = "Exponential Decay Fit", x = "Exam Number", y = "pre_post_alpha")
```
```{r}
plot(resid(nls_model) ~ fitted(nls_model))
abline(h = 0, col = "red")
```

```{r}
AIC(m2_pre_post_reg_alpha, nls_model)
# nls model fits better? 
```

```{r}
# sum(is.na(df_pre_post_collapsed_reg_alpha$pre_post_alpha))
df_pre_post_collapsed_reg_alpha$exam_num <-as.numeric(df_pre_post_collapsed_reg_alpha$exam_num)
```

```{r}
library(nlme)
df_grouped <- groupedData(pre_post_alpha ~ exam_num | ID, data = df_pre_post_collapsed_reg_alpha)

str(df_grouped)

df_grouped$exam_num <- as.numeric(df_grouped$exam_num)
```
```{r}
logistic_model <- nlme(
  pre_post_alpha ~ SSlogis(exam_num, Asym, xmid, scal),
  fixed = Asym + xmid + scal ~ 1,
  random = Asym ~ 1 | ID,
  data = df_grouped,
  start = list(
    fixed = c(
      Asym = max(df$pre_post_alpha, na.rm = TRUE),  # Asymptote ≈ max observed value
      xmid = median(df$exam_num),                   # Midpoint ≈ median exam number
      scal = 1                                      # Default slope
    )
  ),
  control = list(msMaxIter = 500, pnlsMaxIter = 50)
)
```


```{r}
nlme_model <- nlme(
  pre_post_alpha ~ SSlogis(exam_num, Asym, xmid, scal),
  fixed = Asym + xmid + scal ~ 1,
  random = Asym ~ 1 | ID,  # Allow asymptote to vary by participant
  data = df_grouped,               # Use the groupedData object
  control = list(msMaxIter = 500)
)
```

##### Expression
```{r}
df_pre_post_collapsed_exp_alpha <- df_pre_post_collapsed_all %>% filter(collapsed_text_type == "Expression")
```

```{r}
m3_pre_post_exp_alpha <- lmer(pre_post_alpha ~ exam_num + 0 + (1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed_exp_alpha)

summary(m3_pre_post_exp_alpha)
```
##### Neither
```{r}
df_pre_post_collapsed_nei_alpha <- df_pre_post_collapsed_all %>% filter(collapsed_text_type == "Neither")
```

```{r}
m4_pre_post_nei_alpha <- lmer(pre_post_alpha ~ exam_num + 0 + (1|ID) + (1|ResponseNumber), data = df_pre_post_collapsed_nei_alpha)

summary(m4_pre_post_nei_alpha)
```

## PE
One PE score per exam
### Data prep
```{r}
df_PE$exam_num <- as.factor(df_PE$exam_num)
df_PE <- df_PE %>% mutate(PE_1_val = case_when(PE_1 < 0 ~ "negative",
                                               PE_1 > 0 ~ "positive",
                                               PE_1 == 0 ~ "zero"), 
                          PE_1_mag = abs(PE_1),
                          PE_2_val = case_when(PE_2 < 0 ~ "negative",
                                               PE_2 > 0 ~ "positive",
                                               PE_2 == 0 ~ "zero"),
                          PE_2_mag = abs(PE_2),
                          EVPE_val = case_when(EVPE < 0 ~ "negative",
                                               EVPE > 0 ~ "positive",
                                               EVPE == 0 ~ "zero"),
                          EVPE_mag = abs(EVPE),)
df_collapsed_senti_score$exam_num <- as.factor(df_collapsed_senti_score$exam_num)
df_collapsed_senti_PE <- inner_join(df_collapsed_senti_score, df_PE, by = c("ID", "exam_num"))
```

### Model
#### PE_2 vs senti_score
```{r}
m1_avg_senti_collapsed_PE_2 <- lmer(score_avg ~ PE_2 + average_grade + (1|ID) + (1|ResponseNumber) + (1|exam_num), data = df_collapsed_senti_PE)
summary(m1_avg_senti_collapsed_PE_2)
```

```{r}
m2_peak_senti_collapsed_PE_2 <- lmer(score_peak ~ PE_2 + (1|ID) + (1|ResponseNumber) + (1|exam_num), data = df_collapsed_senti_PE)

summary(m2_peak_senti_collapsed_PE_2)
```
```{r}
m3_end_senti_collapsed_PE_2 <- lmer(score_end ~ PE_2 + (1|ID) + (1|ResponseNumber) + (1|exam_num), data = df_collapsed_senti_PE)

summary(m3_end_senti_collapsed_PE_2)
```
```{r}
m2_avg_senti_collapsed_PE_2_exam <- lmer(exam_avg ~ PE_2 + (1|ID) + (1|exam_num), data = df_collapsed_senti_score_exam_df)

summary(m2_avg_senti_collapsed_PE_2_exam)
```
####Plotting
```{r}
PE_2_exam_senti_plot <- ggplot(df_collapsed_senti_score_exam_df, aes(x = PE_2, y = exam_avg)) +
  geom_point(size = 2, alpha = 0.6, color = "skyblue2") +
  geom_smooth(method = "lm", se = TRUE, color = "#e6550d", fill = "#fdae6b") +
  labs(
    title = "Relationship between PE 2 and average exam sentiment",
    x = "PE 2",
    y = "Average sentiment score (per exam)"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text( hjust = 0.5)
  )
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/PE_2_exam_senti.png",plot = PE_2_exam_senti_plot, width = 6, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/PE_2_exam_senti.pdf",plot = PE_2_exam_senti_plot, width = 6, heigh = 4, dpi = 300)
PE_2_exam_senti_plot
```
 #### EVPE vs senti_score
```{r}
df_collapsed_senti_score_exam <- df_senti_full %>%
  dplyr::group_by(ID) %>%
  group_modify(~ collapse_text_blocks(
    label_api_text = .x$label_api_text,
    sentiment = .x$api_val_num,
    intensity = .x$api_intensity, 
    exam_num = .x$exam_num)) %>%
  ungroup()

df_collapsed_senti_score_exam <- df_collapsed_senti_score_exam %>%dplyr::group_by(ID, exam_num) %>% mutate(exam_avg = mean(score_avg, na.rm = TRUE)) %>% ungroup()
df_collapsed_senti_score_exam_unique <- df_collapsed_senti_score_exam %>%
  distinct(ID, exam_avg, .keep_all = TRUE)
```
```{r}
df_collapsed_senti_score_exam_df<- inner_join(df_PE,df_collapsed_senti_score_exam_unique, by = c("ID", "exam_num" ))
```

```{r}
# contain response number
m1_avg_senti_collapsed_EVPE_co <- lmer(score_avg ~ EVPE + average_grade + (1|ID) + (1|ResponseNumber) + (1|exam_num), data = df_collapsed_senti_PE)
summary(m1_avg_senti_collapsed_EVPE_co)
```

```{r}
m2_avg_senti_collapsed_EVPE <- lmer(score_avg ~ EVPE + (1|ID) + (1|ResponseNumber) + (1|exam_num), data = df_collapsed_senti_PE)

summary(m2_avg_senti_collapsed_EVPE)
```
```{r}
m2_avg_senti_collapsed_EVPE_exam <- lmer(exam_avg ~ EVPE + (1|ID) + (1|exam_num), data = df_collapsed_senti_score_exam_df)

summary(m2_avg_senti_collapsed_EVPE_exam)
```
####Plotting
```{r}
EVPE_exam_senti_plot <- ggplot(df_collapsed_senti_score_exam_df, aes(x = EVPE, y = exam_avg)) +
  geom_point(size = 2, alpha = 0.6, color = "skyblue2") +
  geom_smooth(method = "lm", se = TRUE, color = "#e6550d", fill = "#fdae6b") +
  labs(
    title = "Relationship between EVPE and average exam sentiment",
    x = "EVPE",
    y = "Average sentiment score (per exam)"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text( hjust = 0.5)
  )
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/EVPE_exam_senti.png",plot = EVPE_exam_senti_plot, width = 6, heigh = 4, dpi = 300)
ggsave(file = "/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/Final_plot/EVPE_exam_senti.pdf",plot = EVPE_exam_senti_plot, width = 6, heigh = 4, dpi = 300)
EVPE_exam_senti_plot
```

```{r}
m2_peak_senti_collapsed_PE <- lmer(score_peak ~ EVPE + (1|ID) + (1|ResponseNumber) + (1|exam_num), data = df_collapsed_senti_PE)

summary(m2_peak_senti_collapsed_EVPE)
```
```{r}
m3_end_senti_collapsed_PE <- lmer(score_end ~ EVPE + (1|ID) + (1|ResponseNumber) + (1|exam_num), data = df_collapsed_senti_PE)

summary(m3_end_senti_collapsed_EVPE)
```
#### PE2 vs. pre-post reg
```{r}
# df_pre_post_collapsed_reg_alpha_cleaned
df_pre_post_collapsed_reg_alpha_cleaned$exam_num <- as.factor(df_pre_post_collapsed_reg_alpha_cleaned$exam_num)
df_PE$exam_num <- as.numeric(df_PE$exam_num)
df_pre_post_collapsed_reg_PE <- inner_join(df_pre_post_collapsed_reg, df_PE, by = c("ID", "exam_num"))

df_pre_post_collapsed_reg$exam_num <- as.numeric(df_pre_post_collapsed_reg$exam_num)
df_pre_post_collapsed_reg_PE_cleaned <- df_pre_post_collapsed_reg_PE %>% mutate(exam_num = as.numeric(exam_num)) %>% 
  group_by(ID) %>%
  filter(exam_num != max(exam_num, na.rm = TRUE)) %>%
  ungroup()
```
```{r}
m1_pre_post_avg_reg_PE_2 <- lmer(pre_post_reg_avg ~ PE_2 + average_grade + exam_num + (1|ID) + (1|responseID), data = df_pre_post_collapsed_reg_PE)

summary(m1_pre_post_avg_reg_PE_2)
```

####EVPE vs. pre_post_reg
```{r}
m1_pre_post_avg_reg_EVPE <- lmer(pre_post_reg_avg ~ EVPE + (1|ID) + (1|exam_num), data = df_pre_post_collapsed_reg_PE)

summary(m1_pre_post_avg_reg_EVPE)
```
```{r}
pp_check(m1_pre_post_avg_reg_EVPE)
```
```{r}
ggplot(data = df_pre_post_collapsed_reg_PE, aes(x = EVPE, y = pre_post_reg_avg)) +
  geom_point() + geom_smooth(method=lm)
```

```{r}
m1_pre_post_avg_reg_EVPE_val <- lmer(pre_post_reg_avg ~ EVPE_val + 0+ (1|ID) + (1|exam_num), data = df_pre_post_collapsed_reg_PE)

summary(m1_pre_post_avg_reg_EVPE_val)
```
```{r}
emmeans(m1_pre_post_avg_reg_EVPE_val, ~EVPE_val)
```
```{r}
plot_model(m1_pre_post_avg_reg_EVPE_val)
```
```{r}
library(effects)
library(lme4)
library(ggplot2)
```

```{r}
ee <- Effect(c("EVPE_val"),m1_pre_post_avg_reg_EVPE_val) 
ee
```

```{r}
ggplot(df_pre_post_collapsed_reg_PE, aes(x = EVPE_val, y = pre_post_reg_avg)) +
  geom_bar(stat = "identity") +
  labs(title = "My Bar Plot",
       subtitle = "Showing values by category",
       x = "Category Name",
       y = "Observed Value")
```
```{r}
ggplot(data = df_pre_post_collapsed_reg_PE, aes(x = EVPE_val, y = pre_post_reg_avg)) +
  geom_point() + geom_smooth(method=lm)
```

```{r}
pp_check(m1_pre_post_avg_reg_EVPE_val)
```
```{r}
m1_pre_post_avg_reg_EVPE_int <- lmer(pre_post_reg_avg ~ EVPE_val*EVPE_mag +0+ (1|ID) + (1|exam_num), data = df_pre_post_collapsed_reg_PE)

summary(m1_pre_post_avg_reg_EVPE_int)
```
```{r}
plot_model(m1_pre_post_avg_reg_EVPE_int)
```


```{r}
pp_check(m1_pre_post_avg_reg_EVPE_int)
```

```{r}
plot_model(m1_pre_post_avg_reg_EVPE_int, type = "int")
```

#### PE vs. Learning
```{r}
m1_pre_post_alpha_reg_pe <- lmer(pre_post_reg_alpha ~ PE_2 +0 + (1|ID) + (1|responseID), data = df_pre_post_collapsed_reg_PE_cleaned)

summary(m1_pre_post_alpha_reg_pe)
```

```{r}
m1_pre_post_alpha_reg_pe_val <- lmer(pre_post_reg_alpha ~ PE_2_val +0 + (1|ID) + (1|responseID), data = df_pre_post_collapsed_reg_PE_cleaned)
summary(m1_pre_post_alpha_reg_pe_val)
```

```{r}
m1_pre_post_alpha_reg_pe_mag <- lmer(pre_post_reg_alpha ~ PE_2_mag +0 + (1|ID) + (1|responseID), data = df_pre_post_collapsed_reg_PE_cleaned)

summary(m1_pre_post_alpha_reg_pe_mag)
```
```{r}
m1_pre_post_alpha_reg_pe_val_mag <- lmer(pre_post_reg_alpha ~ PE_2_mag * PE_2_val + 0 + (1|ID) + (1|responseID), data = df_pre_post_collapsed_reg_PE_cleaned)

summary(m1_pre_post_alpha_reg_pe_val_mag)
```

```{r}
m1_pre_post_alpha_reg_avg <- lmer(pre_post_reg_alpha ~ average_grade +0 + (1|ID) + (1|responseID), data = df_pre_post_collapsed_reg_PE_cleaned)

summary(m1_pre_post_alpha_reg_avg)
```
#### PE_1 vs. pre_post_avg
```{r}
m1_pre_post_avg_reg_pe_1 <- lmer(pre_post_reg_avg ~ PE_1 + (1|ID) + (1|responseID) + (1|exam_num), data = df_pre_post_collapsed_reg_PE)

summary(m1_pre_post_avg_reg_pe_1)
```

#### PE_2 vs. pre_post_avg
```{r}
m1_pre_post_avg_reg_pe <- lmer(pre_post_reg_avg ~ PE_2 + (1|ID) + (1|responseID) + (1|exam_num), data = df_pre_post_collapsed_reg_PE)

summary(m1_pre_post_avg_reg_pe)
```
#### PE_2_mag vs. pre-post_avg
```{r}
m1_pre_post_avg_reg_pe_mag <- lmer(pre_post_reg_avg ~ PE_2_mag + (1|ID) +  (1|responseID), data = df_pre_post_collapsed_reg_PE)

summary(m1_pre_post_avg_reg_pe_mag)
```
#### PE_2_mag*average vs. pre-post
```{r}
m2_pre_post_avg_reg_pe_mag_intx <- lmer(pre_post_reg_avg ~  PE_2_mag*average_grade + 0 + (1|ID) + (1|responseID), data = df_pre_post_collapsed_reg_PE)

summary(m2_pre_post_avg_reg_pe_mag_intx)
```
#### PE_2_val vs. pre-post reg
```{r}
m3_pre_post_avg_reg_pe_val <- lmer(pre_post_reg_avg ~ PE_2_val + 0 + (1|ID) + (1|exam_num) + (1|responseID), data = df_pre_post_collapsed_reg_PE)

summary(m3_pre_post_avg_reg_pe_val)
```
```{r}
emmeans(m3_pre_post_avg_reg_pe_val, pairwise ~ PE_2_val)
```

#### PE_2_val*average vs. pre-post reg
```{r}
m4_pre_post_avg_reg_pe_val_intx <- lmer(pre_post_reg_avg ~  PE_2_val*average_grade + 0 + (1|ID) + (1|responseID), data = df_pre_post_collapsed_reg_PE)

summary(m4_pre_post_avg_reg_pe_val_intx)
```

```{r}
m1_pre_post_avg_reg_pe_val_mag <- lmer(pre_post_reg_avg ~  PE_2_val * PE_2_mag + 0 + (1|ID) + (1|exam_num) + (1|responseID), data = df_pre_post_collapsed_reg_PE)

summary(m1_pre_post_avg_reg_pe_val_mag)
```

#### EVPE val
```{r}
m1_pre_post_avg_reg_evpe_val <- lmer(pre_post_reg_avg ~  EVPE_val + 0 + (1|ID) + (1|exam_num) + (1|responseID), data = df_pre_post_collapsed_reg_PE)

summary(m1_pre_post_avg_reg_evpe_val)
```
```{r}
emmeans(m1_pre_post_avg_reg_evpe_val, pairwise ~ EVPE_val)
```
```{r}
m1_pre_post_avg_reg_evpe <- lmer(pre_post_reg_avg ~  EVPE  + (1|ID) + (1|exam_num) + (1|responseID), data = df_pre_post_collapsed_reg_PE)

summary(m1_pre_post_avg_reg_evpe)
```
#### EVPE int vs. pre-post-reg
```{r}
m1_pre_post_avg_reg_evpe_val_mag <- lmer(pre_post_reg_avg ~  EVPE_val * EVPE_mag + 0 + (1|ID) + (1|responseID) + (1|exam_num), data = df_pre_post_collapsed_reg_PE)

summary(m1_pre_post_avg_reg_evpe_val_mag)
```
```{r}
emmeans(m1_pre_post_avg_reg_evpe_val, pairwise ~ EVPE_val)
```
#### Average * pre-post_reg
```{r}
m1_pre_post_avg_reg_avg <- lmer(pre_post_reg_avg ~  average_grade + 0 + (1|ID) + (1|responseID), data = df_pre_post_collapsed_reg_PE)

summary(m1_pre_post_avg_reg_avg)
```
```{r}
m2_pre_post_avg_reg_avg_PE_val_mag <- lmer(pre_post_reg_avg ~  PE_2_val*PE_2_mag*average_grade + 0 + (1|ID) + (1|responseID), data = df_pre_post_collapsed_reg_PE)

summary(m2_pre_post_avg_reg_avg_PE_val_mag)
```

```{r}

```

##Individual difference
### Load in survey data
```{r}
df_mood <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/survey_data_f24/processed/premedEMA_exit_mood_final.csv")
```

```{r}
# Load in neuroticism survey
df_neuro <- read.csv("/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/survey_data_f24/negative_emotionality_scores.csv")
colnames(df_neuro)[1] = "ID"
```

```{r}
df_pre_post_collapsed_tmp <- df_pre_post_collapsed %>% relocate(exam_num, .after = ID)
```


```{r}
# df_pre_post_collapsed_reg_tmp <- df_pre_post_collapsed_tmp %>% group_by (ID) %>% summarise(pre_post_reg_mean = mean(pre_post_reg_avg)) %>% ungroup()
```

```{r}
df_pre_post_collapsed_mood <- inner_join(df_pre_post_collapsed_tmp, df_mood, by = "ID")

df_pre_post_collapsed_mood$exam_num <- as.factor(df_pre_post_collapsed_mood$exam_num)
df_pre_post_collapsed_mood_pe <- inner_join(df_pre_post_collapsed_mood, df_PE, by = c("ID", "exam_num"))
```
### lmer model + GAD
```{r}
m5_pre_post_avg_senti_collapsed_text_gad <- lmer(pre_post_avg ~ GAD_score+text_type +GAD_score*text_type + (1|ID) + +(1|exam_num) + (1|ResponseNumber), data = df_pre_post_collapsed_mood_pe)
summary(m5_pre_post_avg_senti_collapsed_text_gad)
```

```{r}
pp_check(m5_pre_post_avg_senti_collapsed_text_gad)
```

### Transition between positive - neutral/positive - negative
```{r}
df_transitions <- df_pre_post_collapsed %>% filter(block_sentiment == "POSITIVE") %>%
  dplyr::mutate(transition_type = case_when(
    post_block_senti == "NEGATIVE" ~ "pos_neg",
    post_block_senti == "NEUTRAL" ~ "pos_neu",
    TRUE ~ NA_character_
  )) %>% filter(!is.na(transition_type))
```

```{r}
df_transition_counts <- df_transitions %>%
  dplyr::group_by(ID, exam_num, ResponseNumber) %>%
  summarise(
    Pos_to_Neg = sum(transition_type == "pos_neg"),
    Pos_to_Neu = sum(transition_type == "pos_neu"),
    .groups = "drop"
  )
```
```{r}
df_transition_counts$ID <- as.integer(df_transition_counts$ID)
df_transition_counts$exam_num <- as.integer(df_transition_counts$exam_num)
df_transition_counts$ResponseNumber <- as.integer(df_transition_counts$ResponseNumber)
df_transition_counts_gad <- inner_join(df_transition_counts, df_mood, by = "ID")
df_transition_counts_gad_PE <- inner_join(df_transition_counts_gad, df_PE, by = c("ID", "exam_num"))
```
```{r}
cor.test(df_transition_counts_gad$GAD_score, df_transition_counts_gad$Pos_to_Neu)

```
```{r}
cor.test(df_transition_counts_gad$GAD_score, df_transition_counts_gad$Pos_to_Neg)
```
```{r}
cor.test(df_transition_counts_gad_PE$GAD, df_transition_counts_gad_PE$Pos_to_Neg)
```
```{r}
cor.test(df_transition_counts_gad_PE$GAD, df_transition_counts_gad_PE$Pos_to_Neu)
```
```{r}
m7_transit_neg_gad_EVPE <- lmer(Pos_to_Neg ~ EVPE + GAD + (1|ID) + (1|exam_num), data = df_transition_counts_gad_PE)
summary(m7_transit_neg_gad_EVPE)
```
```{r}
m7_transit_neg_EVPE<- lmer(Pos_to_Neg ~ EVPE + (1|ID) + (1|exam_num), data = df_transition_counts_gad_PE)
summary(m7_transit_neg_EVPE)
```
#### Final: pos_to_neg ~ GAD_score
```{r}
m7_transit_neg_gad_score <- lmer(Pos_to_Neg ~ GAD_score + (1|ID) + (1|exam_num), data = df_transition_counts_gad_PE)
summary(m7_transit_neg_gad_score)
```
```{r}
plot_model(m7_transit_neg_gad_score, type = "pred", terms = "GAD_score")
```

```{r}
library(ggeffects)
library(ggplot2)

GAD_pos_neg_plot <- ggpredict(
  m7_transit_neg_gad_score,
  terms = "GAD_score"
)

GAD_pos_neg_plot_df <- as.data.frame(GAD_pos_neg_plot)

ggplot() +
  # Original observations
  geom_point(
    data = df_transition_counts_gad_PE,
    aes(x = GAD_score, y = Pos_to_Neg),
    alpha = 0.3,
    color = "lightskyblue1",
    size = 2
  ) +

  # 95% CI
  geom_ribbon(
    data = GAD_pos_neg_plot_df,
    aes(
      x = x,
      ymin = conf.low,
      ymax = conf.high
    ),
    fill = "skyblue3",
    alpha = 0.2
  ) +

  # Model-estimated relationship
  geom_line(
    data = GAD_pos_neg_plot_df,
    aes(x = x, y = predicted),
    color = "skyblue3",
    linewidth = 1.2
  ) +

  labs(
    x = "GAD Score",
    y = "Positive-to-Negative Transitions"
  ) +

  theme_classic()
```
```{r}
plot_counts <- df_transition_counts_gad_PE %>%
  dplyr::count(GAD_score, Pos_to_Neg)

ggplot(plot_counts,
       aes(x = GAD_score, y = Pos_to_Neg)) +
  geom_point(
    aes(size = n),
    alpha = .5,
    color = "skyblue3"
  ) +
  geom_smooth(
    data = df_transition_counts_gad_PE,
    aes(x = GAD_score, y = Pos_to_Neg),
    method = "lm",
    se = TRUE,
    inherit.aes = FALSE
  ) +
  scale_y_continuous(breaks = scales::pretty_breaks()) +
  labs(
    x = "GAD Score",
    y = "Positive-to-Negative Transitions",
    size = "Number of observations"
  ) +
  theme_classic()
```


```{r}
m7_transit_neg_gad_score_EVPE <- lmer(Pos_to_Neg ~ EVPE + GAD_score + (1|ID) + (1|exam_num), data = df_transition_counts_gad_PE)
summary(m7_transit_neg_gad_score_EVPE)
```
```{r}
m7_transit_neg_gad_score_EVPE_int <- lmer(Pos_to_Neg ~ EVPE + GAD_score + EVPE*GAD_score + (1|ID) + (1|exam_num), data = df_transition_counts_gad_PE)
summary(m7_transit_neg_gad_score_EVPE_int)
```
```{r}
# comparison: interaction model is not better than the simple model
anova(m7_transit_neg_gad_score,m7_transit_neg_gad_score_EVPE, m7_transit_neg_gad_score_EVPE_int)
```

```{r}
m7_transit_neu_gad_EVPE <- lmer(Pos_to_Neu ~ EVPE + GAD + (1|ID) + (1|exam_num), data = df_transition_counts_gad_PE)
summary(m7_transit_neu_gad_EVPE)
```
```{r}
m7_transit_neu_gad_EVPE <- lmer(Pos_to_Neu ~ EVPE + GAD + (1|ID) + (1|exam_num), data = df_transition_counts_gad_PE)
summary(m7_transit_neu_gad_EVPE)
```
#### Regulation?
```{r}
# extract regulation ratio for response
df_transitions$ID <- as.integer(df_transitions$ID)
df_transitions$exam_num <- as.integer(df_transitions$exam_num)
df_transitions$ResponseNumber <- as.integer(df_transitions$ResponseNumber)


```
```{r}
df_transition_reg_counts <- df_transitions %>%
  dplyr::group_by(ID, exam_num, ResponseNumber) %>%
  summarise(
    Pos_to_Neg = sum(transition_type == "pos_neg"),
    Pos_to_Neu = sum(transition_type == "pos_neu"),
    .groups = "drop"
  )

df_reg_ratio_transit_mood <-  inner_join(df_resp_senti_full, df_transition_counts_gad_PE, by = c("ID", "exam_num","ResponseNumber"))

```
```{r}
m7_transit_neg_reg <- lmer(Pos_to_Neg ~ reg_word_ratio + (1|ID) + (1|exam_num), data = df_reg_ratio_transit_mood)
summary(m7_transit_neg_reg)
```

```{r}
m7_transit_neg_gad_score_reg <- lmer(Pos_to_Neg ~ GAD_score + reg_word_ratio + (1|ID) + (1|exam_num), data = df_reg_ratio_transit_mood)
summary(m7_transit_neg_gad_score_reg)
```
```{r}
m7_transit_neg_gad_score_reg_int <- lmer(Pos_to_Neg ~ GAD_score + reg_ratio + GAD_score*reg_ratio + (1|ID) + (1|exam_num), data = df_reg_ratio_transit_mood)
summary(m7_transit_neg_gad_score_reg_int)
```

### regulation after pos adn neg Phrasewise - Transition
```{r}
df_senti_full_nona <- df_senti_full %>% filter(!is.na(api_val))
df_phrase_transition <- df_senti_full_nona %>%
  arrange(ID, exam_num, ResponseNumber) %>%
  group_by(ID, exam_num, ResponseNumber) %>%
  mutate(
    post_type = lead(label_api_text)
  ) %>%
  ungroup()

expr_phrase_df <- df_phrase_transition %>%
  filter(label_api_text == "Expression")

phrase_transition_summary <- expr_phrase_df %>%
  group_by(api_val) %>%
  summarise(
    n_expression = n(),
    n_to_regulation = sum(post_type == "Regulation", na.rm = TRUE),
    proportion = n_to_regulation / n_expression
  )
phrase_transition_summary

```

```{r}
expr_phrase_df <- expr_phrase_df %>% dplyr::mutate(next_reg = ifelse(post_type == "Regulation", 1, 0),
                                                   current_valence = factor(api_val, 
                                                                            levels = c("NEGATIVE", "POSITIVE","MIXED","NEUTRAL")))
```

```{r}
library(brms)

m_valence_reg_transition <- brm(
  next_reg ~ current_valence +
    (1 | ID) +
    (1 | exam_num),
  family = bernoulli(link = "logit"),
  data = expr_phrase_df,
  chains = 4,
  cores = 4,
  iter = 4000
)
summary(m_valence_reg_transition)
```
```{r}
emm <- emmeans(
  m_valence_reg_transition,
  ~ current_valence,
  type = "response"
)

emm
pairs(emm)
```
posterior probability
```{r}
newdat <- data.frame(
  current_valence = factor(
    c("NEGATIVE", "POSITIVE", "NEUTRAL", "MIXED"),
    levels = levels(expr_phrase_df$current_valence)
  )
)

p <- posterior_epred(
  m_valence_reg_transition,
  newdata = newdat,
  re_formula = NA
)
```
```{r}
# assuming columns are:
# 1 Negative
# 2 Positive
# 3 Neutral
# 4 Mixed

# Estimated probabilities
apply(p, 2, median)

# 95% credible intervals
apply(p, 2, quantile, probs = c(.025, .975))
```

```{r}
diff_neg_pos <- p[, 1] - p[, 2]

quantile(diff_neg_pos, c(.025, .5, .975))

median(diff_neg_pos>0)
mean(diff_neg_pos > 0)
```
```{r}
plot_df <- data.frame(
  current_valence = newdat$current_valence,
  predicted = apply(p, 2, median),
  lower = apply(p, 2, quantile, probs = 0.025),
  upper = apply(p, 2, quantile, probs = 0.975)
)

plot_df
```
```{r}
ggplot(
  plot_df,
  aes(
    x = current_valence,
    y = predicted,
    color = current_valence
  )
) +
  geom_point(size = 3.5) +
  geom_errorbar(
    aes(ymin = lower, ymax = upper),
    width = 0.12,
    linewidth = 0.9
  ) +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 1)
  ) +
  labs(
    x = "Expression Valence",
    y = "Probability of Subsequent Regulation",
    title = "Probability of Regulation Following Emotional Expression"
  ) +
  theme_classic() +
  theme(
    legend.position = "none"
  )
```


```{r}
ggplot(phrase_transition_summary,
       aes(x = api_val,
           y = proportion,
           fill =  api_val)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = scales::percent(proportion)),
            vjust = -0.4) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    x = "Expression Valence",
    y = "Probability that the Next Phrase is Regulation"
  ) +
  theme_classic()
```
#### transition modelling
```{r}
df_phrase_transition <- df_phrase_transition %>% 
  arrange(ID, exam_num, ResponseNumber) %>%
  group_by(ID, exam_num, ResponseNumber) %>%
  mutate(
    prev_type = lag(label_api_text),
    prev_val   = lag(api_val),
    next_val   = lead(api_val)
  ) %>%
  ungroup()

df_phrase_transit_reg <- df_phrase_transition %>%
  filter(label_api_text == "Regulation")
```

```{r}
df_phrase_transit_reg$next_val <- relevel(
  factor(df_phrase_transit_reg$next_val),
  ref = "NEUTRAL")
m_transit_after_reg <- brm(
  next_val ~ prev_val +
    (1 | ID) +
    (1 | exam_num),
  family = categorical(),
  data = df_phrase_transit_reg
)
summary(m_transit_after_reg)
```
```{r}
df_phrase_transit_reg <- df_phrase_transit_reg %>%
  mutate(
    became_neutral = next_val == "neutral"
  )

m2_transit_neutral_after_reg <- brm(
  became_neutral ~ prev_val +
    (1 | ID) +
    (1 | exam_num),
  family = bernoulli(),
  data = df_phrase_transit_reg
)
summary(m2_transit_neutral_after_reg)
```


### Blockwise - Transition between negative - neutral/positive

```{r}
library(dplyr)
expr_df <- df_pre_post_collapsed %>%
  filter(text_type == "Expression")

transition_summary <- expr_df %>%
  group_by(block_sentiment) %>%
  summarise(
    n_expression = n(),
    n_to_regulation = sum(post_type == "Regulation", na.rm = TRUE),
    proportion = n_to_regulation / n_expression
  )
transition_summary
```
```{r}
ggplot(transition_summary,
       aes(x = block_sentiment,
           y = proportion,
           fill =  block_sentiment)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = scales::percent(proportion)),
            vjust = -0.4) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    x = "Expression Valence",
    y = "Probability that the Next Segment is Regulation"
  ) +
  theme_classic()
```

```{r}
df_transitions_neg <- df_pre_post_collapsed %>% filter(block_sentiment == "NEGATIVE") %>%
  dplyr::mutate(transition_type = case_when(
    post_block_senti == "POSITIVE" ~ "neg_pos",
    post_block_senti == "NEUTRAL" ~ "neg_neu",
    TRUE ~ NA_character_
  )) %>% filter(!is.na(transition_type))
```

```{r}
df_transition_neg_counts <- df_transitions_neg %>%
  dplyr::group_by(ID, exam_num) %>%
  summarise(
    Neg_to_Pos = sum(transition_type == "neg_pos"),
    Neg_to_Pos = sum(transition_type == "neg_neu"),
    .groups = "drop"
  )
```
```{r}
df_transition_neg_counts$ID <- as.integer(df_transition_neg_counts$ID)
df_transition_neg_counts$exam_num <- as.integer(df_transition_neg_counts$exam_num)
df_transition_neg_counts_gad <- inner_join(df_transition_neg_counts, df_mood, by = "ID")
df_transition_neg_counts_gad_PE <- inner_join(df_transition_neg_counts_gad, df_PE, by = c("ID", "exam_num"))
```
####Neg - Pos
```{r}
m8_transit_neg_pos_gad_score <- lmer(Neg_to_Pos ~ GAD_score + (1|ID) + (1|exam_num), data = df_transition_neg_counts_gad_PE)
summary(m8_transit_neg_pos_gad_score)
```
```{r}
m8_transit_neg_pos_EVPE <- lmer(Neg_to_Pos ~ EVPE + (1|ID) + (1|exam_num), data = df_transition_neg_counts_gad_PE)
summary(m8_transit_neg_pos_EVPE)
```

### current_senti ~ GAD +reg_ratio+PE
```{r}

```

```{r}
moodScale_list <- c(
  "GAD_score",
  "EPSI_score",
  "EPSI_binge",       
  "EPSI_purge",       
  "EPSI_restr",      
  "EPSI_exce",          
  "SIR_score",          
  "SIR_disc",          
  "SIR_acq",            
  "SIAS_score",         
  "OCIR_score",         
  "OCIR_check",         
  "OCIR_order",
  "OCIR_wash",          
  "OCIR_obs",
  "NIDA_ALC_score",
  "NIDA_DRUGS_score",
  "ASRM_score",         
  "PQB_score",          
  "PQB_distress_score",
  "MSPSS_score",
  "MSPSS_so",           
  "MSPSS_fmly",         
  "MSPSS_frnd",         
  "ERQ_score",         
  "ERQ_rep",            
  "ERQ_sup",            
  "PHQ_score"
)

```

```{r}
aNameSig="/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/cor/pre_post_reg_mood/significant"
dir.create(aNameSig)
currentX = "pre_post_reg_mean"
for(currentY in moodScale_list){
  mydata = df_pre_post_collapsed_reg_mood
  fname=sprintf('/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/cor/pre_post_reg_mood/Correl_%s_%s.pdf', currentX, currentY)
  fname_sig=sprintf('/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/cor/pre_post_reg_mood/significant/Correl_%s_%s.pdf',currentX, currentY)
  plotTitle=sprintf('%s_vs_%s',currentX, currentY)
  xlab = currentX
  ylab= currentY
  myScatterPlot_SAS(mydata,fname, currentX, currentY, xlab, ylab, plotTitle,fname_sig)
}

```

### Neuroticism correlation
```{r}
df_pre_post_collapsed_reg_neuro <- inner_join(df_pre_post_collapsed_reg_tmp, df_neuro, by = "ID")

df_pre_post_collapsed_reg_neuro_without_max <- df_pre_post_collapsed_reg_neuro %>%
  group_by(ID) %>%
  mutate() %>%
  ungroup()

print(df_without_max)
```

```{r}
df_label_ratio_per_exam_neuro <- inner_join(df_label_ratio_wide_per_exam, df_neuro, by = "ID")
```
```{r}
plot(df_label_ratio_per_exam_neuro$negative_emotionality, df_label_ratio_per_exam_neuro$reg_exam_avg )
```
```{r}
m1_reg_neuro_model <- lmer(reg_exam_avg ~ negative_emotionality + 0+ (1|ID)+(1|exam_num), data = df_label_ratio_per_exam_neuro)

summary(m1_reg_neuro_model)
```

```{r}
# Check with aaron
quadratic_reg_model <- lmer(reg_exam_avg ~ negative_emotionality+I(negative_emotionality^2) + 0+ (1|ID)+(1|exam_num), data = df_label_ratio_per_exam_neuro)

summary(quadratic_reg_model)
# pp_check(quadratic_model)
```
```{r}
quadratic_exp_model <- lmer(exp_exam_avg ~ negative_emotionality+I(negative_emotionality^2) + (1|ID)+(1|exam_num), data = df_label_ratio_per_exam_neuro)

summary(quadratic_exp_model)
```
```{r}
quadratic_nei_model <- lmer(nei_exam_avg ~ negative_emotionality+I(negative_emotionality^2) + (1|ID)+(1|exam_num), data = df_label_ratio_per_exam_neuro)

summary(quadratic_nei_model)
```
#### Adding PE
```{r}
df_label_ratio_per_exam_neuro_PE <- inner_join(df_label_ratio_per_exam_neuro, df_PE, by = c("ID", "exam_num"))
```

```{r}
m1_reg_ratio_neuro_PE_exam <- lmer(reg_exam_avg ~ PE_2+negative_emotionality.y + 0+ (1|ID)+(1|exam_num), data = df_label_ratio_per_exam_neuro_PE)
summary(m1_reg_ratio_neuro_PE_exam)
```
```{r}
pp_check(m1_reg_ratio_neuro_PE_exam)
```

```{r}
m1_reg_ratio_neuro_PE_val_exam <- lmer(reg_exam_avg ~ PE_2_val + 0+ (1|ID)+(1|exam_num), data = df_label_ratio_per_exam_neuro_PE)
summary(m1_reg_ratio_neuro_PE_val_exam)
```
```{r}
pp_check(m1_reg_ratio_neuro_PE_val_exam)
```

```{r}
m1_exp_ratio_neuro_PE_val_exam <- lmer(exp_exam_avg ~ PE_2_val*PE_2_mag + 0+ (1|ID)+(1|exam_num), data = df_label_ratio_per_exam_neuro_PE)

summary(m1_exp_ratio_neuro_PE_val_exam)
```
```{r}
m1_nei_ratio_neuro_PE_val_exam <- lmer(nei_exam_avg ~ PE_2_val*PE_2_mag + 0+ (1|ID)+(1|exam_num), data = df_label_ratio_per_exam_neuro_PE)

summary(m1_nei_ratio_neuro_PE_val_exam)
```
```{r}
pp_check(m1_nei_ratio_neuro_PE_val_exam)
```

#### Adding word count
```{r}
# Summarize word count based on exam and text_label
df_word_acount_per_exam <- df_response_full %>% group_by(ID, exam_num, label_api_text) %>% summarise(word_count_sum = sum(word_count)) %>% ungroup()
```
```{r}
df_word_acount_per_exam_wide <- df_word_acount_per_exam %>%
  group_by(ID, exam_num, label_api_text) %>%
  pivot_wider(
    names_from = label_api_text,
    values_from = word_count_sum,
    names_glue = "{label_api_text}_count",  # Format column names
    values_fill = 0  # Replace NA with 0 if a label is missing
  )
df_word_acount_per_exam_wide$exam_num <- as.factor(df_word_acount_per_exam_wide$exam_num)
```

```{r}
df_label_ratio_per_exam_neuro_PE_count <- inner_join(df_label_ratio_per_exam_neuro_PE, df_word_acount_per_exam_wide, by = c("ID", "exam_num"))
```
```{r}
df_label_ratio_per_exam_neuro_PE_count <- df_label_ratio_per_exam_neuro_PE_count %>% group_by(ID, exam_num) %>% mutate(total_count = Expression_count+ Regulation_count+ Neither_count) %>% ungroup()
```

```{r}
m1_PE_val_total_count <- lmer(total_count ~ PE_2_val + 0+ (1|ID) + (1|exam_num), data = df_label_ratio_per_exam_neuro_PE_count)
summary(m1_PE_val_total_count)
pp_check(m1_PE_val_total_count)
```

```{r}
m2_PE_total_count <- lmer(total_count ~ PE_2 + 0+ (1|ID) + (1|exam_num), data = df_label_ratio_per_exam_neuro_PE_count)
summary(m2_PE_total_count)
```
```{r}
m2_PE_val_mag_total_count <- lmer(total_count ~ PE_2_val * PE_2_mag + 0+ (1|ID) + (1|exam_num), data = df_label_ratio_per_exam_neuro_PE_count)
summary(m2_PE_val_mag_total_count)
pp_check(m2_PE_val_mag_total_count)
```
#### Adding regulation count
```{r}
m3_PE_reg_count <- lmer(Regulation_count ~ PE_2 + 0+ (1|ID) + (1|exam_num), data = df_label_ratio_per_exam_neuro_PE_count)
summary(m3_PE_reg_count)
```

```{r}
m3_PE_val_reg_count <- lmer(Regulation_count ~ PE_2_val + 0+ (1|ID) + (1|exam_num), data = df_label_ratio_per_exam_neuro_PE_count)
summary(m3_PE_val_reg_count)
```
```{r}
pp_check(m3_PE_val_reg_count)
```

#### pre_post_reg_mean vs. neuroticism
```{r}
cor.test (df_pre_post_collapsed_reg_neuro$negative_emotionality, df_pre_post_collapsed_reg_neuro$pre_post_reg_mean)

```


```{r}
# plot(df_pre_post_collapsed_reg_neuro$pre_post_reg_mean, df_pre_post_collapsed_reg_neuro$negative_emotionality)
currentX = "negative_emotionality"
currentY = "pre_post_reg_mean"
xlab = "neuroticism score"
ylab = "pre-post regulation score"
plotTitle = "Neuroticism vs. Pre-post reg score"
fname=sprintf('/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/cor/pre_post_reg_neu/Correl_%s_%s.pdf', currentX, currentY)
  fname_sig=sprintf('/Users/runanwang/Desktop/A_Manetee_lab/Projects/Learning_emotion_regulation/Data/API/Figure/cor/pre_post_reg_neu/significant/Correl_%s_%s.pdf',currentX, currentY)

myScatterPlot_SAS(df_pre_post_collapsed_reg_neuro,fname, currentX, currentY, xlab, ylab, plotTitle,fname_sig)

```


